---
title: "Model Selection for Environmental Parameters in SGD that may affect Physiological Rates"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

## Loading libraries 
```{r, echo=FALSE}
library(LoLinR)
library(lubridate)
library(patchwork)
library(tidyverse)
library(here)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(agricolae)
library(lme4)
library(lmerTest)
library(modelsummary)
library(performance)
library(emmeans)
library(MuMIn)
library(broom.mixed)
```

## Loading Data
```{r, echo=FALSE}
#RespoR_Normalized_Full_ExcelUpdates <- read_csv(here::here("Data","RespoFiles", "Respo_RNormalized_AllRates.csv"))
#NEC_wnuts <- read_csv(here("Data", "NECnuts_withpH.csv"))
#FULL_RespoNEC_allParams <- read_csv(here("Data", "RespoR_Normalized_Full_withNEC_ExcelUpdates.csv"))
RespoR_Normalized_Full_withNEC_nutrients <- read_csv(here::here("Data", "RespoR_Normalized_Full_withNEC_andallnutrients.csv"))
```

### Tidy the data in a way that will be useful for model selection 
separate by site (V/C) and by physio measurement (NP/R/GP/C)

```{r}
RespoR_Normalized_Full_withNEC_nutrients <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  #select(!c("pH","light_dark", "umol.cm2.hr_uncorr", "TrisCalDate":"temp_C", "salinity_insitu":"SGD_number_initial")) %>% 
  mutate(Salinity=salinity)

RespoR_Normalized_Full_withNEC_nutrients$phosphate_umolL <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$phosphate_umolL)
RespoR_Normalized_Full_withNEC_nutrients$silicate_umolL <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$silicate_umolL)
RespoR_Normalized_Full_withNEC_nutrients$NN_umolL <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$NN_umolL)
RespoR_Normalized_Full_withNEC_nutrients$ammonia_umolL <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$ammonia_umolL)
RespoR_Normalized_Full_withNEC_nutrients$Salinity <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$Salinity)
RespoR_Normalized_Full_withNEC_nutrients$new_pH <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$new_pH)
RespoR_Normalized_Full_withNEC_nutrients$TA_initial <- as.numeric(RespoR_Normalized_Full_withNEC_nutrients$TA_initial)
RespoR_Normalized_Full_withNEC_nutrients$new_colonynumber <- as.character(RespoR_Normalized_Full_withNEC_nutrients$new_colonynumber)

RespoR_Normalized_Full_ExcelUpdates_V_NP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari", 
         P_R=="NP") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr))

RespoR_Normalized_Full_ExcelUpdates_V_GP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari", 
         P_R=="GP") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr))

RespoR_Normalized_Full_ExcelUpdates_V_R <- RespoR_Normalized_Full_withNEC_nutrients %>% 
   filter(site=="Varari", 
         P_R=="R") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr))

RespoR_Normalized_Full_ExcelUpdates_C_NP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral", 
         P_R=="NP") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  drop_na(Predictor_Values)

RespoR_Normalized_Full_ExcelUpdates_C_GP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral", 
         P_R=="GP") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  drop_na(Predictor_Values)

RespoR_Normalized_Full_ExcelUpdates_C_R <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral", 
         P_R=="R") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  drop_na(Predictor_Values)

```

### Make nonlienar models for each of these 

```{r, echo=FALSE}
## for Varari NP 
MS_V_NP_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_V_NP %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_V_NP_nonlinear

MS_V_NP_nonlinear_fit <- MS_V_NP_nonlinear$fit # shows you each of the models

MS_V_NP_nonlinear_fitresults <- MS_V_NP_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "V_NP.csv"))

## for Varari GP
MS_V_GP_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_V_GP %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_V_GP_nonlinear

MS_V_GP_nonlinear_fit <- MS_V_GP_nonlinear$fit # shows you each of the models

MS_V_GP_nonlinear_fitresults <- MS_V_GP_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "V_GP.csv"))

## for Varari R
MS_V_R_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_V_R %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_V_R_nonlinear

MS_V_R_nonlinear_fit <- MS_V_R_nonlinear$fit # shows you each of the models

MS_V_R_nonlinear_fitresults <- MS_V_R_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "V_R.csv"))

## for Cabral R
MS_C_R_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_C_R %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_C_R_nonlinear

MS_C_R_nonlinear_fit <- MS_C_R_nonlinear$fit # shows you each of the models

MS_C_R_nonlinear_fitresults <- MS_C_R_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "C_R.csv"))

## for Cabral NP
MS_C_NP_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_C_NP %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_C_NP_nonlinear

MS_C_NP_nonlinear_fit <- MS_C_NP_nonlinear$fit # shows you each of the models

MS_C_NP_nonlinear_fitresults <- MS_C_NP_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "C_NP.csv"))


## for Cabral GP #### THERE IS A SINGULAR BOUNDARY WARNING POPPING UP HERE 
MS_C_GP_nonlinear <- RespoR_Normalized_Full_ExcelUpdates_C_GP %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
  mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_C_GP_nonlinear

MS_C_GP_nonlinear_fit <- MS_C_GP_nonlinear$fit # shows you each of the models

MS_C_GP_nonlinear_fitresults <- MS_C_GP_nonlinear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "C_GP.csv"))

```

### Clean Names 
```{r}
###########################################################
### clean names and calculating delta AIC for params for each site and physio measurement 
###########################################################

### Cabral GP 
MS_C_GP_nonlinear_fitresults_cleannames <- MS_C_GP_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_C_GP_nonlinear_fitresults_cleannames
## result: Silicate is strongest driver (sig p-value), rest are more than 2 AIC 
## WHEN LOGGED: Silicate is lowest AIC, ammonia jsut over 2 (both have sig pvals)

### Cabral NP 
MS_C_NP_nonlinear_fitresults_cleannames <- MS_C_NP_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_C_NP_nonlinear_fitresults_cleannames
## result: Salinity is strongest driver with silicate behind by <1 AIC (both sig p values)
## WHEN LOGGED: Salinity is strongest driver with silicate within 2 AIC (both sig p values)

### Cabral R 
MS_C_R_nonlinear_fitresults_cleannames <- MS_C_R_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_C_R_nonlinear_fitresults_cleannames
## result: NN is strongest driver (sig p value), Ammonia less than 2 AIC , phosphate just over 2
## WHEN LOGGED: Ammonia is lowest AIC and NN is just over 2 (both are signif)


### Varari R 
MS_V_R_nonlinear_fitresults_cleannames <- MS_V_R_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_V_R_nonlinear_fitresults_cleannames
## result: pH is strongest driver (sig pval) - TA under 2 and Phosphate 
## WHEN LOGGED Silicate is lowest AIC then pH is within 2 AIC. Both are signif

### Varari NP 
MS_V_NP_nonlinear_fitresults_cleannames <- MS_V_NP_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_V_NP_nonlinear_fitresults_cleannames
## result: Nitrate is lowest AIC (not sig p value) - silicate within 2 AIC 
### when LOGGED: silicate and NN flip and NN within 2 aIC (both are sig)


### Varari GP 
MS_V_GP_nonlinear_fitresults_cleannames <- MS_V_GP_nonlinear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
MS_V_GP_nonlinear_fitresults_cleannames
## result: Nitrate is lowest AIC , ph and silicate within 2 AIC (no sig p vals)
### when LOGGED: silicate and NN flip and NN is just over 2 aIC (silicates is sig)


```


### Tidy df for the NEC measurements from different df 
```{r, echo=FALSE}

NEC_wnuts_V <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari", 
         P_R=="C") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  drop_na(Predictor_Values)

NEC_wnuts_C <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral", 
         P_R=="C") %>% 
  pivot_longer(cols = phosphate_umolL:Salinity, names_to = "Predictor_Variable", values_to = "Predictor_Values") %>% 
  mutate(Response_Variable=umol.cm2.hr) %>% 
  drop_na(umol.cm2.hr) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  drop_na(Predictor_Values)
```

### Make nonlinear models for NEC 
use new colony number as random factor - includes day automatically 
```{r, echo=FALSE}
## for Varari 
MS_V_NEC_linear <- NEC_wnuts_V %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
   mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models
MS_V_NEC_linear

MS_V_NEC_linear_fit <- MS_V_NEC_linear$fit # shows you each of the models

#MS_V_NEC_linear_fitresults <- MS_V_NEC_linear %>%
 # mutate(#coeff = map(fit, tidy),
    #     aic =  map(fit, glance)) %>% # R2 and others
 # select(Predictor_Variable, coeff, aic) %>% # only keep the results
 # unnest() %>%
 # write_csv(here::here("Outputs", "ModelSelection", "V_NEC.csv"))

MS_V_NEC_linear_fitresults_lmer <- MS_V_NEC_linear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "V_NEC.csv"))

## for Cabral 
MS_C_NEC_linear <- NEC_wnuts_C %>%
  nest(data = -c(Predictor_Variable)) %>% # nest all the data measurement type
   mutate(fit = map(data, ~lmer(Response_Variable~ poly(log(Predictor_Values+1), degree=2)  + (1|new_colonynumber), data = .))) #create models ### KEEP NEW COLONY AS RANDOM 
MS_C_NEC_linear

MS_C_NEC_linear_fit <- MS_C_NEC_linear$fit # shows you each of the models

MS_C_NEC_linear_fitresults <- MS_C_NEC_linear %>%
  mutate(coeff = map(fit, tidy),
         aic =  map(fit, glance)) %>% # R2 and others
  select(Predictor_Variable, coeff, aic) %>% # only keep the results
  unnest() %>%
  write_csv(here::here("Outputs", "ModelSelection", "C_NEC.csv"))

```

### Clean Names 
```{r}
###########################################################
### clean names and calculating delta AIC for params for each site and for NEC 
###########################################################

### Cabral NEC
MS_C_NEC_linear_fitresults_cleannames <- MS_C_NEC_linear_fitresults %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "salinity" = "Salinity", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
## result: pH is lowest AIC, with sig p-val - rest are more tan 2 AIC 
## WHEN LOGGED:  same result 
MS_C_NEC_linear_fitresults_cleannames

### Varari NEC
MS_V_NEC_linear_fitresults_cleannames <- MS_V_NEC_linear_fitresults_lmer %>%
  mutate(Predictor = dplyr::recode(Predictor_Variable,
                            "NN_umolL" = "Nitrite + Nitrate",
                            "phosphate_umolL" = "Phosphate",
                            "silicate_umolL" = "Silicate",
                            "ammonia_umolL" = "Ammonia", 
                            "salinity" = "Salinity", 
                            "new_pH" = "pH", 
                            "TA_initial" = "Initial TA")) %>%
  mutate(delAIC = AIC - min(AIC)) %>%
  arrange(delAIC)
## result: pH is lowest AIC but no sig p-value. Others are more than 2 AIC 
## WHEN LOGGED: Phopshate is lowest AIC (with sig p-val)
MS_V_NEC_linear_fitresults_cleannames
```



### Results: 

