---
title: "Initial Construction of DFs"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

## Loading libraries 

```{r, echo=FALSE}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(ggrepel)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(flextable)
library(performance)
library(agricolae)
library(ggeffects)
library(sjPlot)
library(patchwork)
library(broom)
library(purrr)
library(nlstools)
library(stringr)
library(emmeans)
library(MuMIn)
```


## Loading the data and creating dfs 
```{r}
RespoMeta <- read_csv(here("Data","RespoFiles","Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))
BioData <- read_csv(here("Data","RespoFiles","Fragment_MeasurementSampling_Cabral_Varari.csv"))
Sample_Info <- left_join(RespoMeta, BioData)
pHSlope <- read_csv(here("Data", "pHSlope.csv"))
RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
#full_calc_data <- read_csv(here("Data", "full_calc_data.csv"))
calc_data <- read_csv(here("Data", "Titrations", "Calc_TArates.csv"))


######### Respo table #############
RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 650-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date_block= factor(date)) #make the blank column a factor
```


## calculate NEC and save file --- this is checked and looks good as of May 28th, 2024 
```{r}
######### create new data frame of just the initial data, pull out initial data from sample_type
initial <- calc_data %>% 
  filter(Sample_Collection == "Initial") %>% #tells you all the rows that you have with initial
  select("date","temp_C", "salinity_insitu", "TA", "site", "new_colonynumber") 

######## remove and create new data frame with just blanks
blanks <- calc_data %>% 
  filter(Sample_Type == "Blank")

######### filter out just the post data 
calc_data_post <- calc_data %>% 
  filter(Sample_Collection == "Post")

names(initial)[3:4] <- paste0(names(initial)[3:4], "_initial") #use this to rename all of our columns

###### join blanks and carb chem data frame
calc_data1 <- left_join(calc_data_post, initial) #joining the initials to my data frame for carb chem
blanks1 <- left_join(blanks,initial)

###### figure out delta TA, initial-final
blanks_deltaTA <- blanks1 %>% 
  mutate(delta_TA_blank = TA_initial-TA)

####### getting the averages of blanks for each date and colony/treatment 
blanks_deltaTA_avg <- blanks_deltaTA %>% 
  select(site, date, SGD_number, delta_TA_blank) %>% 
  filter(delta_TA_blank!=0) %>% 
  group_by(date, site, SGD_number) %>% 
  summarise(mean_blanks=mean(delta_TA_blank))

calc_data_InitalPost_wblanks <- left_join(calc_data1, blanks_deltaTA_avg) #bring in mean blanks to calc_data
calc_data_InitalPost_wblanks <- calc_data_InitalPost_wblanks %>% 
  select(!c(pH_nonTris, salinity_insitu_initial))

######## need to join in SA,volume data and time data by fragment ID, before calculating NEC
sample_data <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) #bring in SA and volume data sheet

SA <- sample_data[, c("sample_ID", "SA_cm2", "volume_mL")] #pull out the necessary columns and treatment 

SA2 <- SA %>%
 dplyr::mutate(light_dark = str_extract(sample_ID, "[^_]+$")) #split the sample_ID at the underscore to delete the Dark values

######## steps to organize and delete D values
rows_Dark <- which(SA2$light_dark == "Dark") #tells you all the rows that you have with blanks
Dark <-SA2[rows_Dark,] 
SA3 <- SA2[-rows_Dark,] #to remove the rows with dark data, now have data sheet with only light, SA and volume values
SA3[,4] = NULL #had to delete the light-dark column to allow to just join by fragment.ID

calc_data_withSA <- left_join(calc_data_InitalPost_wblanks, SA)

######## bring in the time data from resp.data sheet --> RespoMeta

######### need to organize and first delete the dark information
rows_dark2 <- which(RespoMeta$light_dark == "DARK") #tells you all the rows that you have with blanks
dark2 <-RespoMeta[rows_dark2 ,] 
resp_data2 <- RespoMeta[-rows_dark2,]

####### pull out columns that we want to use for our bind to the calc.data2 sheet
time_data <- resp_data2 %>% 
  select(c("sample_ID","SGD_dil", "start_time", "stop_time", "site", "date", "light_dark"))

full_calc_data <- left_join(calc_data_withSA, time_data)

######### NOW calculate the NEC rate
full_calc_data2 <- full_calc_data %>% 
  mutate(deltaTA = (TA_initial - TA) - mean_blanks) %>%  ### subtracted blank data 
  mutate(timediff = as.numeric(stop_time - start_time))

########## make a row that has rate.type for "C" assigned to light 
full_calc_data2$P_R <-ifelse(full_calc_data2$light_dark=='LIGHT', "C")

########## equation to calculate NEC rates 
## time is in seconds 

full_calc_data3 <- full_calc_data2 %>% 
  filter(new_colonynumber!="BLANK")

full_calc_data_NEC <- full_calc_data3 %>% 
  mutate(deltaTA_2 = deltaTA/2, 
         deltaTA_L = deltaTA_2*1.025, 
         umol.cm2.s = deltaTA_L*(.650-(volume_mL/1000))/(SA_cm2*timediff), 
         umol.cm2.hr = umol.cm2.s*3600) %>% 
  select(!c(deltaTA_2,deltaTA_L,umol.cm2.s))

write_csv(full_calc_data_NEC , here("Data","full_calc_data_NECrates.csv"))  
```


### figure out pH data -- NOT BEIN USED AS OF MAY 2024 BECAUSE ALREADY FIGURED OUT ANOTHER WAY -- saved csv and read in 
```{r}

####################
### pH data #########
######################
pHcalib<-read_csv(here("Data","TrisCal_20230614.csv")) #%>% ## tris cal date is listed as a character here - make sure change in Excel file before reading in so it is a date 
pHcalib$TrisCalDate <- mdy(pHcalib$TrisCalDate)
pHcalib <- pHcalib[-c(13,14), ]

#View(pHcalib)

pHData <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) 
pHData$TrisCalDate <- mdy(pHData$TrisCalDate)
pHData <- pHData[-c(294,303,435),]
#pHData <- pHData[,-(14:17)]

#View(pHData) ### if re-running after a bit, either add in code for converting TrisCalDate to a date OR make sure it is a date in the file 

pHSlope<-pHcalib %>%
  #filter(HOBO_Orion =="Orion") %>% # extract only the orion data
  nest_by(TrisCalDate) %>%
  dplyr::mutate(fitpH = list(lm(mVTRis~Ttris, data = data))) %>% # linear regression of mV and temp of the tris
  dplyr::summarise(broom::tidy(fitpH)) %>% # make the output tidy
  select(TrisCalDate, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>% # put slope and intercept in their own column
  right_join(.,pHData) %>% # join with the pH sample data
  mutate(mVTRis = temp_C*Ttris + `(Intercept)`) %>% 
  drop_na(TrisCalDate) %>% 
  mutate(new_pH = pH(Ex=mV,Etris=mVTRis,S=salinity,T=temp_C)) 
# calculate pH of the samples using the pH seacarb function - GETTING AN ERRROR ON THIS LAST LINE ######

#### COME BACK AND CHECK LATER ##### ## seems fine as of Jan27th, 2024 
```


## Normalize to Blanks for regular R and GP and NP respo 
- things to consider here: try both ways 
- 1. average across all the days and get one point for each dilution 
- 2. keep it how it is - grouped by date_block (i think this is more correct)
```{r}
RespoR_Normalized_blankperday <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)


## two options: 1) summarise across all 4 days 2) direct comparison day to day 
## look at individual blank values to see if any of the days are particularly off - if everything looks consistent, can stick with individual days 
# take out date_block in group by and then change summarise function - to average all blanks by all dilutions 
# go back and check for blank volume to make sure full chamber vol 

### plot colonies against blanks ######
plot_Blank_Rates <- RespoR_Normalized_blankperday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~date_block, scales="free_y")

plot_Blank_Rates2 <- RespoR_Normalized_blankperday %>% 
  #filter(date_block!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark, scales="free_y")

plot_Blank_Rates2.5 <- RespoR_Normalized_blankperday %>% 
  filter(date_block!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark, scales="free_y")

plot_Blank_Rates3 <- RespoR_Normalized_blankperday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(date_block~light_dark, scales="free_y")


##### DELETE 6/13 FROM BLANK DATA FOR CABRAL 
RespoR_Normalized_blankperdaynoCabral <- RespoR_Normalized_blankperday %>% 
  filter(date_block!="6/13/23")

```

### Option 2 for Blanks - averaging  
```{r}

RespoR_Normalized_avgblanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)

### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- RespoR_Normalized_avgblanks %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

```

## Now combine into two dfs - one based on per day blank rates and the other based on averaged blank rates 
```{r}
#joining with per day blanks 
RespoR_Normalized_blankperday_joined <- RespoR_Normalized_blankperdaynoCabral %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         umol.cm2.hr_uncorr = (umol.sec*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr, umol.cm2.hr_uncorr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL)

#join with Tris pH data -- CAN IGNORE BC HAVE OTHER FILE WITH PH (MAY 2024) 
TrispH_RespoRNormalized_perdayBlanks <- RespoR_Normalized_blankperday_joined %>% 
  left_join(pHSlope)

```

### BASED ON WHAT BLANKS TO USE -  calculate R, GP, and NP 
- RIGHT NOW: using blanks per day
- with edits made to Cabral 

```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- RespoR_Normalized_blankperday_joined %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1,
         umol.cm2.hr_uncorr = umol.cm2.hr_uncorr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr),  # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") %>% # all dark run rates get R for respiration
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr)) ####### DELETE THIS ONCE FIGURE OUT WHAT CABRAL 11/12 

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- RespoR_Normalized_blankperday_joined %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr),  # for any values below 0, make 0
        umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr)) ####### DELETE THIS ONCE FIGURE OUT WHAT CABRAL 11/12 

# rejoin data into single df
RespoR_Normalized2 <- bind_rows(RespoR_Normalized_light, RespoR_Normalized_dark) %>% 
  drop_na(umol.cm2.hr) # removes C20 and C19 that were weird 


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(new_colonynumber, SGD_number, site, date) %>% ## EDITED FROM new_pH
  summarize(umol.cm2.hr = sum(umol.cm2.hr, na.rm=TRUE), 
            umol.cm2.hr_uncorr = sum(umol.cm2.hr_uncorr, na.rm=TRUE)) %>% # NP + R = GP
            #Temp.C = mean(Temp.C)) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(new_colonynumber, pH, sample_ID, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, umol.cm2.hr_uncorr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%
  bind_rows(RespoR_NormalizedGP) %>% ## EDITED FROM NEW PH 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr))
 # filter(new_colonynumber!=20)

####### NEED TO PHYSICALLY COPY THE DATA FROM NP OR R AND PASTE IT VIA MUTATE FOR GP 

## what is wrong with Cabral 20? 
#Cabral20 <- RespoR_Normalized_Full %>%
 #filter(site=="Cabral") %>%
 # ggplot(aes(x=SGD_number, 
 #            y=umol.cm2.hr)) + 
 # facet_wrap(~new_colonynumber, scales = "free_y") +
#  geom_point() +
 # geom_smooth(method = "lm", se = FALSE) +
 # scale_x_continuous(trans="log10") 
  #labs(title="Respiration Normalized to Blanks for SGD Dils per colony")


```

### join Respo rates with pH data and TA data and SAVE CSV  
```{r}

#RespoR_Normalized_Full2 <- RespoR_Normalized_Full %>% 
#  full_join(pHSlope, join_by(sample_ID, SGD_number)) ### keeps blanks included 

RespoR_Normalized_Full3 <- RespoR_Normalized_Full %>% 
  left_join(pHSlope, join_by(sample_ID, SGD_number)) ## successfully joined new_pH data

write_csv(RespoR_Normalized_Full3 , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv")) 
### save and then copy and paste nutrients + new_pH into GP rows - May 31st, 2024 


### try to add TA data also 
full_calc_dataNEC_editforjoin <- full_calc_data_NEC %>% 
  select(!c("sample_ID_edit":"Sample_Collection", "mean_blanks":"timediff")) %>% 
  filter(new_colonynumber!="BLANK",new_colonynumber!=19, new_colonynumber!=20) 
  
write_csv(full_calc_dataNEC_editforjoin, here::here("Data", "full_calc_dataNEC_editforjoin.csv"))


RespoR_Normalized_Full4 <- RespoR_Normalized_Full3 %>% 
  bind_rows(full_calc_dataNEC_editforjoin)


write_csv(RespoR_Normalized_Full4, here::here("Data", "RespoR_Normalized_Full4_withNEC!.csv"))




```

##### try to figure out how to get NEC data into same df with P_R and then also join with nutrients  

Note: May 31st -- NEC data STILL INCLUDES NEW COLONIES 19 and 20 (ie Cabral 11 and 12) -- but not included in Respo Data 
should I add back in ? Or no? 

```{r}
BioData2 <- BioData %>% 
  select(!c("weight_g":"spc", "mV":"mg_L", "pH_night", "TrisCalDate", "CobleA":"Diesel_Chen"))

NEC_wnuts <- full_calc_data_NEC %>% 
  left_join(BioData2)

NEC_wnuts_edit <- NEC_wnuts %>% 
  select(!c("salinity_insitu":"Sample_Collection", "TA_initial":"P_R"))


### add in new_pH and salinity and temp 

#############################
### first need to tidy the ph slope df to be able to join properly 
#############################

### get rid of Dark values first 
pHSlope_nodark <- pHSlope %>% 
 dplyr::mutate(light_dark = str_extract(sample_ID, "[^_]+$"))

rows_Dark <- which(pHSlope_nodark$light_dark == "Dark") #tells you all the rows that you have with blanks
Dark <-pHSlope_nodark[rows_Dark,] 
pHSlope_nodark <- pHSlope_nodark[-rows_Dark,]


##############################
## now join with NEC and save 
##############################


NEC_wnuts_edit_withpH <- NEC_wnuts_edit %>% 
  left_join(pHSlope_nodark)

write_csv(NEC_wnuts_edit_withpH, here("Data", "NEC_wnuts_edit.csv"))

#RespoR_Normalized_Full_ExcelUpdates_select <- RespoR_Normalized_Full_ExcelUpdates %>% 
 # select(new_colonynumber, SGD_number, site, salinity, date, P_R, umol.cm2.hr, phosphate_umolL:new_pH)
#
#full_calc_data_select <- full_calc_data %>% 
 # select(date, site, SGD_number, umol.cm2.hr, new_colonynumber) %>% 
 # mutate(P_R="NEC") %>% 
 # filter(new_colonynumber!="BLANK")

#### ^^ Why are there triplicates of each ?!?! 
### saved as own csv and re-did manually Excle to also add nutrient data 

#write_csv(full_calc_data_select , here("Data","NEC_ExcelAdded.csv")) 


```



