---
title: "June 17th: Plots based on Model Selection for Environmental Parameters in SGD "
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

### Loading libraries 
```{r, echo=FALSE}
library(LoLinR)
library(lubridate)
library(patchwork)
library(tidyverse)
library(here)
library(car)
library(GGally)
library(corrplot)
library(ggcorrplot)
library(corrr)
library(PNWColors)
library(seacarb)
library(broom)
library(agricolae)
library(lme4)
library(ggsci)
library(see)
library(cowplot)
library(lmerTest)
library(modelsummary)
library(performance)
library(emmeans)
library(MuMIn)
library(broom.mixed)
library(kableExtra)
library(reshape2)
theme_set(theme_classic()) ### This sets the default ggplot theme
library(Hmisc)
```

### Loading Data
```{r, echo=FALSE}
RespoR_Normalized_Full_withNEC_nutrients <- read_csv(here::here("Data", "RespoR_Normalized_Full_withNEC_andallnutrients.csv"))
ActualvsPredicted_Nutrients <- read_csv(here::here("Data", "ActualvsPredicted_Values.csv"))
RawGWData <- read_csv(here::here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari2.csv")) 

MooreaMarch_full <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/March2022/Allbiogeochemdata_QC_march_fdom2.csv")
MooreaAugust <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/August2021/Nutrients/Nutrients_Watersampling_Aug21.csv")
MooreaAugust2 <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/August2021/Allbiogeochemdata_QC2.csv")

```

### Plots for Gross Photosynthesis - Cabral: 
-  Cabral is significant for silicate at linear (0.04) and nonlinear (0.02)
-  Cabral is only significant for SGD Dils in the nonlinear model (0.02)
-  With removing an outlier point in the last dilution, Cabral is significant for GP both linear (0.015) and nonlinear (0.015)

```{r}
# mutate(ammonia_umolL = ifelse(ammonia_umolL = "<0.02", 0.01, ammonia_umolL)) %>% 

###################
## Silicate
####################

### confirm linear model 
GP_Cabral_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_silicate_linearmodel)


### confirm nonlinear model 
GP_Cabral_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(silicate_umolL+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
 # filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_silicate_nonlinearmodel)

#### both are significant so can add either trend line 

GP_Cabral_Silicate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 geom_smooth(method="lm", formula = "y~log(x)", color="black") +
 # geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log silicate",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP Rates for Cabral with Silicate") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_Cabral_Silicate

###################
## SGD dils
####################

### confirm a linear model 
GP_Cabral_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_SGD_linearmodel)


### confirm a nonlinear model 
GP_Cabral_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_SGD_nonlinearmodel)


GP_Cabral_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP Rates for Cabral with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_Cabral_SGDDils

###################
## SGD dils WITHOUT POTENTIAL OUTLIERS
####################
GP_Cabral_SGDDils_nooutlier <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(sample_ID!= "Cabral_Col6_Dil9_Light") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
 scale_color_manual(values=pnw_palette("Bay", n=9)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  #geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
  geom_smooth(method="lm", formula = "y~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP Rates for Cabral with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_Cabral_SGDDils_nooutlier

### confirm a linear model 
GP_Cabral_SGD_linearmodel_nooutlier <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(sample_ID!= "Cabral_Col6_Dil9_Light") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_SGD_linearmodel_nooutlier)


### confirm a nonlinear model 
GP_Cabral_SGD_nonlinearmodel_nooutlier <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  filter(sample_ID!= "Cabral_Col6_Dil9_Light") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Cabral_SGD_nonlinearmodel_nooutlier)

```

### Plots for Gross Photosynthesis - Varari 
-  Varari is ONLY significant for silicate in nonlinear model (0.02)
-  Varari has no significant relationship with SGD and GP 

```{r}
###################
## Silicate
####################

### confirm linear model 
GP_Varari_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>%
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Varari_silicate_linearmodel)


### confirm nonlinear model 
GP_Varari_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(silicate_umolL+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Varari_silicate_nonlinearmodel)

#### ONLY significant in nonlinear model 

GP_Varari_Silicate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 # geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log silicate",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP Rates for Varari with Silicate") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_Varari_Silicate

###################
## SGD dils
####################

### confirm a linear model 
GP_Varari_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Varari_SGD_linearmodel)


### confirm a nonlinear model 
GP_Varari_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Varari_SGD_nonlinearmodel)


GP_Varari_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
#  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP Rates for Varari with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_Varari_SGDDils
```

### Plots for Respiration - Cabral: 
-  There is no significance at Cabral for any environmental parameter or broad SGD dilutions

```{r}
###################
## SGD dils
####################

### confirm a linear model 
R_Cabral_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(R_Cabral_SGD_linearmodel)


### confirm a nonlinear model 
R_Cabral_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(R_Cabral_SGD_nonlinearmodel)


R_Cabral_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 # geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "R Rates for Cabral with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
R_Cabral_SGDDils

```

### Plots for Respiration - Varari 
-  There is no significance at Varari for any environmental parameter or broad SGD dilutions 

```{r}

###################
## SGD dils
####################

### confirm a linear model 
R_Varari_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(R_Varari_SGD_linearmodel)


### confirm a nonlinear model 
R_Varari_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(R_Varari_SGD_nonlinearmodel)


R_Varari_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
#  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "R Rates for Varari with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
R_Varari_SGDDils
```

### Plots for Calcification - Cabral: 
-  Cabral was allegedly significant for temperature (0.01) and pH (0.01) with a nonlinear relationship  - but not seeing that here for temp, only for pH 
-  Cabral is NOT significant for SGD Dils 

```{r}
###################
## pH
####################

### confirm nonlinear model 
C_Cabral_pH_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(new_pH+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Cabral_pH_nonlinearmodel)

C_Cabral_pH <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=new_pH, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
# geom_smooth(method="lm", formula = "y~log(x)", color="black") +
 geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log pH",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "C Rates for Cabral with pH") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Cabral_pH

###################
## SGD dils
####################

### confirm a linear model 
C_Cabral_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Cabral_SGD_linearmodel)


### confirm a nonlinear model 
C_Cabral_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Cabral_SGD_nonlinearmodel)


C_Cabral_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  #geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "C Rates for Cabral with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Cabral_SGDDils

```

### Plots for Calcification - Varari 
-  Varari has a significant linear and nonlinear relationship with phosphate (<0.0001) and (0.0002) and TA (0.001) 
-  Varari has a significant ... relationship with SGD 

```{r}
###################
## Phosphate
####################

### confirm nonlinear model 
C_Varari_phosphate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(phosphate_umolL+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
    filter(phosphate_umolL<1) %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_phosphate_nonlinearmodel)


C_Varari_Phosphate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
   filter(phosphate_umolL<1) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=phosphate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 # geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "log phosphate",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "C Rates for Varari with Phosphate") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Varari_Phosphate

###################
## TA 
####################

### confirm a nonlinear model 
C_Varari_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(TA_initial+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
    filter(TA_initial<2550) %>% #### IF CHOOSE TO REMOVE HIGH POINTS, ONLY SIGNIFICANT IN NONLINEAR (otherwise significant in linear too)
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_SGD_nonlinearmodel)


C_Varari_TA <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  # filter(TA_initial<2550) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=TA_initial+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
  geom_hline(yintercept = 0) +
  labs(x = "log TA",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "C Rates for Varari with TA (Minus the potential outliers)") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Varari_TA


###################
## Silicate 
####################

### nonlinear model 
C_Varari_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(silicate_umolL+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_SGD_nonlinearmodel)

## not poly 
C_Varari_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL+1)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_silicate_linearmodel)


C_Varari_silicate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  # filter(TA_initial<2550) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
 geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_hline(yintercept = 0) +
  labs(x = "log Silicate",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "C Rates for Varari with Silicate") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Varari_silicate


###################
## SGD dils
####################

### confirm a linear model 
C_Varari_SGD_linearmodel <- lmer(umol.cm2.hr ~ log(SGD_number+1) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>%
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_SGD_linearmodel)


### confirm a nonlinear model 
C_Varari_SGD_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(SGD_number+1),2) + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>%
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(C_Varari_SGD_nonlinearmodel)


C_Varari_SGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=9), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_hline(yintercept = 0) +
  labs(x = "log SGD Dils",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "NEC Rates for Varari with SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_Varari_SGDDils
```

### Plot nutrient levels with SGD dils to see how different the nutrients actually are across the dilutions 

```{r, echo=FALSE}

#######################
### NN
#######################
Nitrate_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=NN_umolL)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
  geom_smooth(method="lm", formula="y~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "NN",
       title = "NN levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Nitrate_Levels_per_SGDDil

#######################
### Phosphate
#######################

Phosphate_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(phosphate_umolL<1) %>% 
  ggplot(aes(x=SGD_number+1, 
             y=phosphate_umolL)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "Phosphate",
       title = "Phosphate levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Phosphate_Levels_per_SGDDil


#######################
### Silicate
#######################

Silicate_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=silicate_umolL)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "Silicate",
       title = "Silicate levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Silicate_Levels_per_SGDDil

#######################
### Ammonia
#######################

Ammonia_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=ammonia_umolL)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "Ammonia",
       title = "Ammonia levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Ammonia_Levels_per_SGDDil

#######################
### Salinity
#######################

Salinity_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=salinity)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "Salinity",
       title = "Salinity levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Salinity_Levels_per_SGDDil

#######################
### pH
#######################

pH_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=new_pH)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "pH",
       title = "pH levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
pH_Levels_per_SGDDil

#######################
### temp
#######################

temp_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=temp_C)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "temp",
       title = "temp levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
temp_Levels_per_SGDDil

#######################
### TA
#######################

TA_Levels_per_SGDDil <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  ggplot(aes(x=SGD_number+1, 
             y=TA_initial)) + 
  geom_point(size=4, aes(color=as.factor(new_colonynumber))) +
  scale_color_manual(values=pnw_palette("Bay", n=14)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  facet_wrap(~site, scales = "free_y") +
 geom_smooth(method="lm", formula="(y)~log(x)", color="black") +
 # geom_hline(yintercept = 0) +
  labs(x = "SGD Dils",
       y = "TA",
       title = "TA levels per SGD Dils") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
TA_Levels_per_SGDDil
```

### Plot how many corals are net calcifying vs net dissolving  

```{r}
### should make a stacked bar plot with all corals in one group of dilution - % of which of those are positive or negative 

###################################
## attempt 2 
###################################
RespoR_Normalized_Full_withNEC_nutrients_calcifplot <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>%
  select(!c("phosphate_umolL":"TA_initial", "salinity", "date")) %>%
  mutate(rate_category = ifelse(umol.cm2.hr > 0, "positive", "negative")) %>% 
  group_by(SGD_number, site) %>% 
  summarize(positive_count = sum(rate_category == "positive"),
            negative_count = sum(rate_category == "negative"))

RespoR_Normalized_Full_withNEC_nutrients_calcifplot2 <- RespoR_Normalized_Full_withNEC_nutrients_calcifplot %>% 
  pivot_longer(cols = c(positive_count, negative_count),
               names_to = "rate_category",
               values_to = "count") %>% 
  mutate(total_count = sum(count),
         proportion = count / total_count)

## plot 
Net_CalcvsDissolution2 <- RespoR_Normalized_Full_withNEC_nutrients_calcifplot2 %>% 
  ggplot(aes(x=as.factor(SGD_number), 
             y=proportion,
             fill=rate_category)) +
  geom_bar(stat = "identity", position = "fill", width=0.4) +
  #scale_fill_manual(values =  ifelse (umol.cm2.hr > 0, "red", "black")) +
  scale_fill_manual(values=c("red", "black"), 
                    labels = c("positive_count" = "Net Calcifying", "negative_count" = "Net Dissolving")) +
  theme_bw() + 
 # coord_trans(x="log") +
 # geom_hline(yintercept = 0) +
  facet_wrap(~site) +
 #coord_trans(x ="log") +
  labs(x = "% SGD by Volume",
       y = "Proportion of Corals",
      # title = "Net Calcifying vs Net Dissolving Corals per SGD Dilution", 
       fill = "Calcification State") +
   theme(axis.text.x=element_text(size=14), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
Net_CalcvsDissolution2
ggsave(here::here("Outputs", "Results", "Final", "NetCalcifying_NetDissolving.jpg"), 
       width = 10, height=7)

########################
## statistics 
#######################
CalcVsDissol <- lm(proportion ~ SGD_number*site, data = RespoR_Normalized_Full_withNEC_nutrients_calcifplot2)

anova(CalcVsDissol)

##############################################
## look at raw data to see why dissolving is occurring at 0.01 
##############################################
RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="0.01") ### looks like it is only 3 colonies, 1 at Cabral (Col 5, but barely at -0.02), and 2 at Varari (Col 3 and 8)

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="0.03") ### only the same 2 colonies at Varari (Col 3 and 8)

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="0.05") ### only Varari Col 3 

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="0.1") ### only Varari Col 3 

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="0.5") ### Varari Col 3 and barely Col 8 (0.02)

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="1")  ### Varari Col 1 and barely Col 3

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="2")  ### one colony at Cabral (Col 10), Varari Col 3 and Col 8

RespoR_Normalized_Full_withNEC_nutrients_rawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C", 
         SGD_number=="4")  ### one colony at Cabral (Col 8), Varari Cols 2,3 and 4

###################################
## check GP rates of Varari Colony 3  
###################################
RespoR_Normalized_Full_withNEC_nutrients_GPrawdata <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="GP", 
         new_colonynumber=="3"| new_colonynumber=="2")

RespoR_Normalized_Full_withNEC_nutrientsVGPonly <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="GP", 
         site=="Varari") %>% 
   filter(!is.infinite(umol.cm2.hr))

max(RespoR_Normalized_Full_withNEC_nutrientsVGPonly$umol.cm2.hr)
min(RespoR_Normalized_Full_withNEC_nutrientsVGPonly$umol.cm2.hr)


###################################
## attempt 1 
###################################

Net_CalcvsDissolution <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  mutate(SGD_number = as.character(SGD_number), 
         rate_category = ifelse(umol.cm2.hr > 0, "positive", "negative")) %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr,
             fill=rate_category)) + 
  geom_col(width = 0.8,  colour = NA) + 
  #scale_fill_manual(values =  ifelse (umol.cm2.hr > 0, "red", "black")) +
  scale_fill_manual(values=c(positive='black',negative='red')) +
  theme_bw() + 
  geom_hline(yintercept = 0) +
  facet_wrap(~site) +
 #coord_trans(x ="log") +
  labs(x = "SGD values",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcifying vs Net Dissolving Corals per SGD Dilution") +
   theme(axis.text.x=element_text(size=14), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
Net_CalcvsDissolution

```

### Plot GP:R as a function of SGD 
-  Cabral is significant (0.025) but Varari is not 
```{r}
## First make new df
GP_RRatio_bySGDDils <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  dplyr::select(!"sample_ID") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  group_by(P_R, SGD_number, date, site, new_colonynumber) %>% 
  filter(P_R!="C", P_R!="NP") %>% 
  #summarize(GP_R = GP/R)
  pivot_wider(names_from = P_R, values_from = umol.cm2.hr) %>% 
  mutate(GP_R = GP/R) 

### plots 
GP_R_bySGD_bothsites <- GP_RRatio_bySGDDils %>% 
  #filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber)) %>% 
  ggplot(aes(x=(SGD_number+1), 
             y=GP_R)) + 
  geom_point(size=3, aes(color=new_colonynumber)) +
  theme_bw() + 
  coord_trans(x="log") +
  facet_wrap(~site, scales = "free_y") +
  geom_smooth(method="lm", formula = "y~log(x)") +
  labs(x = "SGD Dilutions",
       y = "Gross Photosynthesis/Respiration Rates",
       title = "SGD by GP:R Relationship for Varari") +
   theme(axis.text.x=element_text(size=12), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_R_bySGD_bothsites

## model testing 
model_GP_R_SGD_Varari <- lmer(GP_R ~ log(SGD_number+1) + (1|new_colonynumber), data = GP_RRatio_bySGDDils %>%
                                        filter(site=="Varari"))
anova(model_GP_R_SGD_Varari)

model_GP_R_SGD_Cabral <- lmer(GP_R ~ log(SGD_number+1) + (1|new_colonynumber), data = GP_RRatio_bySGDDils %>%
                                        filter(site=="Cabral"))
anova(model_GP_R_SGD_Cabral)

```

### Make correlation matrix for nutrients 

```{r}
## data 
corr_matrix_envparams <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="R") %>% 
  mutate(Salinity=salinity) %>% 
  select(!c("salinity", "umol.cm2.hr", "SGD_number", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL")) ## removed ammonia for rn because have less than values and causing NAs

##visualize it 
ggcorr(corr_matrix_envparams, method = c("everything", "pearson")) 

###############################
### Dani B's methods #######
cor_mat <- round(cor(corr_matrix_envparams),4)
head(cor_mat)

#melt the correlation matrix means it reassembles data frame to be more effective to complete corr matrix
#to long format
melted_cormat <- melt(cor_mat)
head(melted_cormat)

#visulaize the correlation matrix in general
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower and upper triangle of the correlation matrix
#Note that, a correlation matrix has redundant information. We’ll use the functions below to set half of it to NA
get_lower_tri<-function(cor_mat){
  cormat[upper.tri(cor_mat)] <- NA
  return(cor_mat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cor_mat){
  cor_mat[lower.tri(cor_mat)]<- NA
  return(cor_mat)
}

#apply upper tri calculation to graphc
upper_tri <- get_upper_tri(cor_mat)
upper_tri

#melt the correlation matrix
#melt the correlation data and drop the rows with NA values 
melted_cormat <- melt(upper_tri, na.rm = TRUE)

#heatmap of correlation matrix
#negative correlations are in purple color and positive correlations in red
#scale_fill_gradient2 is used with the argument limit = c(-1,1) as correlation coefficients range from -1 to 1
#coord_fixed() : this function ensures that one unit on the x-axis is the same length as one unit on the y-axis
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "midnightblue", high = "firebrick4", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()

melted_cormat <- melted_cormat %>% mutate_at(vars(starts_with("value")), funs(round(., 2)))

# Create a ggheatmap with basic characteristics, etc. 
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "firebrick3", mid = "white", high = "dodgerblue3", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()


# Print the heatmap
print(ggheatmap)

#add correlation coefficients to the heatmap
#geom_text() to add the correlation coefficients on the graph
#guides() to change the position of the legend title
#if else statement in melted data frame to quotes of black and white to adjust text color 
corr_matrix_SGD_params <- ggheatmap + 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 6) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18, face="bold", color="black"),
        axis.text.y = element_text(size = 18, face="bold", color="black"),
        panel.grid.major = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        legend.justification = c(0.8, 0),
        legend.title = element_text(size = 18, face="bold", color="black"),
        legend.text = element_text(size = 20, face="bold", color="black"),
        legend.position = c(0.48, 0.75),
        legend.direction = "horizontal") +
  guides(fill = guide_colorbar(barwidth = 12, barheight = 2, 
                               title.position = "top", title.hjust = 0.5, title.vjust = 1.0))

corr_matrix_SGD_params

```

### Results of back calculating 
Essentially found that the predicted values were too low to be useful for 

# NEW UPDATES FROM JUNE 19TH MEETING WITH NYSSA: 
Three main figures for publication will include: 

-  Figure 1: Experimental Design, showing methods and set up 

-  Figure 2: Correlation matrix (or PCA) by site to show the relationships of different parameters. Could be paired with a basic bar plot of end-member concentrations 

-  Figure 3: 3 part figure including a plot for GP, R, and NEC with log(silicate) on the x axis and rates on the y axis, colored by site and only including geom_smooth line for NEC. GP can include a dashed line because Cabral was significant but Varari was not. 

-  Exploratory figures: Net calcifying vs net dissolving, GP:C (potentially for index)


### Figure 1: Conceptual 



### Figure 2: ReVamp'd (correlation matrix)
- this has all but the significant correlations for each site as blank 
```{r}
###################################
## Varari 
###################################

## data 
corr_matrix_Varari <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(N_P = NN_umolL/phosphate_umolL) %>% 
  filter(P_R=="R") %>% 
  mutate("Salinity"=salinity, 
         "TA" = TA_initial, 
         "pH" = new_pH, 
         "N+N" = NN_umolL, 
         "Phosphate" = phosphate_umolL,
         "Silicate" = silicate_umolL) %>% 
         #"N+N:P" = N_P) %>% 
  filter(site=="Varari") %>% 
  select(!c("salinity", "silicate_umolL", "TA_initial", "new_pH", "N_P", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL")) 

# Compute a correlation matrix
corr_Varari <- round(cor(corr_matrix_Varari, 
                         method="spearman"), 1)

# Compute a matrix of correlation p-values
p.mat_Varari <- cor_pmat(corr_Varari)

# Visualize the correlation matrix
ggcorrplot(corr_Varari, method = "circle")

# Reordering the correlation matrix using hierarchical clustering
ggcorrplot(corr_Varari, hc.order = TRUE, outline.col = "white", method = "circle")

# Types of correlogram layout - Get the lower triangle
ggcorrplot(corr_Varari, hc.order = TRUE, type = "lower", outline.col = "white", method = "circle")

# Change colors and theme
# Argument colors
Varari_corr_matrix_plot <- ggcorrplot(corr_Varari, 
                                      hc.order = TRUE, ## reordering the correlation matrix with hierarchial clustering
                                      type = "lower", ## correlogram layout - for the lower triangle
                                      outline.col = "white",
                                      # method = "circle", ## determines the shape
                                      ggtheme = ggplot2::theme_classic, ## changes the theme 
                                      colors = c("steelblue3", "white", "tomato3"), ## determines color scheme
                                      sig.level = 0.05, ## default p-value
                                      lab = TRUE, ## adds correlation coefficient
                                      p.mat = p.mat_Varari, ## adds significance
                                    #  insig = "blank", ## makes insig values blank
                                      title = "Pearson Correlation Matrix for Environmental Parameters at Varari",
                                      legend.title = "Correlation", 
                                      tl.srt = 45, ## slant of x axis 
                                      tl.cex = 15, ## size of text axes  
                                      lab_size = 5)  + 
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"), 
        legend.title = element_text(size = 10, face="bold"),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black"))

Varari_corr_matrix_plot
ggsave(here::here("Outputs", "Results", "REDO_VarariCorrelation.jpg"), 
       width=10, height=7)


###################################
## Cabral 
###################################

## data 
corr_matrix_Cabral <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(N_P = NN_umolL/phosphate_umolL) %>% 
  filter(P_R=="R") %>% 
  mutate("Salinity"=salinity, 
         "TA" = TA_initial, 
         "pH" = new_pH, 
         "N+N" = NN_umolL, 
         "Phosphate" = phosphate_umolL,
         "Silicate" = silicate_umolL) %>%  
        # "N:P" = N_P) %>% 
  filter(site=="Cabral") %>% 
  select(!c("salinity", "silicate_umolL", "TA_initial", "new_pH", "N_P", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL")) 

# Compute a correlation matrix
corr_Cabral <- round(cor(corr_matrix_Cabral, 
                         method="spearman"), 1)


# Compute a matrix of correlation p-values
p.mat_Cabral <- cor_pmat(corr_Cabral)

# Visualize the correlation matrix
ggcorrplot(corr_Cabral, method = "circle")

# Change colors and theme
# Argument colors
Cabral_corr_matrix_plot <- ggcorrplot(corr_Cabral, 
                                      hc.order = TRUE, ## reordering the correlation matrix with hierarchial clustering
                                      type = "lower", ## correlogram layout - for the lower triangle
                                      outline.col = "white",
                                      # method = "circle", ## determines the shape
                                      ggtheme = ggplot2::theme_classic, ## changes the theme 
                                      colors = c("steelblue3", "white", "tomato3"), ## determines color scheme
                                      #sig.level = 0.05, ## default p-value
                                      lab = TRUE, ## adds correlation coefficient
                                      p.mat = p.mat_Cabral, ## adds significance
                                    #  insig = "blank", ## makes insig values blank
                                      title = "Pearson Correlation Matrix for Environmental Parameters at Cabral",
                                      legend.title = "Correlation", 
                                      tl.srt = 45, ## slant of x axis 
                                      tl.cex = 15, ## size of text axes  
                                      lab_size = 5)  + 
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"), 
        legend.title = element_text(size = 10, face="bold"),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black")) + 
  labs(x="Location", 
       y = expression(Phosphate~(mu*mol~L^-1))) 

Cabral_corr_matrix_plot
ggsave(here::here("Outputs", "Results", "REDO_CabralCorrelation.jpg"), 
       width=10, height=7)
```

### Figure 2: ReVamp'd 
- this is revamped but still includes all the squares more interpreation 
```{r}
 ###################################
## Varari 
###################################

## data from above 

# Compute a correlation matrix
corr_Varari2 <- round(cor(corr_matrix_Varari), 1)

# Compute a matrix of correlation p-values
p.mat_Varari2 <- cor_pmat(corr_Varari2)

# Specify the desired order of parameters
#param_orderV <- c("Salinity", "TA", "pH", "N+N", "Phosphate", "Silicate") # Replace with your actual parameter names

# Reorder the correlation matrix
#corr_Varari <- corr_Varari[param_orderV, param_orderV]

# Visualize the correlation matrix
ggcorrplot(corr_Varari, method = "circle")


Varari_corr_matrix_plot2 <- ggcorrplot(corr_Varari, 
                                     # hc.order = TRUE, ## reordering the correlation matrix with hierarchial clustering
                                      type = "lower", ## correlogram layout - for the lower triangle
                                      outline.col = "white",
                                      # method = "circle", ## determines the shape
                                      ggtheme = ggplot2::theme_classic, ## changes the theme 
                                      colors = c("steelblue3", "white", "tomato3"), ## determines color scheme
                                      #sig.level = 0.05, ## default p-value
                                      lab = TRUE, ## adds correlation coefficient
                                     #p.mat = p.mat_Varari, ## puts an X on the insignificant ones 
                                    #  insig = "pch", ## makes insig values blank
                                     #insig = label_sig, 
                                  #    title = "Pearson Correlation Matrix for Environmental Parameters at Varari",
                                      legend.title = "Correlation", 
                                      tl.srt = 45, ## slant of x axis 
                                      tl.cex = 15, ## size of text axes  
                                      lab_size = 5) +
  #labs(y="Varari") +
  theme(legend.title = element_text(size = 10, face="bold"),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black"))

Varari_corr_matrix_plot2
ggsave(here::here("Outputs", "Results", "REDO_VarariCorrelation_extended.jpg"), 
       width=10, height=7)


###################################
## Cabral 
###################################

# Compute a correlation matrix
corr_Cabral2 <- round(cor(corr_matrix_Cabral), 1)

# Compute a matrix of correlation p-values
p.mat_Cabral2 <- cor_pmat(corr_Cabral2)

# convert to long format so can add asterisk 
#cor_long_Cabral <- melt(corr_Cabral2)
#p_long_Cabral <- melt(p.mat_Cabral2)

# Mark significant correlations with asterisks
#cor_long_Cabral$signif <- ifelse(p_long_Cabral$value < 0.05, "bold", "plain")

# Specify the desired order of parameters
param_orderC <- c("Salinity", "TA", "pH", "N+N", "Phosphate", "Silicate") # Replace with your actual parameter names

# Reorder the correlation matrix
corr_Cabral2 <- corr_Cabral2[param_orderC, param_orderC]

ggcorrplot(corr_Cabral2, method = "circle")


# Change colors and theme
# Argument colors
Cabral_corr_matrix_plot2 <- ggcorrplot(corr_Cabral2, 
                                     # hc.order = TRUE, ## reordering the correlation matrix with hierarchial clustering
                                      type = "lower", ## correlogram layout - for the lower triangle
                                      outline.col = "white",
                                      # method = "circle", ## determines the shape
                                      ggtheme = ggplot2::theme_classic, ## changes the theme 
                                      colors = c("steelblue3", "white", "tomato3"), ## determines color scheme
                                      #sig.level = 0.05, ## default p-value
                                      lab = TRUE, ## adds correlation coefficient
                                     # p.mat = p.mat_Cabral2, ## adds significance
                                      #insig = "blank", ## makes insig values blank
                                     # title = "Pearson Correlation Matrix for Environmental Parameters at Cabral",
                                      legend.title = "Correlation", 
                                      tl.srt = 45, ## slant of x axis 
                                      tl.cex = 15, ## size of text axes  
                                      lab_size = 5)  + 
  theme(plot.title = element_text(hjust = 0.5, size=15, face="bold"), 
        legend.title = element_text(size = 10, face="bold"),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black")) #+ 
  #geom_text(data = cor_long_Cabral, aes(x = Var1, y = Var2, label = signif), color = "black", size = 5, inherit.aes = FALSE)


Cabral_corr_matrix_plot2
ggsave(here::here("Outputs", "Results", "REDO_CabralCorrelation_extended.jpg"), 
       width=10, height=7)


########################### 
## patch together 
###########################

#### remove x-axis labels 
p_Ccorr <- Cabral_corr_matrix_plot2 
p_Vcorr <- Varari_corr_matrix_plot2 
 
combined_corr_plot <- p_Ccorr/p_Vcorr + plot_layout(guides = 'collect')

combined_corr_plot + 
  plot_annotation(tag_levels = 'A') &
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"), 
        plot.tag = element_text(size = 18, face = "bold"))

ggsave(here::here("Outputs", "Results", "Final", "CorrMatrices.jpg"), 
       width=12, height=15)
```

### Figure 2a: RE Vamp'd (barplots)
- making bar graphs to illustrate differences between sites and from sites to offshore ambient SW 
```{r}
###########################################################
### making bar graphs to illustrate differences ### 
##########################################################
 
#### SEE BACKGROUND SITE DATA SCRIPT FOR HOW OFFSHORE VALUES WERE CALCULATED ####

############################## 
### plots for CSUNposium 
###############################
sitecomparison_maxdata <- tribble(~Site, ~Parameter, ~Value, 
        "Varari", "pH", "7.73", 
        "Cabral", "pH", "6.89", 
        "Reef Crest", "pH", "7.9", 
        "Varari", "Nitrates + Nitrites (umol/L)", "42.49", 
        "Cabral", "Nitrates + Nitrites (umol/L)", "8.22", 
        "Reef Crest", "Nitrates + Nitrites (umol/L)", "0.58", 
        "Varari", "TA (umol/kg-1)", "5393.3", 
        "Cabral", "TA (umol/kg-1)", "1755.18", 
        "Reef Crest", "TA (umol/kg-1)", "2386.84", 
        "Varari", "Phosphate (umol/L)", "2.5", 
        "Cabral", "Phosphate (umol/L)", "3.61", 
        "Reef Crest", "Phosphate (umol/L)", "0.20", 
        "Varari", "Silicate (umol/L)", "725.61", 
        "Cabral", "Silicate (umol/L)", "855.01", 
        "Reef Crest", "Silicate (umol/L)", "3.68", 
        "Varari", "Salinity (psu)", "6.32", 
        "Cabral", "Salinity (psu)", "5.79", 
        "Reef Crest", "Salinity (psu)", "36.7") %>% 
  mutate(Site= as.factor(Site))

### for pH 
SiteComparisons_pH <- sitecomparison_maxdata %>% 
  filter(Parameter=="pH") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(x="Location", 
       y = expression(pH[T])) +
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_pH
ggsave(here::here("Outputs", "Results", "SitevOffshore", "pH.jpg"))

## for TA 
SiteComparisons_TA <- sitecomparison_maxdata %>% 
  filter(Parameter=="TA (umol/kg-1)")  %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(x="Location",
       y = expression(TA~(mu*mol~kg^-1))) +
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_TA
ggsave(here::here("Outputs", "Results", "SitevOffshore", "TA.jpg"))

## Salinity 
SiteComparisons_Salinity <- sitecomparison_maxdata %>% 
  filter(Parameter=="Salinity (psu)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_y_discrete(limits = c("5.79", "6.32", "36.7")) +
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(x="Location", 
       y = "Salinity (psu)") +
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Salinity
ggsave(here::here("Outputs", "Results", "SitevOffshore", "Salinity.jpg"))

## for Phosphates 
SiteComparisons_Phosphate <- sitecomparison_maxdata %>% 
  filter(Parameter=="Phosphate (umol/L)")  %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(x="Location", 
       y = expression(Phosphate~(mu*mol~L^-1))) +
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Phosphate
ggsave(here::here("Outputs", "Results", "SitevOffshore", "Phosphate.jpg"))

## for Silicate 
SiteComparisons_Silicate <- sitecomparison_maxdata %>% 
  filter(Parameter=="Silicate (umol/L)")  %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(x="Location", 
       y = expression(Silicate~(mu*mol~L^-1))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Silicate
ggsave(here::here("Outputs", "Results", "SitevOffshore", "Silicate.jpg"))

  
## nitrates 
SiteComparisons_Nitrates <- sitecomparison_maxdata %>% 
  filter(Parameter=="Nitrates + Nitrites (umol/L)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Reef Crest", "Cabral", "Varari")) + 
  scale_y_discrete(limits = c("0.58", "8.22", "42.49")) +
  scale_fill_manual(values=c("deepskyblue3", "burlywood3", "coral4"), 
                    limits=c("Reef Crest", "Cabral", "Varari"), 
                    guide="none") +
  theme_classic() + 
  labs(y = expression(Nitrate+Nitrite~(mu*mol~L^-1))) +
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Nitrates
ggsave(here::here("Outputs", "Results", "SitevOffshore", "NN.jpg"))


### patch them all together 
p1.1 <- SiteComparisons_Nitrates + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
p1.2 <- SiteComparisons_Phosphate + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
p1.3 <- SiteComparisons_Silicate + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
p1.4 <- SiteComparisons_Salinity + theme(axis.title.x = element_blank()) 
p1.5<- SiteComparisons_TA + theme(axis.title.x = element_blank()) 
p1.6 <- SiteComparisons_pH + theme(axis.title.x = element_blank()) 

combined_endmemberSW_plot <- (p1.1 + p1.2 + p1.3) / (p1.4 + p1.5 + p1.6) +
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 24, face = "bold"))

combined_endmemberSW_plot

ggsave(here::here("Outputs", "Results", "Final", "rawGW_barplots.jpg"), 
       width=20, height = 12)



#plot.margin = unit(c(1, 1, 1, 1), "cm"), 

```

### Figure 3:

```{r}
### Respiration 
R_silicate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
#  geom_smooth(method="lm", formula = "y~poly(log(x),2)", color="black") +
  labs(y = expression(Respiration~Rate~(mu*mol~O[2]~cm^-2~hr^-1)),
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=15, face="bold"),
        axis.title.y=element_text(size=15, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
R_silicate
ggsave(here::here("Outputs", "Results", "R_silicate.jpg"), 
       width=10, height=7)

### R model 
R_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
                                            filter(P_R=="R") %>% 
                                            filter(!is.infinite(umol.cm2.hr)))

anova(R_bothsites_silicate_linearmodel)
r.squaredGLMM(R_bothsites_silicate_linearmodel)

###############################
## Gross Photosynthesis 
###############################
GP_silicate <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
 scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "GP", site == "Varari", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "firebrick4", linetype = "dashed") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "GP", site == "Cabral", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "darkgoldenrod2") +
  #geom_smooth(method="lm", formula = "y~log(x)", color="black", linetype = "dashed") +
  labs(x = expression(Silicate~(mu*mol~L^-1)),
      y = expression(Gross~Photosynthesis~Rate~(mu*mol~O[2]~cm^-2~hr^-1)),
       color = "Site") +
    theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20, face="bold"),
        axis.title.y=element_text(size=20, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
GP_silicate
ggsave(here::here("Outputs", "Results", "GP_silicate.jpg"), 
       width=10, height=7)


### GP model
GP_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>%
                                            filter(P_R=="GP") %>% 
                                            filter(!is.infinite(umol.cm2.hr)))

anova(GP_bothsites_silicate_linearmodel)
r.squaredGLMM(GP_bothsites_silicate_linearmodel)
summary(GP_bothsites_silicate_linearmodel)

### no significant reaction per site - slopes are indistinguishable which explains why there is one line --> 


###############################
## Calcification 
###############################
C_silicate_ECRS_firebrick4 <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=5, aes(color=site)) +
  scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  #scale_x_discrete(breaks = c(1, 10, 20)) +
  geom_hline(yintercept = 0) +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "C", site == "Varari", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "firebrick4") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "C", site == "Cabral", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "darkgoldenrod2", linetype = "dashed") +
 # geom_smooth(method="lm", formula = "y~log(x)", color="red3", 
           #   method="lm", formula = "y~log(x)", color="deepskyblue4", type="dashed") +
 # geom_smooth(method="lm", formula = "y~log(x)", color="deepskyblue4", type="dashed") +
 labs(x = expression(Silicate~(mu*mol~L^-1)),
       y = expression(Calcification~Rate~(mu*mol~CaCO[3]~cm^-2~hr^-1)),
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=15, face="bold"),
        axis.title.y=element_text(size=15, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
C_silicate_ECRS_firebrick4

ggsave(here::here("Outputs", "Results", "C_silicate.jpg"), 
       width=10, height=7)


### C model 
C_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>%
                                            filter(P_R=="C") %>%
                                            filter(!is.infinite(umol.cm2.hr)))

anova(C_bothsites_silicate_linearmodel)
r.squaredGLMM(C_bothsites_silicate_linearmodel)
summary(C_bothsites_silicate_linearmodel)

## intercept = 0.15352 
## slope =  -0.02219  

### ^^ these are Varari's slope and intercept 

#############################################
### make these plots figure worthy using patchwork 
#############################################

#### remove x-axis labels 
p1 <- R_silicate + theme(axis.title.x = element_blank(), axis.text.x = element_blank(),  
                         legend.title = element_blank(), legend.text = element_blank(), legend.position = "none", 
                         axis.title.y=element_text(size=15, face="bold")) + 
  scale_x_continuous(breaks = c(2, 10, 20)) 
p2 <- GP_silicate + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), 
                          axis.title.y=element_text(size=15, face="bold")) + 
  scale_x_continuous(breaks = c(2, 10, 20)) 
p3 <- C_silicate_ECRS_firebrick4 + 
  theme(legend.title = element_blank(), legend.text = element_blank(), legend.position = "none", 
        axis.title.x=element_text(size=15, face="bold"), 
        axis.title.y=element_text(size=15, face="bold")) +
  scale_x_continuous(breaks = c(2, 10, 20)) 

combined_column <- p1/p2/p3 + plot_layout(guides = 'collect')

combined_column + 
  plot_annotation(tag_levels = 'A') &
 theme(plot.margin = unit(c(1, 1, 1, 1), "cm"),
        plot.tag = element_text(size = 24, face = "bold"))

ggsave(here::here("Outputs", "Results", "CombinedRates.jpg"), 
       width=10, height=15)

```


### Figure 3: Re'Vampd with GP nonlinear
Going back to reVamp because nonlinear models show significance in GP at Varari also 
- linearly there is no significance but at Cabral and Varari in nonlinear models (like hypothesized) there is significance 
```{r}
###################
### GP 2.0
###################

#### confirm models are significant for both sites 

### confirm nonlinear model 
GP_Varari_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(silicate_umolL+1),2)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_Varari_silicate_nonlinearmodel)
summary(GP_Varari_silicate_nonlinearmodel)
r.squaredGLMM(GP_Varari_silicate_nonlinearmodel)


#### now plot 
GP_silicate2 <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
 scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "GP", site == "Varari", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y~poly(log(x),2), color = "firebrick4") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "GP", site == "Cabral", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y~poly(log(x),2), color = "darkgoldenrod2") +
  labs(x = expression(Silicate~(mu*mol~L^-1)),
      y = expression(Gross~Photosynthesis~Rate~(mu*mol~O[2]~cm^2~hr^-1)),
       color = "Site") +
    theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20, face="bold"),
        axis.title.y=element_text(size=20, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
GP_silicate2 


 
########################### 
## patch together 
###########################

#### remove x-axis labels 
p1 <- R_silicate + theme(axis.title.x = element_blank(), axis.text.x = element_blank(),  
                         legend.title = element_blank(), legend.text = element_blank(), legend.position = "none", 
                         axis.title.y=element_text(size=15, face="bold")) + 
  scale_x_continuous(breaks = c(2, 10, 20)) 
p2 <- GP_silicate2 + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), 
                          axis.title.y=element_text(size=15, face="bold")) + 
  scale_x_continuous(breaks = c(2, 10, 20)) 
p3 <- C_silicate_ECRS_firebrick4 + 
  theme(legend.title = element_blank(), legend.text = element_blank(), legend.position = "none", 
        axis.title.x=element_text(size=15, face="bold"), 
        axis.title.y=element_text(size=15, face="bold")) +
  scale_x_continuous(breaks = c(2, 10, 20)) 

combined_column <- p1/p2/p3 + plot_layout(guides = 'collect')

combined_column + 
  plot_annotation(tag_levels = 'A') &
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"),
        plot.tag = element_text(size = 18, face = "bold"))

ggsave(here::here("Outputs", "Results", "Final", "CombinedRates.jpg"), 
       width=10, height=15)

```

### FINAL MODELS USED IN RESULTS: 
RESULTS SHOW THAT: 
- linear model is better fit for R, GP, and C 
```{r}

RespoR_Normalized_Full_withNEC_nutrients <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(log_silicate = log(silicate_umolL+1), 
         log_silicate2 = (log_silicate^2)) 

########################
## R
########################
### nonlinear model 
R_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ log_silicate*site + log_silicate2 + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(R_silicate_nonlinearmodel)

summary(R_silicate_nonlinearmodel)
AIC(R_silicate_nonlinearmodel)


### linear model 
R_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL+1)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)))

summary(R_silicate_linearmodel)
AIC(R_silicate_linearmodel)

########################
## GP
########################
### nonlinear model 
GP_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log_silicate,2)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_silicate_nonlinearmodel)
summary(GP_silicate_nonlinearmodel)
AIC(GP_silicate_nonlinearmodel)

### linear model 
GP_silicate_linearmodel <- lmer(umol.cm2.hr ~ log_silicate*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr)))

anova(GP_silicate_linearmodel)
summary(GP_silicate_linearmodel)
AIC(GP_silicate_linearmodel)

########################
## Calcification 
########################
### nonlinear model 
C_Varari_silicate_nonlinearmodel <- lmer(umol.cm2.hr ~ poly(log(silicate_umolL+1),2)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

summary(C_Varari_silicate_nonlinearmodel)
AIC(C_Varari_silicate_nonlinearmodel)

### linear model 
C_Varari_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL+1)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>% 
  #filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)))

summary(C_Varari_silicate_linearmodel)
AIC(C_Varari_silicate_linearmodel)
```




### Plots using pred() function 
```{r}
#####################################
## New attempt: July 29th, 2024
#####################################

### new dfs just for calcification 
RespoR_Normalized_Full_withNEC_nutrients_Conly <- RespoR_Normalized_Full_withNEC_nutrients %>%
  filter(P_R=="C") %>%
  filter(!is.infinite(umol.cm2.hr))

### and sort in the right order from lowest silicate to highest 
RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted <- RespoR_Normalized_Full_withNEC_nutrients_Conly %>% 
  arrange(silicate_umolL)

### this is the MIXED MODEL for C
C_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), 
                                         data=RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted)

###############################################
## the problem is with the predict function 
###############################################

### try with Riley's code 

new_data <- expand.grid(
  silicate_umolL = seq(min(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$silicate_umolL),
                       max(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$silicate_umolL), length.out = 100),
  site = levels(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$site),
  new_colonynumber = unique(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$new_colonynumber))

# Predict values using the model
new_data$predicted <- predict(C_bothsites_silicate_linearmodel, newdata = new_data, re.form = NA)

riley_pred_plot <- new_data %>% 
  ggplot(aes(x = silicate_umolL, 
             y = predicted, 
             color = site)) + 
  geom_line(size = 1, linetype = "dashed") +  # Add dashed trend lines
  geom_point(data = RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted, 
             aes(x = silicate_umolL, 
                 y = umol.cm2.hr, 
                 color = treatment), 
             size = 3) +  # Add original data points
  labs(x = "silicate",
       y = "rate",
       color = "site") +
  theme_minimal() +
  theme(legend.title = element_text(face = "bold"))

riley_pred_plot

###############################
## tidyverse code
###############################

# Generate a sequence of silicate_umolL values for prediction
new_data_C_pred <- tibble(
    silicate_umolL = seq(min(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$silicate_umolL), 
                         max(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$silicate_umolL), length.out = 100),
    site = unique(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$site)[2],  # Use the first site as a placeholder
    new_colonynumber = unique(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted$new_colonynumber)[5]  # Use the first colony as a placeholder
)

# Add predictions to the new data frame
new_data_C_pred <- new_data_C_pred %>%
    mutate(predicted = predict(C_bothsites_silicate_linearmodel, newdata = new_data_C_pred, re.form = NA))  # predict without random effects


Pred_plot_C_10 <- RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted %>% 
  ggplot(aes(x = log(silicate_umolL), 
             y = umol.cm2.hr, 
             color = factor(site))) +
    geom_point(size = 3) +  # Scatter plot of the original data
    geom_line(data = new_data_C_pred, aes(y = predicted), color = 'darkgreen', size = 1) +  # Regression line
    labs(title = "Mixed-Effects Regression Line Plot", 
         x = "Silicate (umol/L)", 
         y = "umol/cm^2/hr") +  # Labels
    theme_minimal()

Pred_plot_C_10

### it's working rn with this code but now I only have one site line ? 
```


## Comparing Actual vs Predicted Nutrient Values 

```{r}
ActualvsPredicted_Nutrients_edit_Nitrate <- ActualvsPredicted_Nutrients %>% 
  pivot_longer(cols = "Actual":"Predicted", names_to = "Value_Type", values_to = "Value") %>% 
  filter(Parameter=="Nitrate")

ActualvsPredicted_Nutrients_edit_Phosphate <- ActualvsPredicted_Nutrients %>% 
  pivot_longer(cols = "Actual":"Predicted", names_to = "Value_Type", values_to = "Value") %>% 
  filter(Parameter=="Phosphate") %>% 
  filter(Value<1)

#### averaging the values across days per SGD dil to get just one value 
ActualvsPredicted_Nutrients_edit_Nitrate_averaged <- ActualvsPredicted_Nutrients_edit_Nitrate %>% 
  group_by(SGD_number, Site, Parameter, Value_Type) %>% 
  summarize(meanN = mean(Value))

ActualvsPredicted_Nutrients_edit_Phosphate_averaged <- ActualvsPredicted_Nutrients_edit_Phosphate %>% 
  group_by(SGD_number, Site, Value_Type) %>% 
  summarize(meanN = mean(Value))
  
#########################
## nitrate 
#########################
 ActualvsPredicted_Nutrients_Nitrateplot_AVERAGED <- ActualvsPredicted_Nutrients_edit_Nitrate_averaged %>%
 ggplot(aes(x=(SGD_number+1), 
            y=meanN, 
            color=Value_Type)) + 
  geom_point(size=4) +
 scale_color_manual(values=pnw_palette("Bay", n=2)) +
  facet_wrap(~Site) +
# geom_smooth(method="lm", formula="y~log(x)", color="black") + 
  theme_bw() + 
 coord_trans(x ="log") +
  labs(x = "SGD Percentages",
       y = expression(Nitrate+Nitrite~(mu*mol~L^-1)),
      # title = "Predicted vs Actual Values by Nitrate",
       color = "Nutrient Measurements") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        legend.title = element_text(size=18), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ActualvsPredicted_Nutrients_Nitrateplot_AVERAGED
ggsave(here::here("Outputs", "Results", "Actual_vs_Predicted_Nitrates_byday_AVG.jpg"), 
       width = 10, height=7)

#########################
## phosphate 
#########################
ActualvsPredicted_Nutrients_Phosphateplot_nooutlier_AVERAGED <- ActualvsPredicted_Nutrients_edit_Phosphate_averaged %>% 
 ggplot(aes(x=(SGD_number+1), 
            y=meanN, 
            color=Value_Type)) + 
  geom_point(size=4) +
 scale_color_manual(values=pnw_palette("Bay", n=2)) +
  facet_wrap(~Site) +
# geom_smooth(method="lm", formula="y~log(x)", color="black") + 
  theme_bw() + 
 coord_trans(x ="log") +
  labs(x = "SGD Percentages",
      y = expression(Phosphate~(mu*mol~L^-1)),
      # title = "Predicted vs Actual Values by Phosphate",
       color = "Nutrient Measurements") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        legend.title = element_text(size=18), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ActualvsPredicted_Nutrients_Phosphateplot_nooutlier_AVERAGED
ggsave(here::here("Outputs", "Results", "Actual_vs_Predicted_Phosphate_nooutlier_AVG.jpg"), 
       width = 10, height=7)
  

### patch them together 
p1.1a <- ActualvsPredicted_Nutrients_Nitrateplot_AVERAGED + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
p1.1b <- ActualvsPredicted_Nutrients_Phosphateplot_nooutlier_AVERAGED 

actualVpredicted_NutsPlot <- p1.1a/p1.1b +
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') #+
  #theme(axis.title = element_text(face = "bold"), 
     #   plot.tag = element_text(size = 12, face = "bold"))

actualVpredicted_NutsPlot
ggsave(here::here("Outputs", "Results", "Final", "ActualVPredicted_NutsPlot.jpg"), 
       width = 12, height=8)

```



## For ECRS: 
```{r}
###############################
## Calcification 
###############################

C_silicate_ECRS_firebrick4 <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(site = dplyr::recode(site, 
                      "Varari" = "Site 2",
                      "Cabral" = "Site 1")) %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=5, aes(color=site)) +
  scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
  geom_hline(yintercept = 0) +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "C", site == "Varari", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "firebrick4") +
  geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
                filter(P_R == "C", site == "Cabral", !is.infinite(umol.cm2.hr)), 
              aes(x = silicate_umolL, y = umol.cm2.hr), 
              method = "lm", formula = y ~ log(x), color = "darkgoldenrod2", linetype = "dashed") +
 # geom_smooth(method="lm", formula = "y~log(x)", color="red3", 
           #   method="lm", formula = "y~log(x)", color="deepskyblue4", type="dashed") +
 # geom_smooth(method="lm", formula = "y~log(x)", color="deepskyblue4", type="dashed") +
  labs(x = "Logged Silicate (umolL)",
       y = "Rate (umol CaCO3 g-1 hr-1)",
       title = "Calcification Rates as a Function of Silicate",
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20, face="bold"),
        axis.title.y=element_text(size=20, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
C_silicate_ECRS_firebrick4

ggsave(here::here("Outputs", "Results", "C_silicate_ECRS.jpg"), 
       width=10, height=7)


```



### check GP and C again colored by site and TA by NEC rates 
Results show that TA and NEC relationship is opposite of what we expect ... so it is likely that nutrients have a stronger effect on the physiological rates than TA

```{r}

### GP on x and C on y - colored by site 
RespoR_Normalized_Full_withNEC_nutrients2 <- RespoR_Normalized_Full_withNEC_nutrients %>%
  select(!c("phosphate_umolL":"TA_initial")) %>% 
  filter(P_R!="R", P_R!="NP") %>% 
  pivot_wider(names_from = P_R, values_from = umol.cm2.hr)


GP_bothsites_forNEC <- RespoR_Normalized_Full_withNEC_nutrients2 %>% 
  filter(sample_ID!="Varari_Col8_Dil6_Light") %>% 
 # filter(P_R=="C") %>% 
  filter(!is.infinite(GP)) %>% 
  ggplot(aes(x=GP, 
             y=C)) + 
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_hline(yintercept = 0) +
  labs(x = "GP",
       y = "C",
       title = "GP by C both sites") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
GP_bothsites_forNEC

## model 
model_GP_C_bothsites <- lmer(GP ~ C*site + (1|new_colonynumber), data = RespoR_Normalized_Full_withNEC_nutrients2 %>% 
                                filter(sample_ID!="Varari_Col8_Dil6_Light") %>% 
                                filter(!is.infinite(GP)))
anova(model_GP_C_bothsites)

############################
## TA by NEC 
###########################

TA_bothsites_forNEC <- RespoR_Normalized_Full_withNEC_nutrients %>% 
#filter(sample_ID=="Varari_Col8_Dil6_Light") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=TA_initial, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2), 
                     guide="none") +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  geom_hline(yintercept = 0) +
  labs(x = "TA",
       y = "C",
       title = "TA by C both sites") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
TA_bothsites_forNEC


```


## EXtra: 
```{r}

RespoR_Normalized_Full_withNEC_nutrients_Cabral_GP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr))

min(RespoR_Normalized_Full_withNEC_nutrients_Cabral_GP$umol.cm2.hr)
max(RespoR_Normalized_Full_withNEC_nutrients_Cabral_GP$umol.cm2.hr)




RespoR_Normalized_Full_withNEC_nutrients_Varari_GP <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(site=="Varari") %>% 
   filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr))

min(RespoR_Normalized_Full_withNEC_nutrients_Varari_GP$umol.cm2.hr)
max(RespoR_Normalized_Full_withNEC_nutrients_Varari_GP$umol.cm2.hr)


### plot 

 C_silicate_edit <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2)) +
  theme_classic() + 
  coord_trans(x ="log") +
  geom_abline(slope = -0.02219, intercept = 0.15352, color = "black") +
 # geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2)
  #geom_smooth(data = RespoR_Normalized_Full_withNEC_nutrients %>% 
              #  filter(P_R == "C", site == "Varari", !is.infinite(umol.cm2.hr)), 
            #  aes(x = silicate_umolL, y = umol.cm2.hr), 
             # method = "lm", formula = y ~ log(x), color = "red3") 
  labs(x = "logged Silicate (umolL)",
       y = "Rate (umol CaCO3 g-1 hr-1)",
       title = "Calcification Rates as a Function of Silicate",
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        legend.title = element_text(size=18), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_silicate_edit





##############################################################
##############################################################

###############################
### trying to use marginal and conditional values to plot 
###############################

### mixed model 
C_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients %>%
                                            filter(P_R=="C") %>% 
                                            filter(!is.infinite(umol.cm2.hr)))

C_silicate2 <- RespoR_Normalized_Full_withNEC_nutrients %>%
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  mutate(fit.m = predict(C_bothsites_silicate_linearmodel),
         fit.c = predict(C_bothsites_silicate_linearmodel)) #+ 
 # mutate(resid = resid(C_bothsites_silicate_linearmodel)) ### getting an error here


C_silicate2.1 <- C_silicate2 %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(pch = 16, col = "grey") +
 geom_line(aes(y = fit.c), col = 1, size = 2) 
  
C_silicate2.1  
  
  geom_point(size=4, aes(color=site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2)) +
  theme_bw() + 
  coord_trans(x ="log") +
  theme(strip.background = element_rect(fill = "white")) +
#  geom_hline(yintercept = 0) +
  geom_line(aes(y = fit.c), col = 1, size = 2) +
#  coord_cartesian(ylim = c(-40, 100)) +
  #geom_smooth(method="lm", formula = "y~log(x)", color="black") +
  labs(x = "logged Silicate (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Calcification Rates as a Function of Silicate",
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_silicate2.1

ggsave(here::here("Outputs", "Results", "C_silicate.jpg"))




###############################
## for Calcification 
###############################
RespoR_Normalized_Full_withNEC_nutrients2<- RespoR_Normalized_Full_withNEC_nutrients %>%
  filter(P_R=="C") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  arrange(RespoR_Normalized_Full_withNEC_nutrients2$umol.cm2.hr) 

C_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients2)

### ^^ look for slope and intercept 
summary(C_bothsites_silicate_linearmodel)


### use predict function to get info for confidence intervals - use cbind to create a new df and use that 

predC <- predict(C_bothsites_silicate_linearmodel) # Gets the predicted values from the regression lines in the ANOVA

graphdata_C <- cbind(RespoR_Normalized_Full_withNEC_nutrients2, predC) # attaches those predictions to the dataset

graphdata_C <- graphdata_C %>% 
  arrange(graphdata_C$silicate_umolL)


# We'll plot the original data as points, and the regression predictions as lines 
C_silicate_pred <- new_data %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr, 
             color=site)) +
  geom_point(size=4) + 
 # geom_line(aes(y=(predC))) +
  geom_line(data = new_data, aes(x = log(silicate_umolL), y = predictions, color = site)) +
  scale_color_manual(values=pnw_palette("Bay", n=2)) +
  theme_classic() + 
  coord_trans(x ="log") +
  labs(x = "logged Silicate (umolL)",
       y = "Rate (umol CaCO3 g-1 hr-1)",
       title = "Calcification Rates as a Function of Silicate",
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        legend.title = element_text(size=18), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
C_silicate_pred


###############################
## for Gross Photosynthesis  
###############################
RespoR_Normalized_Full_withNEC_nutrients3 <- RespoR_Normalized_Full_withNEC_nutrients %>% 
   filter(P_R=="GP") %>% 
  filter(!is.infinite(umol.cm2.hr))

GP_bothsites_silicate_linearmodel <- lmer(umol.cm2.hr ~ log(silicate_umolL)*site + (1|new_colonynumber), data=RespoR_Normalized_Full_withNEC_nutrients3)

### ^^ look for slope and intercept 
summary(GP_bothsites_silicate_linearmodel)

############################
### attemot 1 -- something is off with the pred function, this is for a simpler model, mine is too complex 
############################

Cpred <- predict(C_bothsites_silicate_linearmodel)

graph_Cpred_data <- cbind(RespoR_Normalized_Full_withNEC_nutrients_Conly_sorted, Cpred) 

Cpred_plot <- ggplot(data=graph_Cpred_data,
       aes(x=log(silicate_umolL), 
           y=umol.cm2.hr, 
           color=site)) +
  geom_point(size=4) + 
  geom_line(aes(y=Cpred)) +
  labs(x="silicate_umolL", y="umol.cm2.hr", fill="site") +
  theme_bw() 

Cpred_plot

Cpred_plot2 <- ggplot(data=graph_Cpred_data,
       aes(x=log(silicate_umolL), 
           y=Cpred, 
           color=site)) +
  geom_point(size=4) + 
  geom_line(aes(y=Cpred)) +
  labs(x="silicate_umolL", y="Cpred", fill="site") +
  theme_bw() 


Cpred_plot2






###########################
## get basic correlations with p-values 
##########################
res.cor.Varari <- correlate(corr_matrix_Varari, method = "spearman", diagonal = 1)

###########################
## edit correlation matrix and plot 
##########################
res.cor.Varari %>% 
  rearrange(method = "MDS", absolute = FALSE) %>% 
  shave(upper=TRUE) %>% 
  filter(!Salinity = 1) %>% 
  rplot() ## make correlologram 
  

###########################
res.cor.Varari %>% 
  filter(!"Salinity" = 1)


  rearrange(method = "MDS", absolute = FALSE) %>% 
  shave(upper=TRUE) %>% 
  
##########################


```


### Figure 2:
```{r}
############################################
### correlation matrix for Varari 
############################################

## data 
corr_matrix_envparams_Varari <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(N_P = NN_umolL/phosphate_umolL) %>% 
  filter(P_R=="R") %>% 
  mutate(Salinity=salinity, 
         TA = TA_initial, 
         pH = new_pH, 
         Nitrate_Nitrite_umolL = NN_umolL, 
         Phosphate_umolL = phosphate_umolL,
         Silicate_umolL = silicate_umolL, 
         Ammonia_umolL = ammonia_umolL) %>% 
  filter(site=="Varari") %>% 
  select(!c("salinity", "silicate_umolL", "TA_initial", "Ammonia_umolL", "new_pH", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL")) 

##visualize it 
ggcorr(corr_matrix_envparams_Varari, method = c("everything", "pearson")) 

###############################
cor_mat <- round(cor(corr_matrix_envparams_Varari),4)
#head(cor_mat)

###############################
# Set the diagonal elements to NA
#diag(cor_mat) <- NA
###############################

###############################
# Melt the correlation matrix
melted_cormat <- melt(cor_mat, na.rm = TRUE)
###############################

#melt the correlation matrix means it reassembles data frame to be more effective to complete corr matrix
#to long format
#melted_cormat <- melt(cor_mat)
#head(melted_cormat)

#visualize the correlation matrix in general
#ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
#  geom_tile()

# Get lower and upper triangle of the correlation matrix
#Note that, a correlation matrix has redundant information. We’ll use the functions below to set half of it to NA
get_lower_tri<-function(cor_mat){
  cormat[upper.tri(cor_mat)] <- NA
  return(cor_mat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cor_mat){
  cor_mat[lower.tri(cor_mat)]<- NA
  return(cor_mat)
}

#apply upper tri calculation to graphc
upper_tri <- get_upper_tri(cor_mat)
#upper_tri

#melt the correlation matrix
#melt the correlation data and drop the rows with NA values 
melted_cormat <- melt(upper_tri, na.rm = TRUE)

#heatmap of correlation matrix
#negative correlations are in purple color and positive correlations in red
#scale_fill_gradient2 is used with the argument limit = c(-1,1) as correlation coefficients range from -1 to 1
#coord_fixed() : this function ensures that one unit on the x-axis is the same length as one unit on the y-axis
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "midnightblue", high = "firebrick4", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson Correlation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()

melted_cormat <- melted_cormat %>% mutate_at(vars(starts_with("value")), funs(round(., 2)))

# Create a ggheatmap with basic characteristics, etc. 
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "firebrick3", mid = "white", high = "dodgerblue3", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson Correlation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 10, hjust = 1))+
  coord_fixed() 

diag(melted_cormat) <- NA

# Print the heatmap
#print(ggheatmap)

#add correlation coefficients to the heatmap
#geom_text() to add the correlation coefficients on the graph
#guides() to change the position of the legend title
#if else statement in melted data frame to quotes of black and white to adjust text color 
corr_matrix_SGD_params_Varari <- ggheatmap + 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black"),
        panel.grid.major = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        legend.justification = c(0.8, 0),
        legend.title = element_text(size = 10, color="black"),
        legend.text = element_text(size = 10, color="black"),
        legend.position = c(0.48, 0.75),
        legend.direction = "horizontal", 
        title= element_text(size = 12, hjust=0.5, face="bold", color="black")) +
  labs(title="Pearson Correlation Matrix for Environmental Parameters at Varari") + 
  guides(fill = guide_colorbar(barwidth = 8, barheight = 1, 
                               title.position = "top", title.hjust = 0.5, title.vjust = 1.0))

corr_matrix_SGD_params_Varari

ggsave(here::here("Outputs", "Results", "Varari_correlation_matrix.jpg"), 
       width=10, height=7)

```

### Figure 2a: 
```{r}
############################################
### correlation matrix for Cabral 
############################################

## data 
corr_matrix_envparams_Cabral <- RespoR_Normalized_Full_withNEC_nutrients %>% 
  mutate(N_P = NN_umolL/phosphate_umolL) %>% 
  filter(P_R=="R") %>% 
  mutate(Salinity=salinity, 
         TA = TA_initial, 
         pH = new_pH, 
         Nitrate_Nitrite_umolL = NN_umolL, 
         Phosphate_umolL = phosphate_umolL,
         Silicate_umolL = silicate_umolL, 
         Ammonia_umolL = ammonia_umolL) %>% 
  filter(site=="Cabral") %>% 
  select(!c("salinity", "silicate_umolL", "TA_initial", "new_pH", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL", "Ammonia_umolL")) 

##visualize it 
ggcorr(corr_matrix_envparams_Cabral, method = c("everything", "pearson")) 

###############################
cor_mat <- round(cor(corr_matrix_envparams_Cabral),4)
#head(cor_mat)

#melt the correlation matrix means it reassembles data frame to be more effective to complete corr matrix
#to long format
melted_cormat <- melt(cor_mat)
#head(melted_cormat)


#visualize the correlation matrix in general
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower and upper triangle of the correlation matrix
#Note that, a correlation matrix has redundant information. We’ll use the functions below to set half of it to NA
get_lower_tri<-function(cor_mat){
  cormat[upper.tri(cor_mat)] <- NA
  return(cor_mat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cor_mat){
  cor_mat[lower.tri(cor_mat)]<- NA
  return(cor_mat)
}

#apply upper tri calculation to graphc
upper_tri <- get_upper_tri(cor_mat)
#upper_tri

#melt the correlation matrix
#melt the correlation data and drop the rows with NA values 
melted_cormat <- melt(upper_tri, na.rm = TRUE)

#heatmap of correlation matrix
#negative correlations are in purple color and positive correlations in red
#scale_fill_gradient2 is used with the argument limit = c(-1,1) as correlation coefficients range from -1 to 1
#coord_fixed() : this function ensures that one unit on the x-axis is the same length as one unit on the y-axis
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "midnightblue", high = "firebrick4", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson Correlation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()

melted_cormat <- melted_cormat %>% mutate_at(vars(starts_with("value")), funs(round(., 2)))

# Create a ggheatmap with basic characteristics, etc. 
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "firebrick3", mid = "white", high = "dodgerblue3", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson Correlation") +
  theme_minimal()+ # minimal theme
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 10, hjust = 1))+
  coord_fixed()

# Print the heatmap
#print(ggheatmap)

#add correlation coefficients to the heatmap
#geom_text() to add the correlation coefficients on the graph
#guides() to change the position of the legend title
#if else statement in melted data frame to quotes of black and white to adjust text color 
corr_matrix_SGD_params_Cabral <- ggheatmap + 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 12, face="bold", color="black"),
        axis.text.y = element_text(size = 12, face="bold", color="black"),
        panel.grid.major = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        legend.justification = c(0.8, 0),
        legend.title = element_text(size = 10, color="black"),
        legend.text = element_text(size = 10, color="black"),
        legend.position = c(0.48, 0.75),
        legend.direction = "horizontal", 
        title= element_text(size = 12, hjust=0.5, face="bold", color="black")) +
  labs(title="Pearson Correlation Matrix for Environmental Parameters at Cabral") + 
  guides(fill = guide_colorbar(barwidth = 8, barheight = 1, 
                               title.position = "top", title.hjust = 0.5, title.vjust = 1.0))

corr_matrix_SGD_params_Cabral

ggsave(here::here("Outputs", "Results", "Cabral_correlation_matrix.jpg"), 
       width=10, height=7)

```







