---
title: "Salinity_pH_TA_TestingRelationships"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This script explores the relationship between silicate and the other environmental parameters we measured (pH, NN, Phosphate, TA, and salinity). It also calculates the z-scores and plots a standardized effects plot for the relationship between silicate and the environmental parameters at both Varari and Cabral. 

## Load libraries 
```{r, echo=FALSE, message=FALSE}
library(lubridate)
library(patchwork)
library(tidyverse)
library(here)
library(car)
library(GGally)
library(corrplot) 
library(ggcorrplot) 
library(corrr) 
library(PNWColors) 
library(seacarb) 
library(broom)
library(agricolae) 
library(lme4)
library(ggsci) 
library(see) 
library(cowplot)
library(lmerTest)
library(modelsummary) 
library(performance)
library(emmeans)
library(MuMIn)
library(broom.mixed) 
library(kableExtra) 
library(reshape2) 
theme_set(theme_classic()) ### This sets the default ggplot theme
library(Hmisc) 
require(effects)
```

## Read in data 
```{r, echo=FALSE, message=FALSE}
fulldata <- read_csv(here::here("Data", "RespoR_Normalized_Full_withNEC_andallnutrients.csv"))
Salinity_from_TA <- read_csv(here::here("Data", "Titrations", "TitrationNation_SGD.csv"))

```

## Basic exploratory plots 
1. Scatterplots to show silicate compared to all other env parameters 
2. Notes from a meeting with Nyssa, isolating Varari since that was the site with the one really weird day that is possibly/likley driving the lack of significance in salinity vs silicate correlation. SO create some z-scores and tested significance keeping day in mind
```{r}

#################################
### testing silicate by all other env params 
### looking for daily anomolies to explain significance/non-significance 
#################################

###########################
## silicate by phosphate 

silicate_phos <- fulldata %>% 
  filter(phosphate_umolL < 0.9) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=phosphate_umolL, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw() + 
  facet_wrap(~site) 

silicate_phos


###########################
## silicate by NN  

silicate_NN <- fulldata %>% 
 # filter(phosphate_umolL < 0.9) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=NN_umolL, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw() + 
  facet_wrap(~site) 

silicate_NN


###########################
## silicate by pH 

silicate_pH <- fulldata %>% 
 # filter(phosphate_umolL < 0.9) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=new_pH, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw() + 
  facet_wrap(~site) 

silicate_pH

###########################
## silicate by TA 

silicate_TA <- fulldata %>% 
  filter(P_R == "C") %>% 
  ggplot(aes(x=silicate_umolL, 
             y=TA_initial, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw() + 
  facet_wrap(~site) 

silicate_TA

###########################
## silicate by salinity 

silicate_salinity <- fulldata %>% 
 # filter(phosphate_umolL < 0.9) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=salinity, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw() + 
  facet_wrap(~site) 

silicate_salinity

######################
## add all the plots together 

silicate_pH + silicate_NN + silicate_phos + silicate_TA

```


### Cross reference salinities from in lab and in field 
```{r}

### first clean up that data 

Salinity_inlab <- Salinity_from_TA %>% 
  filter(sample_info != "seawater", 
         site != "Cabral") %>% 
  group_by(date, SGD_number) %>% 
  dplyr::summarize(mean_sal = mean(salinity_psu_calibr0915))


### join with other dataset to compare Varari salinities 

salinity_comparisons <- Salinity_inlab %>% 
  left_join(fulldata)


### now compare two salinities 

salinity_comparison_plot <- salinity_comparisons %>% 
  ggplot(aes(x=salinity, 
             y=mean_sal, 
             color=date)) + 
  geom_point(size=3, alpha = 0.5) + 
  theme_bw() #+ 
 # facet_wrap(~site) 

salinity_comparison_plot ### two salinity measurements are pretty well aligned 

salinity_comparison_plot2 <- salinity_comparisons %>% 
  ggplot(aes(x=SGD_number, 
             y=mean_sal, 
             color=date)) + 
  geom_point(size=3, alpha = 0.5) + 
  theme_bw() 

salinity_comparison_plot2


##########################
#### so go ahead and substract 1 psu from 6/17 which was a wonkyyy day
##########################

fulldata_newsalinity <- fulldata %>% 
  mutate(salinity = if_else(date == "6/17/23", salinity - 1, salinity))
  

### test to make sure I did it correctly 

salinity_test <- fulldata %>%  ## switch out fulldata & fulldata_newsalinity to test if addition evened out salinities
  ggplot(aes(x=SGD_number, 
             y=salinity, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw()

salinity_test

salinity_test2 <- fulldata_newsalinity %>%  ## switch out fulldata & fulldata_newsalinity to test if addition evened out salinities
  ggplot(aes(x=SGD_number, 
             y=salinity, 
             color=date)) + 
  geom_point(size=3) + 
  theme_bw()

salinity_test2 + salinity_test
```


## Calculating the average and standard error of temperature during the experiment 
- Calculated by using the sd and sample size of all the samples, not separated by site 
```{r}
fulldata_temp <- fulldata %>% 
  select(c("sample_ID", "site", "temp_C")) 

max(fulldata_temp$temp_C)
min(fulldata_temp$temp_C)
mean(fulldata_temp$temp_C)
sd <- sd(fulldata_temp$temp_C)
se <- sd/sqrt(500)

(fulldata_temp$temp_C)

```



## compare respiration rates by day to see if 6/17 had different respo rates 
Conclusion: looks relatively even throughout and compared to other dates, does not stand out 

```{r}
respo_test <- fulldata %>% 
  filter(P_R=="R") %>% 
  filter(site=="Varari") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=4, aes(color=date)) +
 # scale_color_manual(values=c("darkgoldenrod2", "firebrick4")) +
  theme_classic() + 
  coord_trans(x ="log") +
  labs(y = expression(Respiration~Rate~(mu*mol~O[2]~cm^-2~hr^-1)),
       color = "Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=15, face="bold"),
        axis.title.y=element_text(size=15, face="bold"),
        legend.title = element_text(size=18, 
                                    face="bold"), 
        legend.text = element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20, 
                                face="bold"))
respo_test
  


```


## Reran the correlation matrix in Plots_Based_on_Model_Selection, line 1389
on March 21st, 2025 

# Ultimate decision: Run z-score random effects model
-  Run independently by site - effect size
-  Believe that salinity and silicate are in fact correlated... Just maybe not being shown properly in the Spearman correlation because Spearman does not group by day like a regression would ... and that one day is really wonky 
-  Based on plots above, it seems like every other env parameter is not too wonky on 6/17/23, but since salinity is such a key part of the story, going to use the z-scores for the analysis 
```{r}
###################################
## example to show that z-score is in fact the way to go 
###################################

### create new dataset to try this with only Varari for right now since that is the site NOT correlated 
fulldata_2 <- fulldata %>% 
  filter(site=="Varari")
  
cor(fulldata_2$salinity, fulldata_2$silicate_umolL, method="spearman") ## not correlated because not grouping by anything -- indicates a calibration error probably

## try with lab salinity data -- need to get single calibration point 

fulldata_2_lmer <- lmer(salinity ~ silicate_umolL + (1|date), data=fulldata_2) ## takes salinity by day 

summary(fulldata_2_lmer)

## run standardized effects plot using z-scores 

fulldata_2 <- fulldata_2 %>% 
  mutate(salinity_scale = as.numeric(scale(salinity)), 
         silicate_scale = as.numeric(scale(silicate_umolL))) ##makes zscores a number 


fulldata_2_lmer_wScales <- lmer(salinity_scale ~ silicate_scale + (1|date), data=fulldata_2)

anova(fulldata_2_lmer_wScales)
summary(fulldata_2_lmer_wScales)

##################
## Notes: 

#### Estimate # in the summary = effect size. If close to 1 = strong 
#### Different from correlation 
#### Matrix using standardized effect sizes 
#### Should be colored to the standardized effect size NOT Spearman 


###################################
## Run actual model and collect z-score info for each parameter and re-run matrix using the z-scores rather than the Spearman corr. 
## Need to still separate by site 
###################################

###################################
## VARARI  
###################################

### create separate df 
zscores_Varari <- fulldata %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="C") %>% 
  mutate(salinity_scale = as.numeric(scale(salinity)),
         pH_scale = as.numeric(scale(new_pH)), 
         TA_scale = as.numeric(scale(TA_initial)), 
         NN_scale = as.numeric(scale(NN_umolL)), 
         phos_scale = as.numeric(scale(phosphate_umolL)),
         silicate_scale = as.numeric(scale(silicate_umolL))) ##makes zscores a number 


## salinity 
salinity_V_zscores <- lmer(salinity_scale ~ silicate_scale + (1|date), data=zscores_Varari) ## takes salinity by day 

anova(salinity_V_zscores)
summary(salinity_V_zscores) #### -0.71


## pH 
pH_V_zscores <- lmer(pH_scale ~ silicate_scale + (1|date), data=zscores_Varari)

anova(pH_V_zscores)
summary(pH_V_zscores) #### -0.30


## TA 

TA_V_zscores <- lmer(TA_scale ~ silicate_scale + (1|date), data=zscores_Varari)

anova(TA_V_zscores)
summary(TA_V_zscores)  #### 0.71


## NN 

NN_V_zscores <- lmer(NN_scale ~ silicate_scale + (1|date), data=zscores_Varari)

anova(NN_V_zscores)
summary(NN_V_zscores) #### 0.32

## Phos 

Phos_V_zscores <- lmer(phos_scale ~ silicate_scale + (1|date), data=zscores_Varari)

anova(Phos_V_zscores)
summary(Phos_V_zscores) #### 0.31

############# 
## Summary: 

## so the significant ones are salinity and TA 
## this differs from the previous matrix which JUST showed TA as significant 
## other params are actually even LESS correlated this way 


###################################
## CABRAL   
###################################

#### create separate df 
zscores_Cabral <- fulldata %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="C") %>% 
  mutate(salinity_scale = as.numeric(scale(salinity)),
         pH_scale = as.numeric(scale(new_pH)), 
         TA_scale = as.numeric(scale(TA_initial)), 
         NN_scale = as.numeric(scale(NN_umolL)), 
         phos_scale = as.numeric(scale(phosphate_umolL)),
         silicate_scale = as.numeric(scale(silicate_umolL)))

## salinity 
salinity_C_zscores <- lmer(salinity_scale ~ silicate_scale + (1|date), data=zscores_Cabral) ## takes salinity by day 

anova(salinity_C_zscores)
summary(salinity_C_zscores) #### -0.97


## pH 
pH_C_zscores <- lmer(pH_scale ~ silicate_scale + (1|date), data=zscores_Cabral)

anova(pH_C_zscores)
summary(pH_C_zscores) #### 0.18, though there was a note of a singular boundary 


## TA 

TA_C_zscores <- lmer(TA_scale ~ silicate_scale + (1|date), data=zscores_Cabral)

anova(TA_C_zscores)
summary(TA_C_zscores)  #### 0.08


## NN 

NN_C_zscores <- lmer(NN_scale ~ silicate_scale + (1|date), data=zscores_Cabral)

anova(NN_C_zscores)
summary(NN_C_zscores) #### 0.17

## Phos 

Phos_C_zscores <- lmer(phos_scale ~ silicate_scale + (1|date), data=zscores_Cabral)

anova(Phos_C_zscores)
summary(Phos_C_zscores) #### 0.51

############# 
## Summary: 

## so the significant ones are salinity and mayyybe phosphate 
## this differs from the previous matrix which was salinity and definitively phosphate -- phosphate was weakened by 0.1 here 
## other params remain relatively the same 
```


# Create the matrix using standardized z-scores 
```{r}

#####################
## VARARI 
#####################
### pearson correlation assumes/uses z-scores 

zscores_Varari2 <- zscores_Varari %>% 
  mutate("Salinity"=salinity_scale, 
         "TA" = TA_scale, 
         "pH" = pH_scale, 
         "N+N" = NN_scale, 
         "Phosphate" = phos_scale,
         "Silicate" = silicate_scale) %>% 
  select(!c("salinity", "silicate_umolL", "log_silicate", "log_silicate2", "TA_initial", "new_pH", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL", "NN_scale", "phos_scale", "silicate_scale", "pH_scale", "TA_scale", "salinity_scale")) 


## version 2.0 
corr_Varari_pearson <- round(cor(zscores_Varari2, method="pearson"), 1)

# Compute a matrix of correlation p-values
p.mat_Varari_pearson <- cor_pmat(corr_Varari_pearson)

# Extract the correlations involving "Silicate"
corr_silicate_V <- corr_Varari_pearson[, "Silicate", drop = FALSE]

# Transpose the matrix to make "Silicate" the row instead of the column
corr_silicate_matrix_V <- t(as.matrix(corr_silicate_V))

# Convert the matrix to a long format
corr_melted_V <- melt(corr_silicate_matrix_V)

# Plot the correlation matrix vertically
Varari_corr_matrix_pearson <- ggplot(corr_melted_V, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile(color = "white") +  # Adjust width of the tiles to make the plot narrower
  scale_fill_gradient2(low = "steelblue3", high = "tomato3", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  theme_minimal() + 
  theme(axis.text.x = element_text(vjust = 0.5, size = 12, face = "bold", color="black"),
        axis.text.y = element_text(size = 12, face = "bold", color="black")) +  
  coord_flip() +  # Flip coordinates for vertical layout
  labs(x = "", y = "")

# Display the plot
Varari_corr_matrix_pearson



#####################
## CABRAL 
#####################
### pearson correlation assumes/uses z-scores 

zscores_Cabral2 <- zscores_Cabral %>% 
  mutate("Salinity"=salinity_scale, 
         "TA" = TA_scale, 
         "pH" = pH_scale, 
         "N+N" = NN_scale, 
         "Phosphate" = phos_scale,
         "Silicate" = silicate_scale) %>% 
  select(!c("salinity", "silicate_umolL", "log_silicate", "log_silicate2", "TA_initial", "new_pH", "phosphate_umolL", "NN_umolL", "umol.cm2.hr", "SGD_number", "temp_C", "new_colonynumber", "sample_ID", "site", "date", "P_R", "ammonia_umolL", "NN_scale", "phos_scale", "silicate_scale", "pH_scale", "TA_scale", "salinity_scale")) 


## version 2.0 
corr_Cabral_pearson <- round(cor(zscores_Cabral2, method="pearson"), 1)

# Compute a matrix of correlation p-values
p.mat_Cabral_pearson <- cor_pmat(corr_Cabral_pearson)

# Extract the correlations involving "Silicate"
corr_silicate_C <- corr_Cabral_pearson[, "Silicate", drop = FALSE]

# Transpose the matrix to make "Silicate" the row instead of the column
corr_silicate_matrix_C <- t(as.matrix(corr_silicate_C))

# Convert the matrix to a long format
corr_melted_C <- melt(corr_silicate_matrix_C)

# Plot the correlation matrix vertically
Cabral_corr_matrix_pearson <- ggplot(corr_melted_C, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile(color = "white") +  # Adjust width of the tiles to make the plot narrower
  scale_fill_gradient2(low = "steelblue3", high = "tomato3", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  theme_minimal() + 
  theme(axis.text.x = element_text(vjust = 0.5, size = 12, face = "bold", color="black"),
        axis.text.y = element_text(size = 12, face = "bold", color="black")) +  
  coord_flip() +  # Flip coordinates for vertical layout
  labs(x = "", y = "")

# Display the plot
Cabral_corr_matrix_pearson


########################### 
## PATCH TOGETHER 
###########################

#### remove x-axis labels 
p_Ccorr_silicate <- Cabral_corr_matrix_pearson
p_Vcorr_silicate <- Varari_corr_matrix_pearson
 
combined_corr_plot_silicate <- p_Ccorr_silicate/p_Vcorr_silicate + plot_layout(guides = 'collect')

combined_corr_plot_silicate + 
  plot_annotation(tag_levels = 'A') &
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"), 
        plot.tag = element_text(size = 18, face = "bold"))

ggsave(here::here("Outputs", "Results", "Final", "CorrMatrices.jpg"), 
       width=10, height=15)



```


# Try again, but make a standardized effects plot 
-  Used the code from Figure 3 

- when rendering: does not like function plot_model, so commented out 
```{r}

############################################
## going to need two separate sep for Varari and Cabral, each with 5 stacked points 
############################################

###########
### get standardized effect sizes 

## For Varari 
#plot_model(salinity_V_zscores, type = "std") 
#plot_model(pH_V_zscores, type = "std")
#plot_model(NN_V_zscores, type = "std")
#plot_model(Phos_V_zscores, type = "std")
#plot_model(TA_V_zscores, type = "std")

## For Cabral 
#plot_model(salinity_C_zscores, type = "std") 
#plot_model(pH_C_zscores, type = "std")
#plot_model(NN_C_zscores, type = "std")
#plot_model(Phos_C_zscores, type = "std")
#plot_model(TA_C_zscores, type = "std")

###########
### Put it all on the same plot though for comparison
### First need to extract the data from plot_model

### for Varari 

V_sal<-tibble(plot_model(salinity_V_zscores, type = "std")$data) %>%
  mutate(Parameter = "Salinity", 
         Significant = "Yes", 
         Site= "Varari")

V_pH<-tibble(plot_model(pH_V_zscores, type = "std")$data) %>%
  mutate(Parameter = "pH", 
         Significant = "Yes", 
         Site= "Varari")

V_NN<-tibble(plot_model(NN_V_zscores, type = "std")$data) %>%
  mutate(Parameter = "Nitrate", 
         Significant = "Yes", 
         Site= "Varari")

V_phos<-tibble(plot_model(Phos_V_zscores, type = "std")$data) %>%
  mutate(Parameter = "Phosphate", 
         Significant = "Yes", 
         Site= "Varari")

V_TA<-tibble(plot_model(TA_V_zscores, type = "std")$data) %>%
  mutate(Parameter = "Total Alkalinity", 
         Significant = "Yes", 
         Site= "Varari")

### for Cabral 

C_sal<-tibble(plot_model(salinity_C_zscores, type = "std")$data) %>%
  mutate(Parameter = "Salinity", 
         Significant = "Yes", 
         Site= "Cabral")

C_pH<-tibble(plot_model(pH_C_zscores, type = "std")$data) %>%
  mutate(Parameter = "pH",
         Significant = "No", 
         Site= "Cabral")

C_NN<-tibble(plot_model(NN_C_zscores, type = "std")$data) %>%
  mutate(Parameter = "Nitrate", 
         Significant = "No", 
         Site= "Cabral")

C_phos<-tibble(plot_model(Phos_C_zscores, type = "std")$data) %>%
  mutate(Parameter = "Phosphate", 
         Significant = "Yes", 
         Site= "Cabral")

C_TA<-tibble(plot_model(TA_C_zscores, type = "std")$data) %>%
  mutate(Parameter = "Total Alkalinity", 
         Significant = "No", 
         Site= "Cabral")

#############
### Bind them all together to be on same plot 

### for Varari 
all_V_params<-V_sal %>%
  bind_rows(V_pH) %>%
  bind_rows(V_NN) %>%
  bind_rows(V_phos) %>%
  bind_rows(V_TA)

### for Cabral 
all_C_params<-C_sal %>%
  bind_rows(C_pH) %>%
  bind_rows(C_NN) %>%
  bind_rows(C_phos) %>%
  bind_rows(C_TA)

#################
### time to plot

### for Varari 
standardized_effects_V <- all_V_params %>%
 # mutate(term = case_when(term == "log_silicate"~ "Log Silicate",
              #            term == "I(log_silicate^2)"~ "Quadratic Log Silicate")) %>% # Reverse the order of Rate
#  mutate(Rate = factor(Rate, levels = c("Respiration","Gross Photosynthesis","Calcification"))) %>% # put the levels in an order I want for plotting
  ggplot(aes(x = estimate, 
             y = term, 
             color = Parameter))+
  geom_vline(xintercept = 0, linetype = 2) +
  geom_point(size = 4, 
             position = position_dodge(0.9)) + # dodge the points so not on top of each other
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0, position = position_dodge(0.9)) +
  scale_color_manual(values=c("#b8b5b5", "#838282", "#484747", "blue", "red"), 
                     guide="none") +
  facet_wrap(~Parameter, nrow = 3) +
  labs(x = "Standardized Effect",
       y = "") +
  theme_classic() +
  theme(legend.text = element_text(size = 14),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 12)) 

standardized_effects_V 

### for Cabral 
standardized_effects_C <- all_C_params %>%
 # mutate(term = case_when(term == "log_silicate"~ "Log Silicate",
              #            term == "I(log_silicate^2)"~ "Quadratic Log Silicate")) %>% # Reverse the order of Rate
#  mutate(Rate = factor(Rate, levels = c("Respiration","Gross Photosynthesis","Calcification"))) %>% # put the levels in an order I want for plotting
  ggplot(aes(x = estimate, 
             y = term, 
             color = Parameter))+
  geom_vline(xintercept = 0, linetype = 2) +
  geom_point(size = 4, 
             position = position_dodge(0.9)) + # dodge the points so not on top of each other
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0, position = position_dodge(0.9)) +
  scale_color_manual(values=c("#b8b5b5", "#838282", "#484747", "blue", "red"), 
                     guide="none") +
  facet_wrap(~Parameter, nrow = 3) +
  labs(x = "Standardized Effect",
       y = "") +
  theme_classic() +
  theme(legend.text = element_text(size = 14),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 12)) 

standardized_effects_C
```

## Edit the plot: 
-  Bring together both sites
-  No facet, so it is easier to compare
-  Parameters on the y-axis, color by Site 
-  Alpha by significant or not
```{r}
both_sites_params <- all_C_params %>%
  bind_rows(all_V_params) 

bothsites_standardized_effects <- both_sites_params %>%
  mutate(Parameter = factor(Parameter, levels = c("Salinity","pH","Total Alkalinity", "Nitrate", "Phosphate"))) %>% # put the levels in an order I want for plotting
  ggplot(aes(x = estimate, 
             y = Parameter, 
             color = Site, 
             alpha= Significant))+
  geom_vline(xintercept = 0, linetype = 2) +
  geom_point(size = 4, 
             position = position_dodge(0.9)) + # dodge the points so not on top of each other
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0, position = position_dodge(0.9)) +
  scale_color_manual(values=c("goldenrod", "firebrick")) +
  scale_alpha_manual(values = c(0.47,1), 
                     guide = "none") +
  labs(x = "Standardized Effect",
       y = "") +
  theme_classic() +
  theme(legend.text = element_text(size = 14),
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 12)) 
  
bothsites_standardized_effects

ggsave(here::here("Outputs", "PaperFigures", "bothsites_standardized_effects.jpg"), 
       width=12, height=10)
  
```


