---
title: "ThesisDefense_RawGW_SW_plots"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# This script was dedicated to creating plots used in Figure 2 of the paper, which show the comparison of collected groundwater from Varari and Cabral compared to ambient seawater for several environmental parameters. 

## Load libraries
```{r, echo=FALSE}
library(tidyverse)
```


## Read in data 
```{r, echo=FALSE, message=FALSE}

MooreaMarch_full <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/March2022/Allbiogeochemdata_QC_march_fdom2.csv")
MooreaAugust2 <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/August2021/Allbiogeochemdata_QC2.csv")

## use this to try and get ambient SW TA and nutrients 
CarbonateChem <- read_csv("https://raw.githubusercontent.com/njsilbiger/MooreaSGD_site-selection/main/Data/March2022/CarbonateChemistry/pHProbe_Data_calculated_POcorrect.csv")

```


## Tidy data 
```{r, message=FALSE}

MooreaAugust2_edit <- MooreaAugust2 %>% 
  select(-c(,2:7,10:14,16,24:30))
MooreaMarch_edit <- MooreaMarch_full %>% 
  select(-c(,2:7,10:14,16,24:30))

MooreaAugust_addedOffshore <- MooreaMarch_edit %>%  
  full_join(MooreaAugust2_edit) %>% 
  pivot_longer(cols= Salinity:Ammonia_umolL, names_to = "Parameter") 

```

## Create df of specific params 
```{r}

################
## Ambient SW 
################
AmbSW <- MooreaAugust_addedOffshore %>% 
  filter(Plate_Seep == "Offshore", 
         Parameter == "Silicate_umolL") 

max(AmbSW$value, na.rm=TRUE)
min(AmbSW$value, na.rm=TRUE) 

################
## Cabral
################
CabralGW <- MooreaAugust_addedOffshore %>% 
  filter(Location=="Cabral",
         Parameter == "TA", 
         Plate_Seep=="Spring") 

max(CabralGW$value, na.rm=TRUE)
min(CabralGW$value, na.rm=TRUE) 

################
## Varari
################
VarariGW <- MooreaAugust_addedOffshore %>% 
  filter(Location=="Varari",
         Parameter == "TA", 
         Plate_Seep=="Spring") 

max(VarariGW$value, na.rm=TRUE)
min(VarariGW$value, na.rm=TRUE) 

################
## Code for values used 
################

### Salinity: Min 
### pH: Min
### NN: Max
### TA: Max
### Silicate: Max


sitecomparison_maxdata <- tribble(~Site, ~Parameter, ~Value, 
        "Varari", "pH", "7.18", 
        "Cabral", "pH", "6.89", 
        "Offshore", "pH", "7.92", 
        "Varari", "Nitrates (umol/L)", "279.15", 
        "Cabral", "Nitrates (umol/L)", "32.50", 
        "Offshore", "Nitrates (umol/L)", "0.58", 
        "Varari", "TA (umol/kg)", "3813.31", 
        "Cabral", "TA (umol/kg)", "1959.29", 
        "Offshore", "TA (umol/kg)", "2386.84", 
        "Varari", "Salinity", "2.89", 
        "Cabral", "Salinity", "0.44", 
        "Offshore", "Salinity", "36.29",
        "Varari", "Silicate (umol/L)", "713.06", 
        "Cabral", "Silicate (umol/L)", "868.38", 
        "Offshore", "Silicate (umol/L)", "3.68") %>% 
  mutate(Site= as.factor(Site))



```


# Using MY data instead 
-  used nutrient data from my raw gw collected in Chapter 1 
-  TA data though is still from Nyssa (max values from either March OR August) 
-  Only value for NN, Silicate, pH, Salinity for Varari and Cabral, min for offshore for salinity and pH (taken from my records), and max for NN and silicate from March 2022 data 

```{r}
Hannah_endmemberdata <- tribble(~Site, ~Parameter, ~Value, 
        "Varari", "Nitrates (umol/L)", 42.49, 
        "Cabral", "Nitrates (umol/L)", 8.22, 
        "Ambient", "Nitrates (umol/L)", 0.58, 
        "Varari", "Silicate (umol/L)", 725.61, 
        "Cabral", "Silicate (umol/L)", 855.01, 
        "Ambient", "Silicate (umol/L)", 3.68, 
        "Varari", "Salinity", 1.70, 
        "Cabral", "Salinity", 0.90, 
        "Ambient", "Salinity", 36.29,
        "Varari", "pH", 7.87, 
        "Cabral", "pH", 7.53, 
        "Ambient", "pH", 8.18,
        "Varari", "TA (umol/kg)", 3813.31, 
        "Cabral", "TA (umol/kg)", 1335.71, 
        "Ambient", "TA (umol/kg)", 2386.84, 
        "Varari", "Phosphate (umol/L)", 2.50, 
        "Cabral", "Phosphate (umol/L)", 3.61, 
        "Ambient", "Phosphate (umol/L)", 0.20) %>% 
  mutate(Site= as.factor(Site))

```

## Plots 

```{r}
## nitrates 
SiteComparisons_Nitrates <- Hannah_endmemberdata %>% 
  filter(Parameter=="Nitrates (umol/L)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = expression(Nitrate+Nitrite~(mu*mol~L^-1))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Nitrates
ggsave(here::here("Outputs", "PaperFigures","Nitrates_GW.jpg"),
       width=10, height=7)


## silicate 
SiteComparisons_Silicate <- Hannah_endmemberdata %>% 
  filter(Parameter=="Silicate (umol/L)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = expression(Silicate~(mu*mol~L^-1))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Silicate
ggsave(here::here("Outputs", "PaperFigures","Silicate_GW.jpg"),
       width=10, height=7)


## salinity 
SiteComparisons_Salinity <- Hannah_endmemberdata %>% 
  filter(Parameter=="Salinity") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = expression(Salinity~(psu))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Salinity
ggsave(here::here("Outputs", "PaperFigures","Salinity_GW.jpg"),
       width=10, height=7)

## pH 
SiteComparisons_pH <- Hannah_endmemberdata %>% 
  filter(Parameter=="pH") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = "pH") + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25)) + 
 coord_cartesian(ylim = c(7, 8))


SiteComparisons_pH
ggsave(here::here("Outputs", "PaperFigures","pH_GW.jpg"),
       width=10, height=7)

## TA 
SiteComparisons_TA <- Hannah_endmemberdata %>% 
  filter(Parameter=="TA (umol/kg)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = expression(TA~(mu*mol~kg^-1))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_TA
ggsave(here::here("Outputs", "PaperFigures","TA_GW.jpg"),
       width=10, height=7)

## Phosphate 
SiteComparisons_Phosphate <- Hannah_endmemberdata %>% 
  filter(Parameter=="Phosphate (umol/L)") %>% 
  ggplot(aes(x=Site,
             y=Value, 
             fill=Site)) + 
  geom_col()  + 
  scale_x_discrete(limits = c("Ambient", "Cabral", "Varari")) + 
  scale_fill_manual(values=c("deepskyblue3", "darkgoldenrod2", "firebrick4"), 
                    limits=c("Ambient", "Cabral", "Varari")) +
  theme_classic() + 
  labs(x="",
       y = expression(Phosphate~(mu*mol~L^-1))) + 
  theme(axis.text.x=element_text(size=25), 
        axis.text.y=element_text(size=25), 
        axis.title.x=element_text(size=25), 
        axis.title.y=element_text(size=25))

SiteComparisons_Phosphate
ggsave(here::here("Outputs", "PaperFigures","Phos_GW.jpg"),
       width=10, height=7)
```

