---
title: "Models_Plots_WSN"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

```{r, echo=FALSE}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
library(agricolae)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(flextable)
library(performance)
library(agricolae)
library(ggeffects)
library(sjPlot)
library(patchwork)
library(broom)
library(purrr)
library(nlstools)
library(stringr)
```


## Loading the data and creating dfs 
```{r}
RespoMeta <- read_csv(here("Data","RespoFiles","Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))
BioData <- read_csv(here("Data","RespoFiles","Fragment_MeasurementSampling_Cabral_Varari.csv"))
Sample_Info <- left_join(RespoMeta, BioData)

RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
#View(RespoR)

####################
### pH data #########
######################
pHcalib<-read_csv(here("Data","TrisCal_20230614.csv")) #%>% ## tris cal date is listed as a character here - make sure change in Excel file before reading in so it is a date 
pHcalib <- pHcalib[-c(13,14), ]

#View(pHcalib)

pHData <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) 
pHData <- pHData[-c(294,303,435),]
pHData <- pHData[,-(14:17)]

#View(pHData)

pHSlope<-pHcalib %>%
  #filter(HOBO_Orion =="Orion") %>% # extract only the orion data
  nest_by(TrisCalDate) %>%
  dplyr::mutate(fitpH = list(lm(mVTRis~Ttris, data = data))) %>% # linear regression of mV and temp of the tris
  dplyr::summarise(broom::tidy(fitpH)) %>% # make the output tidy
  select(TrisCalDate, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>% # put slope and intercept in their own column
  right_join(.,pHData) %>% # join with the pH sample data
  mutate(mVTRis = temp_C*Ttris + `(Intercept)`) %>% 
  mutate(new_pH = pH(Ex=mV,Etris=mVTRis,S=salinity,T=temp_C)) # calculate pH of the samples using the pH seacarb function

#View(pHSlope)
######### Respo table #############
RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 650-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date_block= factor(date)) #make the blank column a factor

#View(RespoR2)
```


## Normalize to Blanks 
- things to consider here: try both ways 
- 1. average across all the days and get one point for each dilution 
- 2. keep it how it is - grouped by date_block (i think this is more correct)
```{r}
RespoR_Normalized_blankperday <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)


## two options: 1) summarise across all 4 days 2) direct comparison day to day 
## look at individual blank values to see if any of the days are particularly off - if everything looks consistent, can stick with individual days 
# take out date_block in group by and then change summarise function - to average all blanks by all dilutions 
# go back and check for blank volume to make sure full chamber vol 

### plot colonies against blanks ######
plot_Blank_Rates <- RespoR_Normalized_blankperday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark, scales="free_y")

```

### Option 2 for Blanks - averaging  
```{r}

RespoR_Normalized_avgblanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)

### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- RespoR_Normalized_avgblanks %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

```

## Now combine into two dfs - one based on per day blank rates and the other based on averaged blank rates 
```{r}

#joining with per day blanks 

RespoR_Normalized_blankperday_joined <- RespoR_Normalized_blankperday %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         umol.cm2.hr_uncorr = (umol.sec*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr)

#join with Tris pH data 
TrispH_RespoRNormalized_perdayBlanks <- RespoR_Normalized_blankperday_joined %>% 
  left_join(pHSlope)



```

### BASED ON WHAT BLANKS TO USE -  calculate R, GP, and NP 
- RIGHT NOW: using blanks per day

```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- TrispH_RespoRNormalized_perdayBlanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1,
         umol.cm2.hr_uncorr = umol.cm2.hr_uncorr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") # all dark run rates get R for respiration

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- TrispH_RespoRNormalized_perdayBlanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP")

# rejoin data into single df
RespoR_Normalized2 <- full_join(RespoR_Normalized_light, RespoR_Normalized_dark) #%>% 
#drop_na(mmol.gram.hr) # removes anticipated sampleID's that were not actually run


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(new_colonynumber, SGD_number, site, date, salinity, new_pH) %>% 
  summarize(umol.cm2.hr = sum(umol.cm2.hr),
            umol.cm2.hr_uncorr = sum(umol.cm2.hr_uncorr)) %>% # NP + R = GP
            #Temp.C = mean(Temp.C)) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(new_colonynumber, new_pH, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, umol.cm2.hr_uncorr) %>% 
  full_join(RespoR_NormalizedGP) %>% 
  filter(new_colonynumber!=20)


## what is wrong with Cabral 20? 
Cabral20 <- RespoR_Normalized_Full %>%
 filter(site=="Cabral") %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  facet_wrap(~new_colonynumber, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(trans="log10") 
  #labs(title="Respiration Normalized to Blanks for SGD Dils per colony")



write_csv(RespoR_Normalized_Full , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))  

```


## Creating models to run stats - starting with Respiration 

```{r}
####################################
#### Respiration for SGD 
###################################

#########################
### for Cabral 
RData_C <- RespoR_Normalized_Full %>% 
  filter(P_R == "R") %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity=as.factor(salinity))

## date nested within random effect of colony number 
model2_SGDbyR <- lmer(data = RData_C, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(model2_SGDbyR) 
summary(model2_SGDbyR)
ranef(model2_SGDbyR)

#######################
#### for Varari 
RData_V <- RespoR_Normalized_Full %>% 
  filter(P_R == "R") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity=as.factor(salinity))

## date nested within random effect 
model2_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))

anova(model2_SGDbyR_V) 
summary(model2_SGDbyR_V)
ranef(model2_SGDbyR)
AIC(model2_SGDbyR_V)


```

### Models for GP data 

```{r}
####################################
#### Gross Production for SGD 
###################################

#######################
#### for Varari 
GPData_V <- RespoR_Normalized_Full %>% 
  filter(P_R == "GP") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity=as.factor(salinity)) %>% 
  select(,1,3:10) %>% 
  drop_na()

## date nested within random effect 
model_SGDbyGP_V <- lmer(data = GPData_V, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))

anova(model_SGDbyGP_V) 
summary(model_SGDbyGP_V)
ranef(model_SGDbyGP_V)
AIC(model_SGDbyGP_V)

### for Cabral 
GPData_C <- RespoR_Normalized_Full %>% 
  filter(P_R == "GP") %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity=as.factor(salinity))

## date nested within random effect of colony number 
model2_SGDbyGP_C <- lmer(data = GPData_C, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(model2_SGDbyGP_C) 
summary(model2_SGDbyGP_C)
ranef(model2_SGDbyGP_C)

```


### Plotting results from models 
```{r}
# plot GP and R separetly and then use patchwork to bring them together so that can include free scale y axes and linear regression lines  

## Varari Respiration 
Respiration_SGD_V <- RespoR_Normalized_Full %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity), position = position_jitterdodge()) + 
  theme_bw() + 
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration for Varari") 

Respiration_SGD_V

## Cabral respiration 
Respiration_SGD_C <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="R") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity), position = position_jitterdodge()) + 
  theme_bw() + 
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration for Cabral") 

Respiration_SGD_C


##############################################

## Varari Gross Production 
GP_SGD_V <- RespoR_Normalized_Full %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity), position = position_jitterdodge()) + 
  theme_bw() + 
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP for Varari") 

GP_SGD_V

## Cabral GP 

GP_SGD_C <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity), position = position_jitterdodge()) + 
  theme_bw() + 
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "GP for Cabral") 

GP_SGD_C

#################################################

## bring in NEC data 


##############################################

#time to patch together for Varari 

GP_SGD_V + Respiration_SGD_V







```
## Calculating TA 
```{r}
calc.data <- read_csv(here("Data", "Titrations", "Calc_TArates.csv"))

######### create new data frame of just the initial data, pull out initial data from sample.type
rows.initial <- which(calc.data$Sample_Type == "Initial") #tells you all the rows that you have with initial
initial <- calc.data[rows.initial,]
calc.data <- calc.data[-rows.initial,] #to remove the rows with initial data

######## remove and create new data frame with just blanks
rows.blanks <- which(calc.data$Sample_Type == "Blank") #tells you all the rows that you have with blanks
blanks <-calc.data[rows.blanks,]
calc.data <- calc.data[-rows.blanks,] #to remove the rows with blank data

######## need to join sample data frame, join initial with your calc.data, only by temperature, pull out the columns we need
initial <- initial[, c("date","temp_C", "salinity_insitu", "salinity_inlab", "TA")] ##if need to use pH then can re-add here but do I need this ?? for TA calc 

names(initial)[3:6] <- paste0(names(initial)[3:6], "_initial") #use this to rename all of our columns

###### join blanks and carb chem data frame
calc.data <- left_join(calc.data, initial) #joing the initials to my data frame for carb chem
blanks <- left_join(blanks,initial)

###### figure out delta TA, initial-final
blanks$delta.TA.blank <- blanks$TA_initial - blanks$TA

####### getting the averages of blanks for each date and colony/treatment 
mean.blanks <- blanks %>% 
  group_by(date, temp_C) %>% #### SAMPLE ID IS CAUSING PROBLEMS WHEN TRYING TO JOIN TO JOIN BY TEMP WHICH IS ALSO UNIQUE 
  summarise(mean.blanks=mean(delta.TA.blank)) 

calc.data <- left_join(calc.data, mean.blanks) #bring in mean blanks to calc.data

######## need to join in SA,volume data and time data by fragment ID, before calculating NEC
sample.data <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) #bring in SA and volume data sheet

SA <- sample.data[, c("sample_ID", "SA_cm2", "volume_mL")] #pull out the necessary columns and treatment 

SA2 <- SA %>%
 dplyr::mutate(light_dark = str_extract(sample_ID, "[^_]+$")) #split the sample_ID at the underscore to delete the Dark values

######## steps to organize and delete D values
rows.Dark <- which(SA2$light_dark == "Dark") #tells you all the rows that you have with blanks
Dark <-SA2[rows.Dark,] 
SA <- SA2[-rows.Dark,] #to remove the rows with dark data, now have data sheet with only light, SA and volume values
SA[,4] = NULL #had to delete the light-dark column to allow to just join by fragment.ID

calc.data2 <- left_join(calc.data, SA)

######## bring in the time data from resp.data sheet
resp.data <- read_csv(here("Data", "RespoFiles", "Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))

######### need to organize and first delete the dark information
rows.dark2 <- which(resp.data$light_dark == "DARK") #tells you all the rows that you have with blanks
dark2 <-resp.data[rows.dark2 ,] 
resp.data <- resp.data[-rows.dark2,]

####### pull out columns that we want to use for our bind to the calc.data2 sheet
time.data <- resp.data[, c("sample_ID","SGD_dil", "start_time", "stop_time")] 
full.calc.data <- left_join(calc.data2, time.data)

######### NOW calculate the NEC rate
full.calc.data$deltaTA<- (full.calc.data$TA_initial - full.calc.data$TA) - full.calc.data$mean.blanks
full.calc.data$timediff <- as.numeric((full.calc.data$stop_time - full.calc.data$start_time)) 

########## make a row that has rate.type for "C" assigned to light 
full.calc.data$rate.type <-ifelse(full.calc.data$light_dark=='LIGHT', "C")
#view(full.calc.data)


########## equation to calculate NEC rates 
full.calc.data$umol.cm2.hr<-((full.calc.data$deltaTA/2)*(1.023)*(full.calc.data$volume_mL))/((full.calc.data$SA_cm2)*(full.calc.data$timediff))
```

### Plot NEC 
```{r}
## now plot NEC by SGD - tried joining dfs 
#RespoR_Normalized_Full_joinedNEC <- full.calc.data
#  left_join(RespoR_Normalized_Full)
  
##############
## NEC for Cabral 
  
NEC_C <- full.calc.data %>%
  filter(site=="Cabral") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity_insitu), position = position_jitterdodge()) + 
  theme_bw() + 
  theme(strip.background = element_rect(fill = "white"))+
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  geom_hline(yintercept = 0)+
  facet_wrap(~site, scales = "free_y") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "NEC at Cabral") 
  
NEC_C

##############
## NEC for Varari 

NEC_V <- full.calc.data %>%
  filter(site=="Varari") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_jitter(aes(color=salinity_insitu), position = position_jitterdodge()) + 
  theme_bw() + 
  theme(strip.background = element_rect(fill = "white"))+
  geom_smooth(method = "lm", se=FALSE, color="lightpink") +
  geom_hline(yintercept = 0)+
  facet_wrap(~site, scales = "free_y") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "NEC at Varari") 
  
NEC_V

```

## Models for NEC 
```{r}

#### NEC for Cabral 
NECData_C <- full.calc.data %>% 
  #filter(P_R == "GP") %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity_insitu=as.factor(salinity_insitu))

model_SGDbyNEC_C <- lmer(data = NECData_C, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(model_SGDbyNEC_C) 
summary(model_SGDbyNEC_C)
ranef(model_SGDbyNEC_C)


## NEC for Varari 
NECData_V <- full.calc.data %>% 
  #filter(P_R == "GP") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date), 
         SGD_number=as.factor(SGD_number), 
         salinity_insitu=as.factor(salinity_insitu))

model_SGDbyNEC_V <- lmer(data = NECData_V, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))

anova(model_SGDbyNEC_V) 
summary(model_SGDbyNEC_V)
ranef(model_SGDbyNEC_V)


```

