---
title: "Plots_Models_PhysioParams"
author: "Hannah Merges"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

## Load libraries 
```{r, echo= FALSE}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
library(agricolae)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(flextable)
library(performance)
library(agricolae)
library(ggeffects)
library(sjPlot)
```

### Taking RespoR table from original script/for loop and loading it here
-  Plus all the pther DFs so things will knit properly 

```{r}
RespoMeta <- read_csv(here("Data","RespoFiles","Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))
BioData <- read_csv(here("Data","RespoFiles","Fragment_MeasurementSampling_Cabral_Varari.csv"))
Sample_Info <- left_join(RespoMeta, BioData)

RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
#View(RespoR)

####################
### pH data #########
######################
pHcalib<-read_csv(here("Data","TrisCal_20230614.csv")) #%>% ## tris cal date is listed as a character here - make sure change in Excel file before reading in so it is a date 
pHcalib <- pHcalib[-c(13,14), ]

#View(pHcalib)

pHData <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) 
pHData <- pHData[-c(294,303,435),]
pHData <- pHData[,-(14:17)]

#View(pHData)

pHSlope<-pHcalib %>%
  #filter(HOBO_Orion =="Orion") %>% # extract only the orion data
  nest_by(TrisCalDate) %>%
  dplyr::mutate(fitpH = list(lm(mVTRis~Ttris, data = data))) %>% # linear regression of mV and temp of the tris
  dplyr::summarise(broom::tidy(fitpH)) %>% # make the output tidy
  select(TrisCalDate, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>% # put slope and intercept in their own column
  right_join(.,pHData) %>% # join with the pH sample data
  mutate(mVTRis = temp_C*Ttris + `(Intercept)`) %>% 
  mutate(new_pH = pH(Ex=mV,Etris=mVTRis,S=salinity,T=temp_C)) # calculate pH of the samples using the pH seacarb function

#View(pHSlope)
######### Respo table #############
RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 650-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date_block= factor(date)) #make the blank column a factor

#View(RespoR2)
```

### Now try to average the blanks 
-  Have been having trouble with getting this to a point that I feel confident about 
-  Questions: am I supposed to have one point for each dilution from all the days combined?? Or one day? 
```{r}
RespoR_Normalized_AvgBlanks_blankonly <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% # get mean value of blanks per each dilution across all days?
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)

### plot colonies against blanks ######
plot_Blank_Rates <- RespoR_Normalized_AvgBlanks_blankonly %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)


RespoR_Normalized_AvgBlanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% # get mean value of blanks per each dilution across all days?
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site) %>%  ## rename the blank column 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  #arrange(FileID_csv) %>% 
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         umol.cm2.hr_uncorr = (umol.sec*3600)/SA_cm2) %>% 
         #mmol.cm2.hr = 0.001*(umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1 --> converting to mmol was for Danielle Barnas work - Dani B left hers in umol units 
         #mmol.cm2.hr_uncorr = 0.001*(umol.sec*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, run_block, SA_cm2, run_block, umol.cm2.hr, chamber_channel, 
                Temp.C, umol.cm2.hr_uncorr, new_colonynumber, salinity, pH, site, SGD_number)

#View(RespoR_Normalized_AvgBlanks)

## try to join in new pH data here## 
TrispH_RespoRNormalized_AvgBlanks <- RespoR_Normalized_AvgBlanks %>% 
  left_join(pHSlope)

#View(TrispH_RespoRNormalized_AvgBlanks)

### try to plot lines 92-95 #######
#RespoR_Normalized_AvgBlanks <- RespoR2 %>% 
#  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
 # filter(new_colonynumber== "BLANK")
#
#plot_RespoR_Normalized_AvgBlanks <- RespoR_Normalized_AvgBlanks %>% 
#  ggplot(aes(x=SGD_number, 
           #  y=umol.cm2.hr)) +
 # scale_x_continuous(trans="log10") +
 # geom_point() + 
 # facet_wrap(site~light_dark)

```

### Plot to see if averaged blanks worked out and only have one per SGD dilution 
```{r}
### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- TrispH_RespoRNormalized_AvgBlanks %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

##there are still multiple points even tho it is supposed to be taking an average 

#View(TrispH_RespoRNormalized_AvgBlanks) 
########## PLOT COLONY NUMBER BY BLNAKS #########
plot_Blank_Rates_Averaged <- TrispH_RespoRNormalized_AvgBlanks %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

```

### Once blanks are sorted - use that dataset to calculate R, GP, and NP 
```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- TrispH_RespoRNormalized_AvgBlanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1,
         umol.cm2.hr_uncorr = umol.cm2.hr_uncorr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") # all dark run rates get R for respiration

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- TrispH_RespoRNormalized_AvgBlanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP")

# rejoin data into single df
RespoR_Normalized2 <- full_join(RespoR_Normalized_light, RespoR_Normalized_dark) #%>% 
#drop_na(mmol.gram.hr) # removes anticipated sampleID's that were not actually run


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(new_colonynumber, SGD_number, site, date, salinity, new_pH) %>% 
  summarize(umol.cm2.hr = sum(umol.cm2.hr),
            umol.cm2.hr_uncorr = sum(umol.cm2.hr_uncorr)) %>% # NP + R = GP
            #Temp.C = mean(Temp.C)) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(new_colonynumber, new_pH, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, umol.cm2.hr_uncorr) %>% 
  full_join(RespoR_NormalizedGP)


write_csv(RespoR_Normalized_Full , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))  

#View(RespoR_Normalized_Full)

```

### Visualizing Respiration rates via plots 
```{r}
RespoR_Normalized_Full <- read_csv(here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))

my_pal <- pnw_palette(name="Starfish",n=2,type="discrete")


##### look at umol by colony numbers for RESPIRATION 
SGDdil_bycolony <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, ##switched to umol but values are still off? 
             color=new_colonynumber)) + ## colony number breakdowns: 1-8=Varari, 13-20=Cabral
  facet_wrap(site~new_colonynumber, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="Respiration Normalized to Avg Blanks for SGD Dils per colony")

```
#### GP 
```{r}
##### GP Rates based on SGD Dils #########
RatesPlot_GP_SGD <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  facet_wrap(site~new_colonynumber, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="GP Rates for SGD Dils")
ggsave(here("Outputs", "PrelimOutputs","GPRates_SGDdils.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_SGD
```

### Salinity plots 
```{r}
## Gross Photosynthesis with salinity 
RatesPlot_GP_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  facet_wrap(site~new_colonynumber, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(title="GP by Salinity")
ggsave(here("Outputs", "PrelimOutputs","GPRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_salinity

## Respiration with salinity 
RatesPlot_R_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  geom_smooth(method = "lm") +
  facet_wrap(site~new_colonynumber, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title="Respiration by Salinity")
ggsave(here("Outputs", "PrelimOutputs","RRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_R_salinity

######################################
## trying with grouped salinity, same as did with pH 
########################################
salinity_combined <- RespoR_Normalized_Full %>% 
  #filter(site=="Varari") %>% 
  group_by(SGD_number, date) 

## Respiration with salinity 
RatesPlot_R_GroupedSalinity <- salinity_combined %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  geom_smooth(method = "lm") +
  facet_wrap(site~new_colonynumber, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title="Respiration by (Grouped) Salinity")
ggsave(here("Outputs", "PrelimOutputs","RRates_Salinity2.jpg"), 
       width = 10, height = 10)

RatesPlot_R_GroupedSalinity

RatesPlot_GP_GroupedSalinity <- salinity_combined %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  facet_wrap(site~new_colonynumber, scales = "free") +
  labs(title="GP by (Grouped) Salinity")
ggsave(here("Outputs", "PrelimOutputs","GPRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_GroupedSalinity

```

#### Now with pH 
```{r}
## need to show pH by day rather than colony 
pH_combined <- RespoR_Normalized_Full %>% 
  #filter(site=="Varari") %>% 
  group_by(SGD_number, date) 

RatesPlot_GP_pH <- pH_combined %>%
  filter(P_R == "GP") %>% 
   ggplot(aes(x=new_pH, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(site~new_colonynumber, scale = "free") +
  geom_smooth(method = "lm") +
  geom_point()+ 
  labs(title="GP by pH")
ggsave(here("Outputs", "PrelimOutputs","GP_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_pH

RatesPlot_R_pH <- pH_combined %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=new_pH, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(site~new_colonynumber, scale = "free") +
  geom_smooth(method = "lm")+
  geom_point() +
  labs(title="Respiration by pH")
ggsave(here("Outputs", "PrelimOutputs","R_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_R_pH

######## now try with salinity and pH plotted against each other #######
RatesPlot_R_SalpH <- RespoR_Normalized_Full %>%
  #filter(P_R == "R") %>%
  ggplot(aes(x=new_pH, 
             y=salinity, 
             color=new_colonynumber)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(site~new_colonynumber, scale = "free") +
  geom_smooth(method = "lm")+
  geom_point() +
  labs(title="Salinity by pH")
ggsave(here("Outputs", "PrelimOutputs", "Salinity_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_R_SalpH

## how are pH and salinity correlated ? is pH affecting salinity? 

```
#### Calculate GP:R ratios 

```{r}

wide_RespoRNormalizedFull <- RespoR_Normalized_Full %>% 
  dplyr::select(P_R, umol.cm2.hr, site, new_colonynumber, SGD_number) %>%
  pivot_wider(id_cols = c(site, new_colonynumber, SGD_number),names_from=P_R, values_from=umol.cm2.hr) %>% 
  mutate(GP_R_Ratio=R/GP)

########## now plot the GP:R ratio ######## 
RatesPlot_GPR <- wide_RespoRNormalizedFull %>%
  ggplot(aes(x=SGD_number, 
             y=GP_R_Ratio, 
             color=new_colonynumber)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(site~new_colonynumber, scale = "free") +
  geom_smooth(method = "lm")+
  geom_point() +
  labs(title="GP:R")

RatesPlot_GPR

#View(wide_RespoRNormalizedFull)

```

### Show stats via models - R and GP:R first 

```{r}
#### GP:R ratio 
#testRData <- wide_RespoRNormalizedFull %>% 
 # filter(site=="Cabral") %>% 
 # drop_na() %>% 
  #mutate(new_colonynumber= as.factor(new_colonynumber))
          #date=as.factor(date))
#View(wide_RespoRNormalizedFull)

#model_GPbyR <- lmer(data = testRData, 
             #GP_R_Ratio ~ SGD_number + (1|new_colonynumber))

#anova(model_GPbyR) 
#summary(model_GPbyR)

##### Respiration by site ###########
## Cabral first 
RData_C <- RespoR_Normalized_Full %>% 
  filter(P_R == "R") %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

## date as an interaction 
model_SGDbyR <- lmer(data = RData_C, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyR) 
summary(model_SGDbyR)
#ranef(model_SGDbyR)

## without date 
model2_SGDbyR <- lmer(data = RData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR) 
summary(model2_SGDbyR)
#ranef(model2_SGDbyR)

### R by salinity 
model_RbySalinity <- lmer(data = RData, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity) 
summary(model_RbySalinity)
ranef(model_RbySalinity)

### R by pH 
model_RbypH <- lmer(data = RData, 
             umol.cm2.hr ~ new_pH + (1|new_colonynumber/date))
             
anova(model_RbypH) 
summary(model_RbypH)
ranef(model_RbypH)

########### then Varari ################ 
RData_V <- RespoR_Normalized_Full %>% 
  filter(P_R == "R") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

## date as an interaction 
model_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyR_V) 
summary(model_SGDbyR_V)
#ranef(model_SGDbyR)

## without date 
model2_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR_V) 
summary(model2_SGDbyR_V)
#ranef(model2_SGDbyR)

### R by salinity 
model_RbySalinity_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity_V) 
summary(model_RbySalinity_V)
ranef(model_RbySalinity_V)

### R by pH 
model_RbypH_V <- lmer(data = RData, 
             umol.cm2.hr ~ new_pH + (1|new_colonynumber/date))
             
anova(model_RbypH_V) 
summary(model_RbypH_V)
ranef(model_RbypH_V)

```

## AIC for R models 

```{r}
AIC(model_RbypH_V)
AIC(model_RbypH)

AIC(model2_SGDbyR_V)
AIC(model_SGDbyR_V) 
AIC(model_SGDbyR) ## this is lowest AIC value, 693 
AIC(model2_SGDbyR)

AIC(model_RbySalinity_V)
AIC(model_RbySalinity)
```


### next GP models 

```{r}
##### Gross Photosynthesis by site ###########
## Cabral first 
GPData_C <- RespoR_Normalized_Full %>% 
  filter(P_R == "GP") %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

## date as an interaction 
model_SGDbyGP <- lmer(data = GPData_C, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyGP) 
summary(model_SGDbyGP)
#ranef(model_SGDbyR)

## without date 
model2_SGDbyGP <- lmer(data = GPData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyGP) 
summary(model2_SGDbyGP)
#ranef(model2_SGDbyGP)

### GP by salinity 
model_GPbySalinity <- lmer(data = GPData_C, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_GPbySalinity) 
summary(model_GPbySalinity)
ranef(model_GPbySalinity)

### GP by pH 
model_GPbypH <- lmer(data = GPData_C, 
             umol.cm2.hr ~ new_pH + (1|new_colonynumber/date))
             
anova(model_GPbypH) 
summary(model_GPbypH)
ranef(model_GPbypH)

########### then Varari ################ 
GPData_V <- RespoR_Normalized_Full %>% 
  filter(P_R == "GP") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

## date as an interaction 
model_SGDbyGP_V <- lmer(data = GPData_V, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyGP_V) 
summary(model_SGDbyGP_V)
#ranef(model_SGDbyGP_V)

## without date 
model2_SGDbyGP_V <- lmer(data = GPData_V, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))

anova(model2_SGDbyGP_V) 
summary(model2_SGDbyGP_V)
#ranef(model2_SGDbyGP_V)

### GP by salinity 
model_GPbySalinity_V <- lmer(data = GPData_V, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_GPbySalinity_V) 
summary(model_GPbySalinity_V)
ranef(model_GPbySalinity_V)
#check_model(model_GPbySalinity_V)

### GP by pH 
model_GPbypH_V <- lmer(data = GPData_V, 
             umol.cm2.hr ~ new_pH + (1|new_colonynumber/date))
             
anova(model_GPbypH_V) 
summary(model_GPbypH_V)
ranef(model_GPbypH_V)
#check_model(model_GPbypH_V)
```

## Comparing AIC values for GP models 

```{r}
## AIC for GP models 

AIC(model_GPbySalinity_V)
AIC(model_GPbySalinity)

AIC(model2_SGDbyGP_V)
AIC(model_SGDbyGP_V) ##lowest AIC (only one in the 500s)
AIC(model2_SGDbyGP)
AIC(model_SGDbyGP)

AIC(model_GPbypH)
AIC(model_GPbypH_V)

# all significantly different between sites and between treatments 


```
#### Making models to test different interactions with salinity and pH and eventually other parameters 

```{r}
##################################
## mixed model regression with env params #### 
###### Models for GP_R ratio #######
GPR_Ratio <- wide_RespoRNormalizedFull %>% 
  filter(site=="Cabral") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber)) 
         #date=as.factor(date))

GP_R_model <- lmer(data = GPR_Ratio, 
             GP_R_Ratio ~ SGD_number + (1|new_colonynumber))

anova(GP_R_model) 
summary(GP_R_model)

check_model(GP_R_model)

## salinity and pH as random effects 
RData_V_envparam <- RespoR_Normalized_Full %>% 
  filter(P_R == "R") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

model_RData_V_envparam <- lmer(data = RData_V_envparam, 
             umol.cm2.hr ~ salinity + new_pH + (1|new_colonynumber/date))

anova(model_RData_V_envparam)
summary(model_RData_V_envparam)
ranef(model_RData_V_envparam)

######### tidying model results ########
#tidymodels <- tidy(model4)
#tidymodels

#results <- glance(model4)
#results





```

##### Making polynomial regression models

```{r}
polymodel_SGDbyR <- lmer(data = RData, 
             umol.cm2.hr ~ poly(SGD_number, degree=2) + 1|new_colonynumber/date)

anova(polymodel_SGDbyR) 
summary(polymodel_SGDbyR)
#check_model(polymodel_SGDbyR)
```

### Just using SGD number and salintiy in models, try to figure out how to plot for digestable results 
```{r}
model_RbySalinity <- lmer(data = RData_C, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity) 
summary(model_RbySalinity)
ranef(model_RbySalinity)

model2_SGDbyR <- lmer(data = RData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR) 

### WHEN RUNNING DATE AS AN INTERACTION: THERE IS SIGNFICANT EFFECT OF DATE 

model_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyR_V) 
summary(model_SGDbyR_V)

### no significance of SGD with date as rnadom effect 
model2_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR_V) 
summary(model2_SGDbyR_V)

##nor by pH 
model_RbySalinity_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity_V) 
summary(model_RbySalinity_V)


############ FOR GP #############
## almost significant effect og SGD on GP rates, just barely over 
model2_SGDbyGP <- lmer(data = GPData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyGP) 
plot(model2_SGDbyGP)
#qqp(model2_SGDbyGP)


## no significant effect of salinity at Cabral or Varari 

## BUT THERE IS A SIGNIFICANT EFFECT OF PH ON GP AT VARARI 

#### plot models for presentation style ######
plot <- ggpredict(model2_SGDbyGP, terms = c("SGD_number", "umol.cm2.hr", "new_colonynumber", "date"),
                  type="re") %>% 
  plot() + 
  labs(x="Test", 
       y="Testing") + 
  scale_fill_viridis()
library(tidyverse)

```

### Trying new plots #### 
```{r}
# plot GP, NP and R
my_pal <- pnw_palette(name="Starfish")

AllRatesPlot_SGD <- RespoR_Normalized_Full %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr,
             color = SGD_number))+
  #scale_x_continuous(trans="log10") + 
  #geom_boxplot(aes(color = SGD_number),
              # outlier.shape = NA)+ 
  geom_jitter(aes(color = SGD_number), position = position_jitterdodge()) + 
  theme_bw()+
  #geom_text_repel(aes(label = SampleID), size = 2.5, max.overlaps = 15) +
  theme(strip.background = element_rect(fill = "white"))+
  labs(x = "Environmental Treatment (SGD Level)",
       color = "SGD_number",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Rate of O2 production or consumption") +
  #scale_color_manual(values=my_pal) +
  facet_wrap(~ P_R, scales = "fixed")
AllRatesPlot_SGD

ggsave(here("Outputs", "RespoOutput","AllRatesPlot_SGD.png"), AllRatesPlot_SGD, device = "png", width = 6, height = 6)
#ggsave(here("Outputs", "RespoOutput","AllRates.pdf"), RatesPlot, device = "pdf", width = 6, height = 6)


AllRatesPlot_Salinity <- RespoR_Normalized_Full %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr,
             color = salinity))+
  #scale_x_continuous(trans="log10") + 
  #geom_boxplot(aes(color = SGD_number),
              # outlier.shape = NA)+ 
  geom_jitter(aes(color = salinity), position = position_jitterdodge()) + 
  theme_bw()+
  #geom_text_repel(aes(label = SampleID), size = 2.5, max.overlaps = 15) +
  theme(strip.background = element_rect(fill = "white"))+
  labs(x = "Environmental Treatment (SGD Level)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Rate of O2 production or consumption") +
  #scale_color_manual(values=my_pal) +
  facet_wrap(~ P_R, scales = "fixed")
AllRatesPlot_Salinity

ggsave(here("Outputs", "RespoOutput","AllRatesPlot_Salinity"), AllRatesPlot_Salinity, device = "png", width = 6, height = 6)

##############################################

```

## FOR DANIELLE TO LOOK AT 
```{r}

###########################
### making plots to just visualize relationship/trends 
###########################

## Gross Photosynthesis with salinity 
RatesPlot_GP_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  facet_wrap(site~new_colonynumber, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(title="GP by Salinity")
ggsave(here("Outputs", "PrelimOutputs","GPRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_salinity

## Respiration with salinity 
RatesPlot_R_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  geom_smooth(method = "lm") +
  facet_wrap(site~new_colonynumber, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title="Respiration by Salinity")
ggsave(here("Outputs", "PrelimOutputs","RRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_R_salinity

##### GP Rates based on SGD Dils #########
RatesPlot_GP_SGD <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) +
  facet_wrap(site~new_colonynumber, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="GP Rates for SGD Dils")
ggsave(here("Outputs", "PrelimOutputs","GPRates_SGDdils.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_SGD

##### look at umol by colony numbers for RESPIRATION for SGD dilutions 
SGDdil_bycolony <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, ##switched to umol but values are still off? 
             color=new_colonynumber)) + ## colony number breakdowns: 1-8=Varari, 13-20=Cabral
  facet_wrap(site~new_colonynumber, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="Respiration Normalized to Avg Blanks for SGD Dils per colony")

###########################
#### making mixed models to test for significance 
###########################

model_RbySalinity <- lmer(data = RData_C, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity) 
summary(model_RbySalinity)
ranef(model_RbySalinity)

model2_SGDbyR <- lmer(data = RData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR) 

### WHEN RUNNING DATE AS AN INTERACTION: THERE IS SIGNFICANT EFFECT OF DATE 

model_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number*date + (1|new_colonynumber))

anova(model_SGDbyR_V) 
summary(model_SGDbyR_V)

### no significance of SGD with date as rnadom effect 
model2_SGDbyR_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyR_V) 
summary(model2_SGDbyR_V)

##nor by pH 
model_RbySalinity_V <- lmer(data = RData_V, 
             umol.cm2.hr ~ salinity + (1|new_colonynumber/date))

anova(model_RbySalinity_V) 
summary(model_RbySalinity_V)


############ FOR GP #############
## almost significant effect og SGD on GP rates, just barely over 
model2_SGDbyGP <- lmer(data = GPData_C, 
             umol.cm2.hr ~ SGD_number + (1|new_colonynumber/date))
anova(model2_SGDbyGP) 
plot(model2_SGDbyGP)
#qqp(model2_SGDbyGP)

## no significant effect of salinity at Cabral or Varari 

## BUT THERE IS A SIGNIFICANT EFFECT OF PH ON GP AT VARARI 


#####################################
##### making plots to show all the rates together based on SGD number and salinity bc pH was kinda wonky 
####################################

# plot GP, NP and R
#my_pal <- pnw_palette(name="Starfish")

AllRatesPlot_SGD <- RespoR_Normalized_Full %>%
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr,
             color = SGD_number))+
  #scale_x_continuous(trans="log10") + 
  #geom_boxplot(aes(color = SGD_number),
              # outlier.shape = NA)+ 
  geom_jitter(aes(color = SGD_number), position = position_jitterdodge()) + 
  theme_bw()+
  #geom_text_repel(aes(label = SampleID), size = 2.5, max.overlaps = 15) +
  theme(strip.background = element_rect(fill = "white"))+
  labs(x = "Environmental Treatment (SGD Level)",
       color = "SGD_number",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Rate of O2 production or consumption") +
  #scale_color_manual(values=my_pal) +
  facet_wrap(~ P_R, scales = "fixed")
AllRatesPlot_SGD

ggsave(here("Outputs", "RespoOutput","AllRatesPlot_SGD.png"), AllRatesPlot_SGD, device = "png", width = 6, height = 6)
#ggsave(here("Outputs", "RespoOutput","AllRates.pdf"), RatesPlot, device = "pdf", width = 6, height = 6)


AllRatesPlot_Salinity <- RespoR_Normalized_Full %>%
  ggplot(aes(x=salinity, 
             y=umol.cm2.hr,
             color = salinity))+
  #scale_x_continuous(trans="log10") + 
  #geom_boxplot(aes(color = SGD_number),
              # outlier.shape = NA)+ 
  geom_jitter(aes(color = salinity), position = position_jitterdodge()) + 
  theme_bw()+
  #geom_text_repel(aes(label = SampleID), size = 2.5, max.overlaps = 15) +
  theme(strip.background = element_rect(fill = "white"))+
  labs(x = "Environmental Treatment (SGD Level)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Rate of O2 production or consumption") +
  #scale_color_manual(values=my_pal) +
  facet_wrap(~ P_R, scales = "fixed")
AllRatesPlot_Salinity

ggsave(here("Outputs", "RespoOutput","AllRatesPlot_Salinity"), AllRatesPlot_Salinity, device = "png", width = 6, height = 6)

```


