---
title: "VisualizationPlots_RespoData"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries 

```{r }
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
```

## Taking RespoR table from original script/for loop and loading it here

```{r}
RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
View(RespoR)

RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 600-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(colony_number= as.factor(colony_number), 
         date_block= factor(date)) #make the blank column a factor
```

## Now try to average the blanks 
- Have been having trouble with getting this to a point that I feel confident about 
```{r}
RespoR_Normalized_AvgBlanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, colony_number, site) %>% 
  filter(colony_number== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% # get mean value of blanks per each dilution 
  dplyr::select(blank.rate = umol.sec, site) %>%  ## rename the blank column 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  #arrange(FileID_csv) %>% 
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates #### HOW IS THIS NORMALIZING THE DATA IS EVERYTHING IS JUST GOING TO BE 0 #####   
         mmol.cm2.hr = 0.001*(umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         mmol.cm2.hr_uncorr = 0.001*(umol.sec*3600)/SA_cm2) %>% 
  filter(colony_number!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, run_block, SA_cm2, run_block, mmol.cm2.hr, chamber_channel, 
                Temp.C, mmol.cm2.hr_uncorr, colony_number, salinity, pH, site, SGD_number)
```

## Plot to see if averaged blanks worked out and only have one per SGD dilution 
```{r}
### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- RespoR_Normalized_AvgBlanks %>% 
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr_uncorr)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

##there are still multiple points even tho it is supposed to be taking an average 

```

## once blanks are sorted - use that dataset to calculate R, GP, and NP 
```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- RespoR_Normalized_AvgBlanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(mmol.cm2.hr = mmol.cm2.hr*-1,
         mmol.cm2.hr_uncorr = mmol.cm2.hr_uncorr*-1) %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") # all dark run rates get R for respiration

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- RespoR_Normalized_AvgBlanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP")

# rejoin data into single df
RespoR_Normalized2 <- full_join(RespoR_Normalized_light, RespoR_Normalized_dark) #%>% 
#drop_na(mmol.gram.hr) # removes anticipated sampleID's that were not actually run


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(colony_number, SGD_number, site, salinity, pH) %>% 
  summarize(mmol.cm2.hr = sum(mmol.cm2.hr),
            mmol.cm2.hr_uncorr = sum(mmol.cm2.hr_uncorr), # NP + R = GP
            #Temp.C = mean(Temp.C)
  ) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(colony_number, pH, SGD_number, site, salinity, light_dark, P_R, mmol.cm2.hr, mmol.cm2.hr_uncorr) %>% 
  full_join(RespoR_NormalizedGP)


write_csv(RespoR_Normalized_Full , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))  

View(RespoR_Normalized_Full)

```

## Now make some plots to look at the respo data 
Salinity should be main priority 
Then pH 
Then nutrients (probably silicate will be most telling) and TA once I have them 

## First few = Repiration rates across SGD dilutions 
What does mmol.cm2.hr really mean?? 
-  Represents the molar units 
- standardized by cm2 which is surface area of coral 
- by an hour of R/P runs 

## Calculating respiration 
- rate of oxygen change: Change in % O2 min-1--> mg L --> umol L (as referenced in Krueger 2019)
- converstion rate of O2 concentration (umol L) to rate of total amount of O2 produced/consumed (umol min) including volume 
- Calc based on assumption that O2-generation and consumption are proportional to actual carbon
metabolism

```{r}
RespoR_Normalized_Full <- read_csv(here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))

my_pal <- pnw_palette(name="Starfish",n=2,type="discrete")

##### Respiration rates with dilutions and u.mol ######### 
RespRates_SGDdil <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(colony_number~site, scales = "free_y") +
  geom_point() +
  scale_x_continuous(trans="log10") +
  labs(title="Respiration Normalized to Avg Blanks for SGD Dils")
ggsave(here("Outputs", "RespoOutput","RespRates_SGDdils.jpg"), 
       width = 10, height = 10)

RespRates_SGDdil <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free_y") +
  geom_boxplot() +
  scale_x_continuous(trans="log10") +
  labs(title="Respiration Normalized to Avg Blanks for SGD Dils")




##### GP Rates based on SGD Dils #########
RatesPlot_GP <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free_y") +
  geom_point() +
  scale_x_continuous(trans="log10") +
  labs(title="GP Rates for SGD Dils")
ggsave(here("Outputs", "RespoOutput","GPRates_SGDdils.jpg"), 
       width = 10, height = 10)


## first plot shows separated by replicates, second just shows all by site. Don't really see a trend - at least not a full curve, though Cabral seems to go down a little bit 

RatesPlot_GP <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free_y") +
  geom_boxplot() +
  scale_x_continuous(trans="log10") +
  labs(title="GP Rates for SGD Dils")
#ggsave(here("Outputs", "RespoOutput","GPRates_SGDdils_BoxPlot.jpg"), 
    #   width = 10, height = 10)

## Cabral is at least at much higher GP rates than Varari -- greater difference with GP than R 

```
## Environmental Parameters
- Starting with salinity 

```{r}
## Gross Photosynthesis with salinity 
RatesPlot_GP_EnvParameters <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=salinity, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(title="GP with Environmental Parameters")


## Respiration with salinity 
RatesPlot_R_EnvParameters <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=mmol.gram.hr, 
             color=colony_number)) +
  geom_smooth(method = "lm")+
  facet_wrap(colony_number~site, scales = "free") +
  geom_point() +
  labs(title="Respiration with Environmental Parameters")


### log scale NOT faceted by replicate
RatesPlot_R_EnvParameters <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=salinity, 
             color=colony_number)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_line()+
  labs(title="GP with Environmental Parameters")


RatesPlot_R_EnvParameters <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=pH, 
             color=colony_number)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(colony_number~site, scale = "free") +
  geom_line() +
  geom_point()
labs(title="Respiration with Environmental Parameters")
```





## Some notes: 
- oxygen = *produced* during photosynthesis 
- oxygen = *consumed* during respiration 
- NP = GP-R
- Muscatine et al. 1981 uses mg C rather than mmol 


## pH-TA technique
-  used to calculate the difference between the downstream and upstream concentrations of DIC
- use standard equations that describe the seawater inorganic carbon system 
- forward TA reaction is based on Redfield ration of C:N:P
- See Gattuso et al 1999 for equation 

## QUESTIONS/COMMENTS 




