---
title: "VisualizationPlots_RespoData"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

### Loading libraries 

```{r, echo= FALSE}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
```

### Taking RespoR table from original script/for loop and loading it here
-  Plus all the pther DFs so things will knit properly 

```{r}
RespoMeta <- read_csv(here("Data","RespoFiles","Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))
BioData <- read_csv(here("Data","RespoFiles","Fragment_MeasurementSampling_Cabral_Varari.csv"))
Sample_Info <- left_join(RespoMeta, BioData)

RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
#View(RespoR)

####################
### pH data #########
######################
pHcalib<-read_csv(here("Data","TrisCal_20230614.csv")) #%>% ## tris cal date is listed as a character here - make sure change in Excel file before reading in
pHcalib <- pHcalib[-c(13,14), ]

pHData <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) 
pHData <- pHData[-c(294,303,435),]
pHData <- pHData[,-(14:17)]

pHSlope<-pHcalib %>%
  #filter(HOBO_Orion =="Orion") %>% # extract only the orion data
  nest_by(TrisCalDate) %>%
  dplyr::mutate(fitpH = list(lm(mVTRis~Ttris, data = data))) %>% # linear regression of mV and temp of the tris
  dplyr::summarise(broom::tidy(fitpH)) %>% # make the output tidy
  select(TrisCalDate, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>% # put slope and intercept in their own column
  right_join(.,pHData) %>% # join with the pH sample data
  mutate(mVTRis = temp_C*Ttris + `(Intercept)`) %>% 
  mutate(new_pH = pH(Ex=mV,Etris=mVTRis,S=salinity,T=temp_C)) # calculate pH of the samples using the pH seacarb function

######### Respo table #############
RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 600-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(colony_number= as.factor(colony_number), 
         date_block= factor(date)) #make the blank column a factor

#View(RespoR2)
```

### Now try to average the blanks 
-  Have been having trouble with getting this to a point that I feel confident about 
-  Questions: am I supposed to have one point for each dilution from all the days combined?? Or one day? 
```{r}
RespoR_Normalized_AvgBlanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, colony_number, site) %>% 
  filter(colony_number== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% # get mean value of blanks per each dilution across all days? 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site) %>%  ## rename the blank column 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  #arrange(FileID_csv) %>% 
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates   
         mmol.cm2.hr = 0.001*(umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         mmol.cm2.hr_uncorr = 0.001*(umol.sec*3600)/SA_cm2) %>% 
  filter(colony_number!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, run_block, SA_cm2, run_block, mmol.cm2.hr, chamber_channel, 
                Temp.C, mmol.cm2.hr_uncorr, colony_number, salinity, pH, site, SGD_number)

#View(RespoR_Normalized_AvgBlanks)

## try to join in new pH data here## 
TrispH_RespoRNormalized_AvgBlanks <- RespoR_Normalized_AvgBlanks %>% 
  left_join(pHSlope)

```

### Plot to see if averaged blanks worked out and only have one per SGD dilution 
```{r}
### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- TrispH_RespoRNormalized_AvgBlanks %>% 
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr_uncorr)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

##there are still multiple points even tho it is supposed to be taking an average 

```

### Once blanks are sorted - use that dataset to calculate R, GP, and NP 
```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- TrispH_RespoRNormalized_AvgBlanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(mmol.cm2.hr = mmol.cm2.hr*-1,
         mmol.cm2.hr_uncorr = mmol.cm2.hr_uncorr*-1) %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") # all dark run rates get R for respiration

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- TrispH_RespoRNormalized_AvgBlanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP")

# rejoin data into single df
RespoR_Normalized2 <- full_join(RespoR_Normalized_light, RespoR_Normalized_dark) #%>% 
#drop_na(mmol.gram.hr) # removes anticipated sampleID's that were not actually run


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(colony_number, SGD_number, site, salinity, new_pH) %>% 
  summarize(mmol.cm2.hr = sum(mmol.cm2.hr),
            mmol.cm2.hr_uncorr = sum(mmol.cm2.hr_uncorr), # NP + R = GP
            #Temp.C = mean(Temp.C)
  ) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(mmol.cm2.hr = ifelse(mmol.cm2.hr < 0, 0, mmol.cm2.hr), # for any values below 0, make 0
         mmol.cm2.hr_uncorr = ifelse(mmol.cm2.hr_uncorr < 0, 0, mmol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(colony_number, new_pH, SGD_number, site, salinity, date, light_dark, P_R, mmol.cm2.hr, mmol.cm2.hr_uncorr) %>% 
  full_join(RespoR_NormalizedGP)


write_csv(RespoR_Normalized_Full , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))  

#View(RespoR_Normalized_Full)

```

#### Now make some plots to look at the respo data 
Salinity should be main priority 
Then pH 
Then nutrients (probably silicate will be most telling) and TA once I have them 

#### First few figures = Repiration and GP rates across SGD dilutions
What does mmol.cm2.hr really mean?? 
-  Represents the molar units 
-  standardized by cm2 which is surface area of coral 
-  by an hour of R/P runs 

#### Calculating respiration 
-  rate of oxygen change: Change in % O2 min-1--> mg L --> umol L (as referenced in Krueger 2019)
-  converstion rate of O2 concentration (umol L) to rate of total amount of O2 produced/consumed (umol min) including volume 
-  Calc based on assumption that O2-generation and consumption are proportional to actual carbon
metabolism

```{r}
RespoR_Normalized_Full <- read_csv(here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))

my_pal <- pnw_palette(name="Starfish",n=2,type="discrete")

##### Respiration rates with dilutions and u.mol ######### 
RespRates_SGDdil <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="Respiration Normalized to Avg Blanks for SGD Dils")
ggsave(here("Outputs", "PrelimOutputs","RespRates_SGDdils.jpg"), 
       width = 10, height = 10)

RespRates_SGDdil

#RespRates_SGDdil <- RespoR_Normalized_Full %>%
 # filter(P_R == "R") %>%
 # ggplot(aes(x=SGD_number, 
  #           y=mmol.cm2.hr, 
  #           color=colony_number)) +
  #facet_wrap(~site, scales = "free_y") +
 # geom_boxplot() +
 # scale_x_continuous(trans="log10") +
 # labs(title="Respiration Normalized to Avg Blanks for SGD Dils")

```
#### GP 
```{r}
##### GP Rates based on SGD Dils #########
RatesPlot_GP_SGD <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=SGD_number, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free_y") +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_continuous(trans="log10") +
  labs(title="GP Rates for SGD Dils")
ggsave(here("Outputs", "PrelimOutputs","GPRates_SGDdils.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_SGD

## first plot shows separated by replicates, second just shows all by site. Don't really see a trend - at least not a full curve, though Cabral seems to go down a little bit 

#RatesPlot_GP <- RespoR_Normalized_Full %>%
 # filter(P_R == "GP") %>%
 # ggplot(aes(x=SGD_number, 
            # y=mmol.cm2.hr, 
           #  color=colony_number)) +
  #facet_wrap(~site, scales = "free_y") +
 # geom_boxplot() +
  #scale_x_continuous(trans="log10") +
  #labs(title="GP Rates for SGD Dils")
#ggsave(here("Outputs", "RespoOutput","GPRates_SGDdils_BoxPlot.jpg"), 
    #   width = 10, height = 10)

## Cabral is at least at much higher GP rates than Varari -- greater difference with GP than R
```

#### Environmental Parameters
- Starting with salinity 
- calculated new pH from Tris Calibration 

```{r}
## Gross Photosynthesis with salinity 
RatesPlot_GP_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "GP") %>%
  ggplot(aes(x=salinity, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(title="GP by Salinity")
ggsave(here("Outputs", "PrelimOutputs","GPRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_GP_salinity

## Respiration with salinity 
RatesPlot_R_salinity <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  geom_smooth(method = "lm") +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title="Respiration by Salinity")
ggsave(here("Outputs", "PrelimOutputs","RRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_R_salinity

######################################
## trying with grouped salinity, same as did with pH 
########################################
salinity_combined <- RespoR_Normalized_Full %>% 
  #filter(site=="Varari") %>% 
  group_by(SGD_number, date) 

## Respiration with salinity 
RatesPlot_R_GroupedSalinity <- RespoR_Normalized_Full %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=salinity, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  geom_smooth(method = "lm") +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title="Respiration by (Grouped) Salinity")
ggsave(here("Outputs", "PrelimOutputs","RRates_Salinity2.jpg"), 
       width = 10, height = 10)

RatesPlot_R_GroupedSalinity

RatesPlot_NP_GroupedSalinity <- RespoR_Normalized_Full %>%
  filter(P_R == "NP") %>%
  ggplot(aes(x=salinity, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  facet_wrap(~site, scales = "free") +
  geom_point() +
  geom_smooth(method = "lm")+
  labs(title="GP by (Grouped) Salinity")
ggsave(here("Outputs", "PrelimOutputs","NPRates_Salinity.jpg"), 
       width = 10, height = 10)

RatesPlot_NP_GroupedSalinity

### log scale NOT faceted by replicate
#RatesPlot_R_EnvParameters <- RespoR_Normalized_Full %>%
  #filter(P_R == "GP") %>%
  #ggplot(aes(x=SGD_number, 
             #y=salinity, 
            # color=colony_number)) +
  #scale_x_continuous(trans="log10") +
  #facet_wrap(~site, scales = "free") +
  #geom_point() +
  #geom_line()+
 # labs(title="GP with Environmental Parameters")



```
#### Now with pH 
```{r}
## need to show pH by day rather than colony 
pH_combined <- RespoR_Normalized_Full %>% 
  #filter(site=="Varari") %>% 
  group_by(SGD_number, date) 

RatesPlot_NP_pH <- pH_combined %>%
  filter(P_R == "NP") %>% ## trying it with NP here because GP doesn't have assigned date to it -- could try with day block but would need to reconfigure the grouping 
   ggplot(aes(x=new_pH, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(~site, scale = "free") +
  geom_smooth(method = "lm") +
  geom_point()+ 
  labs(title="NP by pH")
ggsave(here("Outputs", "PrelimOutputs","NP_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_NP_pH

RatesPlot_R_pH <- pH_combined %>%
  filter(P_R == "R") %>%
  ggplot(aes(x=new_pH, 
             y=mmol.cm2.hr, 
             color=colony_number)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(~site, scale = "free") +
  geom_smooth(method = "lm")+
  geom_point() +
  labs(title="Respiration by pH")
ggsave(here("Outputs", "PrelimOutputs","R_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_R_pH

######## now try with salinity and pH plotted against each other #######
RatesPlot_R_EnvParameters <- RespoR_Normalized_Full %>%
  #filter(P_R == "R") %>%
  ggplot(aes(x=new_pH, 
             y=salinity, 
             color=colony_number)) +
  scale_x_continuous(trans="log10") +
  facet_wrap(~site, scale = "free") +
  geom_smooth(method = "lm")+
  geom_point() +
  labs(title="Salinity by pH")
ggsave(here("Outputs", "PrelimOutputs", "Salinity_pH.jpg"), 
       width = 10, height = 10)

RatesPlot_R_EnvParameters

```


#### Now figure out how to do GP:R ratios 
-  having some trouble with this formatting 

```{r}
wide_RespoRNormalizedFull <- RespoR_Normalized_Full %>% 
  pivot_wider(names_from=P_R, values_from=mmol.cm2.hr) %>% 
  mutate(GP_R_Ratio=R/GP)


### how do I set this up because the values are all in different columns not side by side from one another 

#View(wide_RespoRNormalizedFull)


```


### What are the stats?? 
```{r}
library(agricolae) # HSD.test()

# quick modeling
# check assumptions for all (referencing Biometry notes below)

# models
GPData <- RespoR_Normalized_Full %>% filter(P_R == "GP")
model1 <- lm(data = GPData, mmol.cm2.hr ~ salinity)
anova(model1)
HSD.test(model1, "salinity", console=TRUE)

NPData <- RespoR_Normalized_Full %>% filter(P_R == "NP")
model2 <- lm(data = NPData, mmol.cm2.hr ~ salinity)
anova(model2)
HSD.test(model2, "salinity", console=TRUE)

RData <- RespoR_Normalized_Full %>% filter(P_R == "R")
model3 <- lm(data = RData, mmol.cm2.hr ~ salinity)
anova(model3)
HSD.test(model3, "salinity", console=TRUE)

# check parameters with pH 
RData <- RespoR_Normalized_Full %>% filter(P_R == "R")
model3 <- lm(data = RData, new_pH ~ mmol.cm2.hr) ### testing it with vars switched both ways to make sure the P value stays the same 
anova(model3)
HSD.test(model3, "pH", console=TRUE)

GPData <- RespoR_Normalized_Full %>% filter(P_R == "NP")
model1 <- lm(data = GPData, mmol.cm2.hr ~ new_pH) ### testing it with vars switched both ways to make sure the P value stays the same 
anova(model1)
HSD.test(model1, "pH", console=TRUE) ## significant 


### check for SGD dilutions 
RData <- RespoR_Normalized_Full %>% filter(P_R == "R")
model3 <- lm(data = RData, mmol.cm2.hr ~ SGD_number)
anova(model3)
HSD.test(model3, "SGD_number", console=TRUE)

GPData <- RespoR_Normalized_Full %>% filter(P_R == "GP")
model1 <- lm(data = GPData, mmol.cm2.hr ~ SGD_number)
anova(model1)
HSD.test(model1, "SGD_number", console=TRUE)


```


#### Some notes: 
- oxygen = *produced* during photosynthesis 
- oxygen = *consumed* during respiration 
- NP = GP-R
- Muscatine et al. 1981 uses mg C rather than mmol 


#### pH-TA technique
-  used to calculate the difference between the downstream and upstream concentrations of DIC
- use standard equations that describe the seawater inorganic carbon system 
- forward TA reaction is based on Redfield ration of C:N:P
- See Gattuso et al 1999 for equation 

#### QUESTIONS/COMMENTS 




