---
title: "Nutrient_Analyses"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries 
```{r}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
library(agricolae)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(flextable)
library(performance)
library(agricolae)
library(ggeffects)
library(sjPlot)
library(patchwork)
library(broom)
library(purrr)
library(nlstools)
library(stringr)
library(emmeans)
library(MuMIn)
```



# Bring in processed respo data 
## note: having error with calculating "new_pH" in dataset 
## note: run from WSN Pots and Models script
```{r}
RespoR_Normalized_Full
```




# Original plots for R, GP, and C - for Varari and Cabral 
## edit: try without jitter (to see if salinity problem is fixed and if data looks any better?)
## note: report marginal and conditional R2 value 
## note: report non-significant p-values

```{r}

##############################
## R for Varari 
##############################


##############################
## R for Cabral 
##############################


##############################
## GP for Varari 
##############################



##############################
## GP for Cabral 
##############################


##############################
## NEC for Varari 
##############################




##############################
## NEC for Cabral 
##############################

# with jitter
NEC_C <- full.calc.data %>%
  filter(site=="Cabral") %>% 
  filter(new_colonynumber!="20") %>% 
  filter(new_colonynumber!="BLANK") %>%
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
 # facet_wrap(~new_colonynumber)+
  theme(strip.background = element_rect(fill = "white"))+
  #geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  geom_hline(yintercept = 0)+
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcification Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 

NEC_C

# without jitter 
NEC_C2 <- full.calc.data %>%
  filter(site=="Cabral") %>% 
  filter(new_colonynumber!="20") %>% 
  filter(new_colonynumber!="BLANK") %>%
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
 # facet_wrap(~new_colonynumber)+
  theme(strip.background = element_rect(fill = "white"))+
  #geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  geom_hline(yintercept = 0)+
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcification Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
NEC_C2

NEC_C2 + NEC_C
```


# Nutrient analyses for GP, R, and C using parameters of NN, PO4, NH4, SiO4, TA, and pH at both Varari and Cabral 
## plot and model for R with all parameters for Varari 
```{r}
# creating new dataset for models 
Nutrient_Models_Varari_R <- RespoR_Normalized_Full %>% 
  filter(site=="Varari") %>% 
  drop_na(NN_umolL) %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr))
Nutrient_Models_Varari_R<-Nutrient_Models_Varari_R[-c(24),]  


#######################
## NN ## 
########################
NNbyRplot <- Nutrient_Models_Varari_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
 # filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=NN_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with N+N (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "N+N for Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
NNbyRplot

## normal model with full nesting and random effects 
Varari_NN_resp <- lmer(data = Nutrient_Models_Varari_R, 
             umol.cm2.hr ~ poly(NN_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_NN_resp) 
summary(Varari_NN_resp)

#######################
## NH4 ## 
########################
NH4byRplot <- Nutrient_Models_Varari_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
 # filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=ammonia_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with NH4 (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "NH4 for Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))

NH4byRplot

### model 
Varari_NH4_resp <- lmer(data = Nutrient_Models_Varari_R, 
             umol.cm2.hr ~ poly(ammonia_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_NH4_resp) 
summary(Varari_NH4_resp)

#######################
## PO4 ## 
########################
PhosbyRplot <- Nutrient_Models_Varari_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
 # filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=phosphate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with Phosphate (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Phosphate for Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
PhosbyRplot

Varari_PO4_resp <- lmer(data = Nutrient_Models_Varari_R, 
             umol.cm2.hr ~ poly(phosphate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_PO4_resp) 
summary(Varari_PO4_resp)


#######################
## SiO3 ## 
########################
SilicatebyRplot <- Nutrient_Models_Varari_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
 # filter(!is.infinite(umol.cm2.hr)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Silicate (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration Rates for Varari with Silicate") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
SilicatebyRplot

Varari_SiO4_resp <- lmer(data = Nutrient_Models_Varar_R, 
             umol.cm2.hr ~ poly(silicateate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_SiO4_resp) 
summary(Varari_SiO4_resp)

#######################
## pH ## 
########################
pHbyRplot <- Nutrient_Models_Varari_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=pH, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "pH",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration Rates for Varari with pH") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
pHbyRplot

Varari_pH_resp <- lmer(data = Nutrient_Models_Varari_R, 
             umol.cm2.hr ~ poly(pH, degree=2) + (1|date/new_colonynumber))

anova(Varari_pH_resp) 
summary(Varari_pH_resp)


#######################
## TA ???? ## 
########################
```

## plot and model for R with all parameters for Cabral  

```{r}
Nutrient_Models_Cabral_R <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral") %>% 
  drop_na(NN_umolL) %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr))

#######################
## NN ## 
########################
NNbyRplot_Cabral <- Nutrient_Models_Cabral_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=NN_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with N+N (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "N+N for Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
NNbyRplot_Cabral

## normal model with full nesting and random effects 
Cabral_NN_resp <- lmer(data = Nutrient_Models_Cabral_R, 
             umol.cm2.hr ~ poly(NN_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_NN_resp) 
summary(Cabral_NN_resp)

#######################
## NH4 ## 
########################
NH4byRplot_Cabral <- Nutrient_Models_Cabral_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=ammonia_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with NH4 (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "NH4 for Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
NH4byRplot_Cabral

## normal model with full nesting and random effects 
Cabral_NH4_resp <- lmer(data = Nutrient_Models_Cabral_R, 
             umol.cm2.hr ~ poly(ammonia_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_NH4_resp) 
summary(Cabral_NH4_resp)

#######################
## PO4 ## 
########################
PhosbyRplot_Cabral <- Nutrient_Models_Cabral_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=phosphate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with PO4 (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "PO4 for Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
PhosbyRplot_Cabral

## normal model with full nesting and random effects 
Cabral_PO4_resp <- lmer(data = Nutrient_Models_Cabral_R, 
             umol.cm2.hr ~ poly(phosphate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_PO4_resp) 
summary(Cabral_PO4_resp)

#######################
## SiO3 ## 
########################
SiO4byRplot_Cabral <- Nutrient_Models_Cabral_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with SiO4 (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "SiO4 for Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
SiO4byRplot_Cabral

## normal model with full nesting and random effects 
Cabral_SiO4_resp <- lmer(data = Nutrient_Models_Cabral_R, 
             umol.cm2.hr ~ poly(silicate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_SiO4_resp) 
summary(Cabral_SiO4_resp)

#######################
## pH ## 
########################
pHbyRplot_Cabral <- Nutrient_Models_Cabral_R %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=pH, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  theme_bw() + 
  labs(x = "Respiration Rates with pH",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "pH for Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
pHbyRplot_Cabral

## normal model with full nesting and random effects 
Cabral_pH_resp <- lmer(data = Nutrient_Models_Cabral_R, 
             umol.cm2.hr ~ poly(pH, degree=2) + (1|date/new_colonynumber))

anova(Cabral_pH_resp) 
summary(Cabral_pH_resp)


#######################
## TA ???? ## 
########################
```


## plots and models for NP with all parameters for Varari AND Cabral 
## note: NP data does not contain any of the nutrient values 
```{r}
Nutrient_Models_NP <- RespoR_Normalized_Full %>% 
  drop_na(NN_umolL) %>% 
  filter(P_R=="NP") %>% 
  filter(!is.infinite(umol.cm2.hr))
Nutrient_Models_NP<-Nutrient_Models_NP[-c(36),]  ## drop the outlier from varari 

#######################
## NN ## 
########################

NNbyNPplot <- Nutrient_Models_NP %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=NN_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  facet_wrap(~site) +
  theme_bw() + 
  labs(x = "N+N (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "N+N for NP Rates by Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ggsave(here("Outputs", "NutrientAnalyses", "NN_NP_plot.jpg"), 
       width = 10, height = 7)

NNbyNPplot

## models 
## separate by site 
Nutrient_Models_NP_V <- Nutrient_Models_NP %>% 
  filter(site=="Varari")

Nutrient_Models_NP_C <- Nutrient_Models_NP %>% 
  filter(site== "Cabral")

# actual model set up 
Varari_NN_NP <- lmer(data = Nutrient_Models_NP_V, 
             umol.cm2.hr ~ poly(NN_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_NN_NP) 
summary(Varari_NN_NP)

Cabral_NN_NP <- lmer(data = Nutrient_Models_NP_C, 
             umol.cm2.hr ~ poly(NN_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_NN_NP) 
summary(Cabral_NN_NP)


#######################
## NH4 ## 
########################

NH4byNPplot <- Nutrient_Models_NP %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=ammonia_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  facet_wrap(~site) +
  theme_bw() + 
  labs(x = "Ammonia (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Ammonia for NP Rates by Site") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ggsave(here("Outputs", "NutrientAnalyses", "NH4_NP_plot.jpg"), 
       width = 10, height = 7)

NH4byNPplot

## full models 
Varari_NH4_NP <- lmer(data = Nutrient_Models_NP_V, 
             umol.cm2.hr ~ poly(ammonia_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_NH4_NP) 
summary(Varari_NH4_NP)

Cabral_NH4_NP <- lmer(data = Nutrient_Models_NP_C, 
             umol.cm2.hr ~ poly(ammonia_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_NH4_NP) 
summary(Cabral_NH4_NP)


#######################
## PO4 ## 
########################

PhosphatesbyNPplot <- Nutrient_Models_NP %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=phosphate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  facet_wrap(~site) +
  theme_bw() + 
  labs(x ="Phosphates (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Phosphates for NP Rates by site") + 
  theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ggsave(here("Outputs", "NutrientAnalyses", "PO4_NP_plot.jpg"), 
       width = 10, height = 7)

PhosphatesbyNPplot

#models 
Varari_PO4_NP <- lmer(data = Nutrient_Models_NP_V, 
             umol.cm2.hr ~ poly(phosphate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_PO4_NP) 
summary(Varari_PO4_NP)

Cabral_PO4_NP <- lmer(data = Nutrient_Models_NP_C, 
             umol.cm2.hr ~ poly(phosphate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_PO4_NP) 
summary(Cabral_PO4_NP)

#######################
## SiO4 ## 
########################
SiO4byNPplot <- Nutrient_Models_NP %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=silicate_umolL, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  facet_wrap(~site) +
  theme_bw() + 
  labs(x ="Silicate (umolL)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Silicate for NP Rates by site") + 
  theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ggsave(here("Outputs", "NutrientAnalyses", "SiO4_NP_plot.jpg"), 
       width = 10, height = 7)

SiO4byNPplot

## models 
Varari_SiO4_NP <- lmer(data = Nutrient_Models_NP_V, 
             umol.cm2.hr ~ poly(silicate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Varari_SiO4_NP) 
summary(Varari_SiO4_NP)

Cabral_SiO4_NP <- lmer(data = Nutrient_Models_NP_C, 
             umol.cm2.hr ~ poly(silicate_umolL, degree=2) + (1|date/new_colonynumber))

anova(Cabral_SiO4_NP) 
summary(Cabral_SiO4_NP)


#######################
## pH ## 
########################
pHbyNPplot <- Nutrient_Models_NP %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  ggplot(aes(x=pH, 
             y=umol.cm2.hr)) + 
  geom_point(size=3) +
  facet_wrap(~site) +
  theme_bw() + 
  labs(x ="pH",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "pH for NP Rates by site") + 
  theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
ggsave(here("Outputs", "NutrientAnalyses", "pH_NP_plot.jpg"), 
       width = 10, height = 7)


pHbyNPplot

#models
Varari_pH_NP <- lmer(data = Nutrient_Models_NP_V, 
             umol.cm2.hr ~ poly(pH, degree=2) + (1|date/new_colonynumber))

anova(Varari_pH_NP) 
summary(Varari_pH_NP)

Cabral_pH_NP <- lmer(data = Nutrient_Models_NP_C, 
             umol.cm2.hr ~ poly(pH, degree=2) + (1|date/new_colonynumber))

anova(Cabral_pH_NP) 
summary(Cabral_pH_NP)

#######################
## TA ??? ## 
########################
```

## note: try to join calc.data with respo data to get TA for NP and R?? 
## make new datasets for calc data 

```{r}
## dataset for TA and Calcification data 
full.calc.data <- full.calc.data %>% 
  mutate(deltaTA_2 = deltaTA/2,
         deltaTA_L = deltaTA_2*1.025, 
         umol.cm2.s = deltaTA_L*(.650-(volume_mL/1000))/(SA_cm2*timediff), 
         umol.cm2.hr = umol.cm2.s*3600) 

CalcData_wNutrients <- full.calc.data %>% 
  full_join(RespoR_Normalized_Full)
## ^^ this isn't working yet 
  
NEC_Varari <- full.calc.data %>% 
  filter(site=="Varari")

NEC_Cabral <- full.calc.data %>% 
  filter(site=="Cabral")


```

## plots and models for Varari 
```{r}

## TA plots 
TA_NEC_V <- NEC_Varari %>%
  filter(site=="Varari") %>% 
 # filter(new_colonynumber!="BLANK") %>%
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=TA, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
  theme(strip.background = element_rect(fill = "white"))+
  geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  geom_hline(yintercept = 0)+
  labs(x = "TA",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcification Rates at Varari for TA") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "NutrientAnalyses", "TA_NEC_plot_V.jpg"), 
       width = 10, height = 7)

TA_NEC_V


Varari_TA_NEC <- lmer(data = NEC_Varari, 
             umol.cm2.hr ~ poly(TA, degree=2) + (1|date/new_colonynumber))

anova(Varari_TA_NEC) 
summary(Varari_TA_NEC)
```


## plot and model for C with all parameters for Cabral 

```{r}

## original plot with SGD - in WSN plots and models 

##plot for TA 
TA_NEC_C <- NEC_Cabral %>%
  #filter(new_colonynumber!="20") %>% 
 # filter(new_colonynumber!="BLANK") %>%
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=TA, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
  theme(strip.background = element_rect(fill = "white"))+
  geom_hline(yintercept = 0) +
  labs(x = "TA",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcification Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "NutrientAnalyses", "TA_NEC_plot.jpg"), 
       width = 10, height = 7)

##model for TA 

Cabral_TA_NEC <- lmer(data = NEC_Cabral, 
             umol.cm2.hr ~ poly(TA, degree=2) + (1|date/new_colonynumber))

anova(Cabral_TA_NEC) 
summary(Cabral_TA_NEC)



```




