---
title: "OSM Edits, Nutrient Data"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

## Loading libraries 

```{r, echo=FALSE}
library(segmented)
library(plotrix)
library(gridExtra)
library(LoLinR)
library(lubridate)
library(chron)
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(ggrepel)
#library(PerformanceAnalytics)
library(reshape2)
library(viridis)
library(car)
library(GGally)
library(corrplot)
library(PNWColors)
library(seacarb)
library(broom)
library(calecopal)
library(ggridges)
library(agricolae)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(flextable)
library(performance)
library(agricolae)
library(ggeffects)
library(sjPlot)
library(patchwork)
library(broom)
library(purrr)
library(nlstools)
library(stringr)
library(emmeans)
library(MuMIn)
```


## Loading the data and creating dfs 
```{r}
RespoMeta <- read_csv(here("Data","RespoFiles","Respo_Metadata_SGDDilutions_Cabral_Varari.csv"))
BioData <- read_csv(here("Data","RespoFiles","Fragment_MeasurementSampling_Cabral_Varari.csv"))
Sample_Info <- left_join(RespoMeta, BioData)

RespoR <- read_csv(here("Data","RespoFiles","Respo_R.csv"))
#View(RespoR)

####################
### pH data #########
######################
pHcalib<-read_csv(here("Data","TrisCal_20230614.csv")) #%>% ## tris cal date is listed as a character here - make sure change in Excel file before reading in so it is a date 
pHcalib$TrisCalDate <- mdy(pHcalib$TrisCalDate)
pHcalib <- pHcalib[-c(13,14), ]

#View(pHcalib)

pHData <- read_csv(here("Data", "RespoFiles", "Fragment_MeasurementSampling_Cabral_Varari.csv")) 
pHData$TrisCalDate <- mdy(pHData$TrisCalDate)
pHData <- pHData[-c(294,303,435),]
#pHData <- pHData[,-(14:17)]

#View(pHData) ### if re-running after a bit, either add in code for converting TrisCalDate to a date OR make sure it is a date in the file 

pHSlope<-pHcalib %>%
  #filter(HOBO_Orion =="Orion") %>% # extract only the orion data
  nest_by(TrisCalDate) %>%
  dplyr::mutate(fitpH = list(lm(mVTRis~Ttris, data = data))) %>% # linear regression of mV and temp of the tris
  dplyr::summarise(broom::tidy(fitpH)) %>% # make the output tidy
  select(TrisCalDate, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>% # put slope and intercept in their own column
  right_join(.,pHData) %>% # join with the pH sample data
  mutate(mVTRis = temp_C*Ttris + `(Intercept)`) #%>% 
 # mutate(new_pH = pH(Ex=mV,Etris=mVTRis,S=salinity,T=temp_C)) # calculate pH of the samples using the pH seacarb function - GETTING AN ERRROR ON THIS LAST LINE ######

#### COME BACK AND CHECK LATER ##### ## seems fine as of Jan27th, 2024 

#View(pHSlope)
######### Respo table #############
RespoR2 <- RespoR %>%
  #drop_na(FileID_csv) %>% # drop NAs
  left_join(Sample_Info) %>% # Join the raw respo calculations with the metadata in Sample Info 
  #mutate(Ch.Volume.ml = ifelse(is.na(volume_ml),ch.vol,ch.vol-volume_ml)) %>% # add 6 L for volume of all blanks and subtract org volume from chamber vol for all else
  mutate(Ch.Volume.mL = 650-volume_mL) %>% # hannah changed all this volume stuff to match my project
  mutate(Ch.Volume.L = Ch.Volume.mL * 0.001) %>% # mL to L conversion
  mutate(umol.sec = umol.L.sec*Ch.Volume.L) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes (different because of coral size) and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert character columns to factors
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date_block= factor(date)) #make the blank column a factor

#View(RespoR2)
```

## Normalize to Blanks 
- things to consider here: try both ways 
- 1. average across all the days and get one point for each dilution 
- 2. keep it how it is - grouped by date_block (i think this is more correct)
```{r}
RespoR_Normalized_blankperday <- RespoR2 %>% 
  group_by(SGD_number, light_dark, date_block, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)


## two options: 1) summarise across all 4 days 2) direct comparison day to day 
## look at individual blank values to see if any of the days are particularly off - if everything looks consistent, can stick with individual days 
# take out date_block in group by and then change summarise function - to average all blanks by all dilutions 
# go back and check for blank volume to make sure full chamber vol 

### plot colonies against blanks ######
plot_Blank_Rates <- RespoR_Normalized_blankperday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~date_block, scales="free_y")

plot_Blank_Rates2 <- RespoR_Normalized_blankperday %>% 
  #filter(date_block!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark, scales="free_y")

plot_Blank_Rates2.5 <- RespoR_Normalized_blankperday %>% 
  filter(date_block!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark, scales="free_y")

plot_Blank_Rates3 <- RespoR_Normalized_blankperday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(date_block~light_dark, scales="free_y")


##### DELETE 6/13 FROM BLANK DATA FOR CABRAL 
RespoR_Normalized_blankperdaynoCabral <- RespoR_Normalized_blankperday %>% 
  filter(date_block!="6/13/23")

```

### Option 2 for Blanks - averaging  
```{r}

RespoR_Normalized_avgblanks <- RespoR2 %>% 
  group_by(SGD_number, light_dark, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site)

### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- RespoR_Normalized_avgblanks %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~light_dark)

```

## Now combine into two dfs - one based on per day blank rates and the other based on averaged blank rates 
```{r}
#joining with per day blanks 
RespoR_Normalized_blankperday_joined <- RespoR_Normalized_blankperdaynoCabral %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date_block, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2, # convert to mmol g-1 hr-1
         umol.cm2.hr_uncorr = (umol.sec*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr, umol.cm2.hr_uncorr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL)

#join with Tris pH data 
TrispH_RespoRNormalized_perdayBlanks <- RespoR_Normalized_blankperday_joined %>% 
  left_join(pHSlope)

```

### BASED ON WHAT BLANKS TO USE -  calculate R, GP, and NP 
- RIGHT NOW: using blanks per day
- with edits made to Cabral 

```{r}
# make the respiration values positive (pull out data for dark treatments)

RespoR_Normalized_dark <- TrispH_RespoRNormalized_perdayBlanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1,
         umol.cm2.hr_uncorr = umol.cm2.hr_uncorr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr),  # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "R") %>% # all dark run rates get R for respiration
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr)) ####### DELETE THIS ONCE FIGURE OUT WHAT CABRAL 11/12 

# all light run rates get NP for net photosynthesis
RespoR_Normalized_light <- TrispH_RespoRNormalized_perdayBlanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr),  # for any values below 0, make 0
        umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr)) %>% 
  mutate(P_R = "NP") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr)) ####### DELETE THIS ONCE FIGURE OUT WHAT CABRAL 11/12 

# rejoin data into single df
RespoR_Normalized2 <- bind_rows(RespoR_Normalized_light, RespoR_Normalized_dark) %>% 
  drop_na(umol.cm2.hr) # removes C20 and C19 that were weird 


#make column for GP and group by fragment ID and salinity to keep R and NP together
RespoR_NormalizedGP <- RespoR_Normalized2 %>% 
  group_by(new_colonynumber, SGD_number, site, date, salinity, pH) %>% ## EDITED FROM new_pH
  summarize(umol.cm2.hr = sum(umol.cm2.hr, na.rm=TRUE), 
            umol.cm2.hr_uncorr = sum(umol.cm2.hr_uncorr, na.rm=TRUE)) %>% # NP + R = GP
            #Temp.C = mean(Temp.C)) %>% 
  mutate(P_R="GP") %>% # Label for Gross Photosynthesis
  mutate(light_dark = "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr), # for any values below 0, make 0
         umol.cm2.hr_uncorr = ifelse(umol.cm2.hr_uncorr < 0, 0, umol.cm2.hr_uncorr))

# rejoin for full df with NP, R, and GP rates
RespoR_Normalized_Full <- RespoR_Normalized2 %>% 
  dplyr::select(new_colonynumber, pH, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, umol.cm2.hr_uncorr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%
  bind_rows(RespoR_NormalizedGP) %>% ## EDITED FROM NEW PH 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr))
 # filter(new_colonynumber!=20)


## what is wrong with Cabral 20? 
#Cabral20 <- RespoR_Normalized_Full %>%
 #filter(site=="Cabral") %>%
 # ggplot(aes(x=SGD_number, 
 #            y=umol.cm2.hr)) + 
 # facet_wrap(~new_colonynumber, scales = "free_y") +
#  geom_point() +
 # geom_smooth(method = "lm", se = FALSE) +
 # scale_x_continuous(trans="log10") 
  #labs(title="Respiration Normalized to Blanks for SGD Dils per colony")

write_csv(RespoR_Normalized_Full , here("Data","RespoFiles","Respo_RNormalized_AllRates.csv"))  

```

## NOW FOR THE NEW STUFF 

## try calculating means and variance and then plotting with raw data in the background 
```{r}
RespoR_Normalized_Full_meanvar <- RespoR_Normalized_Full %>% 
  group_by(SGD_number, site, P_R) %>% 
  summarize(mean_umol = mean(umol.cm2.hr, na.rm=TRUE), 
            var_umol = var(umol.cm2.hr, na.rm=TRUE), 
            sd_umol = sd(umol.cm2.hr, na.rm = TRUE)) %>% 
  filter(!is.infinite(mean_umol)) #%>% 
  #ungroup() %>% 
  #left_join(RespoR_Normalized_Full)



## are the variances significant??
#variances_model <- lmer(data = RespoR_Normalized_Full_meanvar, 
         #    SGD_number*site ~ var_umol + 1|date/new_colonynumber)

#anova(variances_model)
#summary(variances_model)

### ^^ something is wrong up here 


## now try to plot these things 

plot_meanvars <- RespoR_Normalized_Full_meanvar %>% 
  filter(P_R=="NP") %>% 
  ggplot(aes(x=SGD_number, 
             y=var_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
   labs(x = "SGD Dilutions (% by volume)",
       y = "Variance of Rate (umol O2 cm2 hr-1)",
       title = "Variance of NP Rates")

plot_meanvars2 <- RespoR_Normalized_Full_meanvar %>% 
  filter(P_R=="GP") %>% 
  ggplot(aes(x=SGD_number, 
             y=var_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
   labs(x = "SGD Dilutions (% by volume)",
       y = "Variance of Rate (umol O2 cm2 hr-1)",
       title = "Variance of GP Rates")

plot_meanvars3 <- RespoR_Normalized_Full_meanvar %>% 
  filter(P_R=="R") %>% 
  ggplot(aes(x=SGD_number, 
             y=var_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
  labs(x = "SGD Dilutions (% by volume)",
       y = "Variance of Rate (umol O2 cm2 hr-1)",
       title = "Variance of Respiration Rates")
  
## do for calcification as well 

full.calc.data_meanvar <- full.calc.data %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  group_by(SGD_number, site) %>% 
  summarize(mean_umol = mean(umol.cm2.hr, na.rm=TRUE), 
            var_umol = var(umol.cm2.hr, na.rm=TRUE), 
            sd_umol = sd(umol.cm2.hr, na.rm = TRUE))

plot_meanvars4 <- full.calc.data_meanvar %>%
  ggplot(aes(x=SGD_number, 
             y=sd_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
  labs(x = "SGD Dilutions (% by volume)",
       y = "SD of Rate (umol O2 cm2 hr-1)",
       title = "SD of Calcification Rates")

full.calc.data_meanvar1.5 <- full.calc.data %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  group_by(SGD_number, site) %>% 
  summarize(mean_umol = mean(umol.cm2.hr, na.rm=TRUE), 
            var_umol = var(umol.cm2.hr, na.rm=TRUE), 
            sd_umol = sd(umol.cm2.hr, na.rm = TRUE)) 

full.calc.data_meanvar1.5 <- full.calc.data_meanvar1.5[-c(11), ]
  
plot_meanvars4.5_nooutlier <- full.calc.data_meanvar1.5 %>%
  ggplot(aes(x=SGD_number, 
             y=sd_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
  labs(x = "SGD Dilutions (% by volume)",
       y = "SD of Rate (umol O2 cm2 hr-1)",
       title = "SD of Calcification Rates")

plot_meanvars4_nooutlier <- full.calc.data_meanvar1.5 %>%
  ggplot(aes(x=SGD_number, 
             y=var_umol)) + 
  geom_point(size=4) + 
  theme_bw() + 
  facet_wrap(~site) + 
  labs(x = "SGD Dilutions (% by volume)",
       y = "Variance of Rate (umol O2 cm2 hr-1)",
       title = "Variance of Calcification Rates")


plot_meanvars4_nooutlier + plot_meanvars4.5_nooutlier


plot_meanvars4 + plot_meanvars3 + plot_meanvars2 + plot_meanvars


```


### Testing models to see if nutrients has any significance 

```{r}

## get only the first and last days of nutrients narrowed down 
nutrientdata <- RespoR_Normalized_Full %>% 
  drop_na(NN_umolL) 


### Varari 
RespoR_Normalized_Full3 <- RespoR_Normalized_Full %>% 
  filter(site=="Varari")
max(RespoR_Normalized_Full3$salinity, na.rm=TRUE)
min(RespoR_Normalized_Full3$salinity, na.rm=TRUE)

Varari_resp <- nutrientdata %>% 
  filter(P_R == "R") %>% 
  filter(site=="Varari") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))

Varari_resp_SGD <- lmer(data = Varari_resp, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(Varari_resp_SGD)

Varari_resp_Silicate <- lmer(data = Varari_resp, 
             umol.cm2.hr ~ silicate_umolL + (1|date/new_colonynumber))
anova(Varari_resp_Silicate)
summary(Varari_resp_Silicate)

Varari_resp_NN <- lmer(data = Varari_resp, 
             umol.cm2.hr ~ NN_umolL + (1|date/new_colonynumber))
anova(Varari_resp_NN)

Varari_resp_Phos <- lmer(data = Varari_resp, 
             umol.cm2.hr ~ phosphate_umolL + (1|date/new_colonynumber))
anova(Varari_resp_Phos)


## Cabral 

RespoR_Normalized_Full2 <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral")
max(RespoR_Normalized_Full2$salinity, na.rm=TRUE)
min(RespoR_Normalized_Full2$salinity, na.rm=TRUE)


Cabral_resp<- nutrientdata %>% 
  filter(P_R == "R") %>% 
  filter(site=="Cabral") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date))


Cabral_resp_SGD <- lmer(data = Cabral_resp, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(Cabral_resp_SGD)


Cabral_resp_SGD <- lmer(data = Cabral_resp, 
             umol.cm2.hr ~ SGD_number + (1|date/new_colonynumber))
anova(Cabral_resp_SGD)





```


### plotting for Respiration (Varari and Cabral)
```{r}
## Varari respiration 
Respiration_SGD_V <- RespoR_Normalized_Full %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="R") %>% 
  filter(!is.infinite(umol.cm2.hr)) %>% 
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", 16))) +
  theme_classic() + 
  labs(x = "SGD Dilutions (% by volume)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration Rates at Varari") +
  #scale_x_continuous(limits=c(7.9,8.1)) +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "WSNOutputs","Varari_Resp.jpg"), 
       width = 10, height = 10)
Respiration_SGD_V

### Cabral respiration
Respiration_SGD_C <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="R") %>% 
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=14)) ,
                     guide="none") +
  theme_classic() + 
  #geom_smooth(method = "lm", se=TRUE, color="lightpink") + #### REMOVE GEOM SMOOTH BC INSIGNIFICANT 
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration Rates at Cabral") +
 theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "WSNOutputs","Cabral_Resp.jpg"), 
       width = 10, height = 10)
Respiration_SGD_C

## trying to do it all on one graph so axes are the same and facet by site 
Respiration_SGD_bothsites <- RespoR_Normalized_Full %>% 
  filter(P_R=="R") %>% 
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=18)) ,
                     guide="none") +
  facet_wrap(~site) + 
  theme_classic() + 
  #geom_smooth(method = "lm", se=TRUE, color="lightpink") + #### REMOVE GEOM SMOOTH BC INSIGNIFICANT 
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Respiration Rates by Site") +
 theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20))
```


### plotting GP for Cabral and Varari 
```{r}
## Cabral GP plot  
GP_SGD_C <- RespoR_Normalized_Full %>% 
  filter(site=="Cabral") %>% 
  filter(P_R=="GP") %>% 
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Gross Photosynthesis Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "WSNOutputs","Cabral_GP.jpg"), 
       width = 10, height = 10)

GP_SGD_C

## GP for Varari 

GPData_V <- RespoR_Normalized_Full %>% 
  filter(P_R == "GP") %>% 
  filter(site=="Varari") %>% 
  mutate(new_colonynumber= as.factor(new_colonynumber), 
         date=as.factor(date)) %>% 
  filter(!is.infinite(umol.cm2.hr))

GP_SGD_V <- RespoR_Normalized_Full %>% 
  filter(site=="Varari") %>% 
  filter(P_R=="GP") %>%
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_point(aes(color=salinity, show.legend=FALSE), 
             size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
 # geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Gross Photosynthesis Rates at Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
ggsave(here("Outputs", "WSNOutputs","Varari_GP.jpg"), 
       width = 10, height = 10)

GP_SGD_V


## faceting by site to get plot with both sites in one so scales are the same for axes 
GP_SGD_bothsites <- RespoR_Normalized_Full %>% 
  filter(P_R=="GP") %>%
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr)) + 
  geom_point(aes(color=salinity, show.legend=FALSE), 
             size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=18)), 
                     guide="none") +
  facet_wrap(~site) +
  theme_classic() + 
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Gross Photosynthesis Rates at Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 

GP_SGD_bothsites2 <- RespoR_Normalized_Full %>% 
  filter(P_R=="GP") %>% 
  mutate(salinity=as.factor(salinity)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=18)), 
                     guide="none") +
  theme_classic() + 
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Gross Photosynthesis Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
```
## plotting NEC 

```{r}

## NEC by both sites 

NEC_bothsites <- full.calc.data %>%
  filter(new_colonynumber!="BLANK") %>%
  filter(new_colonynumber!="20") %>% 
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=20)), 
                     guide="none") +
 # facet_wrap(~site) + 
  theme_classic() + 
 # theme(strip.background = element_rect(fill = "white"))+
  geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  geom_hline(yintercept = 0)+
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol CaCO3 g-1 hr-1)",
       title = "Net Calcification Rates at Varari") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 


NEC_C <- full.calc.data %>%
  filter(site=="Varari") %>% 
  mutate(salinity_insitu=as.factor(salinity_insitu)) %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=salinity_insitu)) + 
  geom_point(size=4, 
             position = position_jitterdodge()) +
  scale_color_manual(values=rev(pnw_palette("Sunset2", n=16)), 
                     guide="none") +
  theme_classic() + 
 # facet_wrap(~new_colonynumber)+
  theme(strip.background = element_rect(fill = "white"))+
  geom_smooth(method = "lm", se=TRUE, color="lightpink") +
  geom_hline(yintercept = 0)+
  labs(x = "SGD Dilutions (% by volume)",
       color = "Salinity (ppt)",
       y = "Rate (umol O2 cm2 hr-1)",
       title = "Net Calcification Rates at Cabral") +
   theme(axis.text.x=element_text(size=18), 
        axis.text.y=element_text(size=18), 
        axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18), 
        plot.title=element_text(hjust=0.5, ## centers title 
                                size=20)) 
```

