---
title: "Testing_Blanks"
author: "Hannah Merges"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries 
```{r}
library(patchwork)
library(tidyverse)
library(here)
library(PNWColors)
library(lme4)
library(lmerTest)
library(modelsummary)
library(tidymodels)
library(performance)
library(agricolae)
```

## Read in data 
```{r}
RespoR2 <- read_csv(here("Data","RespoR2.csv")) 


```

# Normalize to Blanks for regular R and GP
Things to think about: 
-  compare the outputs of the averaged and individual days and see if they are similar or really different 
-  plot raw data against blanks to make sure that raw data BEFORE normalized are substantially higher than blanks 

### first way: average across all days 
-  average across all the days and get one point for each dilution 

```{r}
## 1) summarise across all 4 days

avgblanks <- RespoR2 %>% 
  filter(date!="6/13/23") %>% 
  group_by(SGD_number, light_dark, new_colonynumber, site) %>% 
  filter(new_colonynumber== "BLANK") %>%
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% 
  dplyr::select(blank.rate = umol.sec, site)

### plot the averaged blanks to see if it is working properly ### 
plot_Blank_Rates_Averaged <- avgblanks %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(~site) + 
  labs(title="Avg Blanks Across All Days (minus 6/13 Cabral)")

plot_Blank_Rates_Averaged

```


### second way: keep as individual days 
```{r}
## 2) direct comparison day to day 
## look at individual blank values to see if any of the days are particularly off - if everything looks consistent, can stick with individual days 

# each individual chamber has its own blank data 
blanks_perday <- RespoR2 %>% 
  filter(new_colonynumber== "BLANK") %>%
  group_by(SGD_number, light_dark, date, new_colonynumber, site) %>% 
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>% ## so should have one value for each dilution 
  dplyr::select(blank.rate = umol.sec, site) %>% 
  filter(date!="6/13/23")


###############################################
### plot colonies against blanks ###
###############################################
plot_BlankRates <- blanks_perday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(~site, scales="free_y")

plot_BlankRates


plot_BlankRates2 <- blanks_perday %>% 
  ggplot(aes(x=SGD_number, 
             y=blank.rate)) +
  scale_x_continuous(trans="log10") +
  geom_point() + 
  facet_wrap(site~date, scales="free_y")

plot_BlankRates2
```

### Now combine blank data with RespoR2 df 
-  one based on per day blank rates 
-  another based on averaged blank rates 
```{r}

### joining with averaged blanks 
avgblanks_joined <- avgblanks %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, site) %>%
  right_join(RespoR2) %>%  
  filter(new_colonynumber!=19, new_colonynumber!=20,sample_ID!="Varari_Col5_Dil1_Dark") 

### joining with per day blanks 
perdayblanks_joined <- blanks_perday %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date, site) %>%
  right_join(RespoR2) %>% 
  filter(new_colonynumber!=19, new_colonynumber!=20,sample_ID!="Varari_Col5_Dil1_Dark") 

```


### plot raw data unnormalized for umol.L.sec with blanks 

```{r}
## day to day 
plot_raw_vs_avgblanks <- avgblanks_joined %>% 
  mutate(umol.L.sec = ifelse(umol.L.sec < 0, 0, umol.L.sec)) %>% # for any values below 0, make 0
  filter(date!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.L.sec, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(date~site) + 
  labs(title="avg blanks")

plot_raw_vs_avgblanks

## day to day 
plot_raw_vs_dayblanks <- perdayblanks_joined %>% 
  mutate(umol.L.sec = ifelse(umol.L.sec < 0, 0, umol.L.sec)) %>% # for any values below 0, make 0
  filter(date!="6/13/23") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.L.sec, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(date~site) + 
  labs(title="daily blanks")

plot_raw_vs_dayblanks

plot_raw_vs_dayblanks + plot_raw_vs_avgblanks ## no difference here with raw data and blanks, which is good 

```


### Calculate R and GP with normalizing to averaged blanks 
-  **without** Cabral (blanks are weird on 13th)  

```{r}

### joining with averaged blanks 
normalizingR_with_avgblanks <- avgblanks %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%  
  filter(new_colonynumber!=19, new_colonynumber!=20,sample_ID!="Varari_Col5_Dil1_Dark") 
## trying to eliminate the potential for errors here -- so remove the whole colony 5 from Varari (Dark for Respo, Light for GP/NP)

##########
## Dec 5: try without removing blanks for oxygen evolution table request from Craig 
normalizingR_with_avgblanks2 <- avgblanks %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2) %>% 
 # filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%  
  filter(new_colonynumber!=19, new_colonynumber!=20,sample_ID!="Varari_Col5_Dil1_Dark") 



###############################
### calculate R 
###############################
# make the respiration values positive (pull out data for dark treatments)

normalizedR_avgblanks <- normalizingR_with_avgblanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>% 
  mutate(P_R = "R")

###############################
### calculate NP 
###############################

# all light run rates get NP for net photosynthesis
normalizedNP_avgblanks <- normalizingR_with_avgblanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>% 
  mutate(P_R = "NP") 

# rejoin data into single df
normalizedRates_avgblanks <- bind_rows(normalizedNP_avgblanks, normalizedR_avgblanks) 

###############################
### calculate GP 
###############################

normalizedGP_avgblanks <- normalizedRates_avgblanks %>%
  group_by(new_colonynumber, SGD_number, site, date) %>%
  dplyr::summarize(umol.cm2.hr = sum(umol.cm2.hr, na.rm = TRUE)) %>% # NP + R = GP
  ungroup() %>%
  mutate(P_R = "GP", light_dark = "LIGHT") %>% # Label for Gross Photosynthesis
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>%
  left_join(dplyr::select(normalizedRates_avgblanks, new_colonynumber, sample_ID, SGD_number, site, salinity, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL)) 

### steps to organize and delete Dark values
RespoR_NormalizedGP_2.1 <- normalizedGP_avgblanks %>% 
  dplyr::mutate(light_dark = str_extract(sample_ID, "[^_]+$"))

RespoR_NormalizedGP_2.1_rows_Dark <- which(RespoR_NormalizedGP_2.1$light_dark == "Dark") #tells you all the rows that you have with blanks
Dark_2 <-RespoR_NormalizedGP_2.1[RespoR_NormalizedGP_2.1_rows_Dark,] 
RespoR_NormalizedGP_2.1_rows_Dark_3 <- RespoR_NormalizedGP_2.1[-RespoR_NormalizedGP_2.1_rows_Dark,] #to remove the rows with dark data, now have data sheet with only light, SA and volume values
RespoR_NormalizedGP_2.1_rows_Dark_3[,7] = NULL #delete the light-dark column to allow to just join by fragment.ID

normalizedGP_avgblanks <- RespoR_NormalizedGP_2.1_rows_Dark_3


# rejoin for full df with NP, R, and GP rates
AllRates_Normalized_avgblanks <- normalizedRates_avgblanks %>% 
  dplyr::select(new_colonynumber, sample_ID, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%
  bind_rows(normalizedGP_avgblanks) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr))



```

### Calculate R and GP with day to day blanks 
```{r}

### joining with day to day blanks 
normalizingR_with_dailyblanks <- blanks_perday %>% 
  ungroup() %>% 
  dplyr::select(SGD_number, light_dark, blank.rate, date, site) %>%
  right_join(RespoR2) %>% # join with the respo data
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.cm2.hr = (umol.sec.corr*3600)/SA_cm2) %>% 
  filter(new_colonynumber!="BLANK") %>% # remove the Blank data
  #ungroup() %>%
  dplyr::select(date, sample_ID, light_dark, SA_cm2, umol.cm2.hr, umol.sec, blank.rate, Temp.C, new_colonynumber, salinity, pH, site, SGD_number, umol.sec.corr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%  
  filter(new_colonynumber!=19, new_colonynumber!=20,sample_ID!="Varari_Col5_Dil1_Dark") 
## trying to eliminate the potential for errors here -- so remove the whole colony 5 from Varari (Dark for Respo, Light for GP/NP)


###############################
### calculate R 
###############################
# make the respiration values positive (pull out data for dark treatments)

normalizedR_dailyblanks <- normalizingR_with_dailyblanks %>% 
  filter(light_dark == "DARK") %>% 
  mutate(umol.cm2.hr = umol.cm2.hr*-1) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>% 
  mutate(P_R = "R")

###############################
### calculate NP 
###############################

# all light run rates get NP for net photosynthesis
normalizedNP_dailyblanks <- normalizingR_with_dailyblanks %>% 
  filter(light_dark == "LIGHT") %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>% 
  mutate(P_R = "NP") 

# rejoin data into single df
normalizedRates_dailyblanks <- bind_rows(normalizedNP_dailyblanks, normalizedR_dailyblanks) 

normalizedRates_dailyblanks <- normalizedRates_dailyblanks %>% 
  dplyr::select(!c("SA_cm2", "umol.sec", "blank.rate", "umol.sec.corr", "pH"))


###############################
### calculate GP 
###############################

normalizedGP_dailyblanks <- normalizedRates_dailyblanks %>%
  group_by(new_colonynumber, SGD_number, site, date) %>%
  dplyr::summarize(umol.cm2.hr = sum(umol.cm2.hr, na.rm = TRUE)) %>% # NP + R = GP
  ungroup() %>%
  mutate(P_R = "GP", light_dark = "LIGHT") %>% # Label for Gross Photosynthesis
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr < 0, 0, umol.cm2.hr)) %>%
  left_join(dplyr::select(normalizedRates_dailyblanks, new_colonynumber, sample_ID, SGD_number, site, salinity, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL)) 

### steps to organize and delete Dark values
GP_dailyblanks <- normalizedGP_dailyblanks %>% 
  dplyr::mutate(light_dark = str_extract(sample_ID, "[^_]+$"))

GP_dailyblanks_Dark <- which(GP_dailyblanks$light_dark == "Dark") #tells you all the rows that you have with blanks
Dark_2 <-GP_dailyblanks[GP_dailyblanks_Dark,] 
GP_dailyblanks_Dark_2 <- GP_dailyblanks[-GP_dailyblanks_Dark,] #to remove the rows with dark data, now have data sheet with only light, SA and volume values
GP_dailyblanks_Dark_2[,7] = NULL #delete the light-dark column to allow to just join by fragment.ID

normalizedGP_dailyblanks <- GP_dailyblanks_Dark_2


# rejoin for full df with NP, R, and GP rates
AllRates_Normalized_dailyblanks <- normalizedRates_dailyblanks %>% 
  dplyr::select(new_colonynumber, sample_ID, SGD_number, site, salinity, date, light_dark, P_R, umol.cm2.hr, phosphate_umolL, silicate_umolL, NN_umolL, ammonia_umolL) %>%
  bind_rows(GP_dailyblanks_Dark_2) %>% 
  mutate(umol.cm2.hr = ifelse(umol.cm2.hr ==0, NA, umol.cm2.hr))


  

```


### plot normalized rates from avg and day to day to see differences in pattern or rates 
```{r}

#### averaged for R 
Rrates_avgblanks <- AllRates_Normalized_avgblanks %>% 
  filter(P_R=="R") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(~new_colonynumber)

Rrates_avgblanks

#### daily for R
Rrates_dailyblanks <- AllRates_Normalized_dailyblanks %>% 
  filter(P_R=="R") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(~new_colonynumber)

Rrates_dailyblanks

Rrates_dailyblanks + Rrates_avgblanks

################################################
################################################

## for GP 

GPrates_avgblanks <- AllRates_Normalized_avgblanks %>% 
  filter(P_R=="GP") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(~new_colonynumber)

GPrates_avgblanks


GPrates_dailyblanks <- AllRates_Normalized_dailyblanks %>% 
  filter(P_R=="GP") %>% 
  ggplot(aes(x=SGD_number, 
             y=umol.cm2.hr, 
             color=new_colonynumber)) + 
  geom_point() + 
  facet_wrap(~new_colonynumber)

GPrates_dailyblanks
```




#### Show that blanks were always x% of corals

```{r}

perdayblanks_joined_edit <- perdayblanks_joined %>% 
  dplyr::select(c("new_colonynumber", "blank.rate", "umol.L.sec", "SGD_number", "date", "site", "light_dark")) %>% 
  group_by(SGD_number, light_dark, date) %>% 
  mutate(ratio = blank.rate/umol.L.sec) %>% 
  filter(new_colonynumber!="BLANK")


blank_coral_ratio_plot <- perdayblanks_joined_edit %>% 
  ggplot(aes(x=ratio,
             fill=site)) + 
  geom_histogram(bins=40, binwidth=0.01) + 
  scale_fill_manual(values=c("goldenrod", "firebrick4"))

blank_coral_ratio_plot



#### look at the values that have ratios greater than 0.1

perdayblanks_joined_edit2 <- perdayblanks_joined_edit %>% 
  filter(ratio < -0.1) ## 38 (23 values > 0.1 and 15 values < -0.1) values are particularly high out of 250

```








